---
title: "Kelp Biomass Map"
author: "Chance English"
date: "7/23/2024"
output: html_document
---


```{r setup, include=FALSE, echo=F, warning=F, message=F}
knitr::opts_chunk$set(echo = TRUE, message = F, echo = F, warning = F)
```

```{r,include=FALSE, echo=F, warning=F, message=F}


library(tidyverse)
library(lmodel2)
library(ggplot2)
library(readxl)
library(kableExtra)
library(scales)
library(factoextra)
library(mgcv)
library(janitor)
library(broom)
library(rstatix)
library(ggpubr)
library(vegan)
library(ggbump)
library(maps)
library(mapdata)
library(ggmap)
library(reshape2)
library(here)

```

# Map of california coastline 

```{r}

states <- map_data("state")

ca_df <- states %>%
  filter(region == "california")

ca_base <- ggplot(data = ca_df, mapping = aes(x = long, y = lat, group = group)) + 
  coord_quickmap() + 
  geom_polygon(color = "black", fill = "gray")




```



# Load in Quarterly Kelp Biomass Data from 1987-2019


```{r}


annual_kelp_biomass <- read_csv(here("Data","kelp_no3_waves_annual_long.csv"))

kelp_biomass_lat_long <- read_csv(here("Data","locations.csv"))



```


# Summarize Average Annual Biomass at each site 

```{r}


site_avg_annual_kelp_biomass <- annual_kelp_biomass %>% 
  group_by(site_id) %>% 
  summarise(avg_biomass_kg_ww = mean(kelp)) %>% 
  ungroup()

annual_biomass_total <- annual_kelp_biomass %>% 
  group_by(year) %>% 
  summarise(total_biomass = sum(kelp)) %>% 
  ungroup()

min(annual_biomass_total$total_biomass)
max(annual_biomass_total$total_biomass)



```


# Merge Annual Kelp Biomass at site with lat and long data 

```{r}

avg_biomass_lat_long <- merge(site_avg_annual_kelp_biomass, kelp_biomass_lat_long, by = c("site_id"))


avg_biomass_lat_long <- avg_biomass_lat_long %>% 
  mutate(long = lon,
         lat = lat)

total_avg_biomass <- sum(avg_biomass_lat_long$avg_biomass_kg_ww) 

```


# Add Kelp Biomass Data to Map of California 


```{r}

mid <- median(avg_biomass_lat_long$avg_biomass_kg_ww)

ca_kelp_biomass <- ggplot() + 
  coord_quickmap() + 
  geom_polygon(data = ca_df, 
               mapping = aes(x = long, 
                             y = lat, 
                             group = group), 
               color = "black", 
               fill = "gray") +
  geom_point(data = avg_biomass_lat_long, 
             aes(x = long, 
                 y = lat, 
                 color = avg_biomass_kg_ww/100000), 
             size = 2,
             position = position_jitter(width = 0.1, height = 0.025)) +
  geom_point(aes(x = -119.7299, y = 34.3934), shape= 13, size = 10, fill = "red") +
  scale_color_gradient2(midpoint = mid/100000, 
                        low = "yellow", 
                        mid = "darkgreen",
                        high = "olivedrab4", 
                        space = "Lab", 
                        name = expression(paste("Biomass (","10"^5," kg)")),
                        breaks = c(0, 0.1, 1, 10, 20),
                        trans = "log10") +
  labs(x = "Longitude (ºW)",
       y = "Latitude (ºN)") +
   theme(panel.background = element_rect(fill = "white", 
                                         color = "black", 
                                         size = 1.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = margin(1,1,1,1, "cm"),
        strip.background = element_rect(fill = "white", 
                                        color = "black"),
        legend.key = element_rect(fill = "white"),
        legend.text = element_text(size = 20),
        legend.key.height = unit(0.4, "inch"),
        legend.key.width = unit(0.3, "inch"),
        legend.position = "top",
        legend.title = element_text(size = 24),
        axis.text = element_text(size = 20, 
                                 color = "black"),
        axis.title = element_text(size = 24),
        text = element_text(family = "Times"))

  

ggsave(file="ca_kelp_biomass.png", plot= ca_kelp_biomass, width=10, height=10)



```


# LTER Mohawk CN and NUTS

# Giant Kelp Stoichiometry 

```{r}

kelp_C_N_lter <- read_csv(here("Data", "CHN_Field_all_years_20211006.csv"))

kelp_C_N_lter[kelp_C_N_lter == -99999.00] <- NA

kelp_C_N_lter_MK <- kelp_C_N_lter %>% 
  mutate(month = case_when(
    MONTH == 1 ~ "Jan",
    MONTH == 2 ~ "Feb",
    MONTH == 3 ~ "Mar",
    MONTH == 4 ~ "Apr",
    MONTH == 5 ~ "May",
    MONTH == 6 ~ "Jun",
    MONTH == 7 ~ "Jul",
    MONTH == 8 ~ "Aug",
    MONTH == 9 ~ "Sep",
    MONTH == 10 ~ "Oct",
    MONTH == 11 ~ "Nov",
    MONTH == 12 ~ "Dec"),
    molC = C/12, molN = N/14, c_n_molar = molC/molN) %>% 
  filter(c_n_molar != "NA") %>% 
  mutate(c_n_molar = as.numeric(c_n_molar)) %>% 
  filter(c_n_molar < 300) %>% 
  filter(SITE == "MOHK")

kelp_C_N_lter_MK$month <- factor(kelp_C_N_lter_MK$month, levels = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"))

MK_CN <- kelp_C_N_lter_MK %>% 
  group_by(month) %>% 
  summarize(mean_C_N = mean(CN_RATIO), se_c_n = (sd(CN_RATIO)/sqrt(length(CN_RATIO)))) %>% 
  ggplot(aes(x = month, y = mean_C_N)) +
  geom_point(size = 5) +
  geom_line() +
  geom_errorbar(aes(ymin = mean_C_N - se_c_n, ymax = mean_C_N + se_c_n), width = 0, alpha = 0.5) +
  labs(y = "Carbon:Nitrogen",
       x = "") + 
  scale_y_continuous(limits = c(10,25), breaks = c(10,15,20,25,30)) +
  theme(panel.background = element_rect(fill = "white", color = "black", size = 1.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        strip.background = element_rect(fill = "white", color = "black"),
        legend.key = element_rect(fill = "white"),
        legend.title = element_blank(),
        plot.title = element_text(face = "italic", size = 15),
        legend.text = element_text(size = 15),
        axis.text = element_text(size = 15, color = "black"),
        axis.title = element_text(size = 20),
        text = element_text(family = "Times"))



```

# Monthyl Nutrients 

```{r}

lter_bottle_monthly <- read_xlsx(here("data","SBC_LTER_Monthly_Bottle_Data.xlsx"))

lter_bottle_monthly[lter_bottle_monthly == 99999.000] <- NA

lter_bottle_monthly$`NO2+NO3 (umol/l)`[lter_bottle_monthly$`NO2+NO3 (umol/l)` == "BDL"] <- 0

lter_bottle_monthly_nuts <- lter_bottle_monthly %>% 
  mutate(`yyyy-mm-dd` = as.Date(`yyyy-mm-dd`,format = "%yyyy-%mm-%dd")) %>% 
  mutate(month_name = as.character(format(as.Date(`yyyy-mm-dd`),"%b"))) %>% 
  filter(`NO2+NO3 (umol/l)` != "NA") %>% 
  filter(`Target Depth (m)` == 1) %>% 
# %>% 
  select(month_name, `NO2+NO3 (umol/l)`)


lter_bottle_monthly_nuts <- lter_bottle_monthly_nuts %>% 
  mutate(`NO2+NO3 (umol/l)` = as.numeric(`NO2+NO3 (umol/l)`))

lter_bottle_monthly_nuts$month_name <- factor(lter_bottle_monthly_nuts$month_name, levels = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"))

nuts_p <- lter_bottle_monthly_nuts %>% 
  filter(month_name != "NA") %>% 
  group_by(month_name) %>% 
  summarize(mean_n = mean(`NO2+NO3 (umol/l)`), se_n = sd(`NO2+NO3 (umol/l)`)/sqrt(length(`NO2+NO3 (umol/l)`))) %>% 
  ungroup() %>% 
  ggplot(aes(x = month_name, y = mean_n)) +
  geom_point(size = 5) +
  geom_line() +
  geom_errorbar(aes(ymin = mean_n - se_n, ymax = mean_n + se_n), width = 0, alpha = 0.5) +
  labs(y = "N+N (µM)",
       x = "") + 
  theme(panel.background = element_rect(fill = "white", color = "black", size = 1.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        strip.background = element_rect(fill = "white", color = "black"),
        legend.key = element_rect(fill = "white"),
        legend.title = element_blank(),
        plot.title = element_text(face = "italic", size = 15),
        legend.text = element_text(size = 15),
        axis.text = element_text(size = 15, color = "black"),
        axis.title = element_text(size = 20),
        text = element_text(family = "Times"))+
  geom_hline(yintercept = 1, color = "red")
  

lter_bottle_monthly_nuts_sum <- lter_bottle_monthly_nuts %>% 
  group_by(month_name) %>% 
  summarize(mean_n = mean(`NO2+NO3 (umol/l)`)) %>% 
  ungroup()



```

# Combine CN, NUTS and Biomass plots 

```{r}


library(cowplot)

CN_nuts_part_one <- plot_grid(nuts_p, MK_CN,labels = c('B', 'C'), ncol = 1,label_size = 20, label_fontfamily = "Times New Roman")


biomass_CN_nuts <- plot_grid(ca_kelp_biomass, CN_nuts_part_one,labels = c('A', ''), label_size = 20 ,label_fontfamily = "Times New Roman")


ggsave("biomass_CN_nuts.png", plot = biomass_CN_nuts, path = "/Users/chanceenglish/Desktop/Lab Shiz/ARPA-e/Giant_Kelp_DOC/Figures/", width = 15, height = 8 , device='tiff', dpi=1000, units = "in")








```


# M pyrifera and bull kelp data from SBC LTER NC Files 

https://doi.org/10.6073/pasta/c40db2c8629cfa3fbe80fdc9e086a9aa 

```{r}

library(ncdf4) # package for netcdf manipulation
library(raster) # package for raster manipulation
library(rgdal) # package for geospatial analysis
library(ggplot2)


```


# Load Data 

```{r}
    
nc_data <- nc_open(here("Data", 'CAkelpCanopyEnv_2021_final.nc'))


lon <- ncvar_get(nc_data, "lon")
lat <- ncvar_get(nc_data, "lat")
year <- ncvar_get(nc_data, "year")
quarter <- ncvar_get(nc_data, "quarter")
biomass <- ncvar_get(nc_data, "biomass")
area <- ncvar_get(nc_data, "area")



```



```{r}

latitude <- as.numeric(lat[1:332640])
longitude <- as.numeric(lon[1:332640])

year <- as.numeric(year[1:152])
quarter <- as.numeric(quarter[1:152])

biomass_df <- as.data.frame(biomass)
area_df <- as.data.frame(area)

year_quarter_df <- as.data.frame(year) %>% 
  mutate(quarter = quarter)

year_quarter_df$year_quarter <- paste(year_quarter_df$year,year_quarter_df$quarter,sep="_")

year_quarter <- year_quarter_df$year_quarter



colnames(biomass_df) <- year_quarter

# Get Biomass and Calculate Total Quarterly Biomass for every year

biomass_df_year_quarter <- biomass_df %>% 
  mutate(
    lat = latitude,
    long = longitude
  ) 



biomass_long <- melt(biomass_df_year_quarter, 
                     id.vars = c("lat", "long"),
                     variable.name = "year_quarter",
                     value.name = "kelp_biomass")

biomass_long_noNA <- biomass_long %>% 
  filter(kelp_biomass != "NA") %>% 
  filter(kelp_biomass != 0)

biomass_long_no_blank_images_df <- biomass_long_noNA %>% 
  separate(year_quarter, into = c("year", "quarter"), sep = "_")

write.csv(biomass_long_no_blank_images_df, "/Users/chanceenglish/Desktop/Lab Shiz/ARPA-e/Giant_Kelp_DOC/Data/biomass_long_no_blank_images_df.csv", row.names = F)

biomass_2021_summer_noNA <- biomass_long_no_blank_images_df %>% 
  filter(year == 2021, quarter == 3)

median(biomass_2021_summer_noNA$kelp_biomass)

annual_quarterly_kelp_biomass <- biomass_long_no_blank_images_df %>% 
  group_by(year, quarter) %>% 
  summarize(total_biomass_kg_ww = sum(kelp_biomass))


write.csv(biomass_long, "~/kelp_area_latlong_time.csv", row.names = F)



# Kelp Total Kelp Area 

colnames(area_df) <- year_quarter

area_df_year_quarter <- area_df %>% 
  mutate(
    lat = latitude,
    long = longitude
  ) 



area_long <- melt(area_df_year_quarter, 
                     id.vars = c("lat", "long"),
                     variable.name = "year_quarter",
                     value.name = "kelp_area")

area_long_noNA <- area_long %>% 
  filter(kelp_area != "NA") %>% 
  filter(kelp_area != 0) %>% 
  filter(lat <= 37.52588)

area_long_no_blank_images_df <- area_long_noNA %>% 
  separate(year_quarter, into = c("year", "quarter"), sep = "_")

annual_quarterly_kelp_area <- area_long_no_blank_images_df %>% 
  group_by(year, quarter) %>% 
  summarize(total_area_km2 = sum(kelp_area)/1000000)


# Merge Annual Kelp Biomass and Area

kelp_annual_quarterly_biomass_area <- merge(annual_quarterly_kelp_biomass, annual_quarterly_kelp_area, by = c("year", "quarter"))


write.csv(kelp_annual_quarterly_biomass_area, file = "/Users/chanceenglish/Desktop/Lab Shiz/ARPA-e/MP Exudate Sampling/data/Compiled Data/kelp_annual_quarterly_biomass_area.csv", row.names = FALSE)



```


```{r}

kelp_biomass_p <- ggplot() + 
  coord_quickmap() + 
  geom_polygon(data = ca_df, 
               mapping = aes(x = long, 
                             y = lat, 
                             group = group), 
               color = "black", 
               fill = "gray") +
  geom_point(data = biomass_2021_summer_noNA, 
             aes(x = long, 
                 y = lat, 
                 color = kelp_biomass/1000), 
             size = 0.5,
             position = position_jitter(width = 0.025, height = 0.025)) +
  labs(x = "Longitude (ºW)",
       y = "Latitude (ºN)") +
  scale_color_gradient2(midpoint = 1.8 , 
                        low = "goldenrod", 
                        mid = "goldenrod1",
                        high = "goldenrod4", 
                        space = "Lab",
                        name = "Canopy Biomass\n(Mg WW)",
                        breaks = c(1,5,10)) +
   theme(panel.background = element_rect(fill = "white", 
                                         color = "black", 
                                         size = 1.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = margin(1,1,1,1, "cm"),
        strip.background = element_rect(fill = "white", 
                                        color = "black"),
        legend.key = element_rect(fill = "white"),
        legend.text = element_text(size = 20),
        legend.key.height = unit(0.3, "inch"),
        legend.key.width = unit(0.3, "inch"),
        legend.position = c(0.75,0.78),
        legend.title = element_text(size = 20),
        axis.text = element_text(size = 20, 
                                 color = "black"),
        axis.title = element_text(size = 25),
        text = element_text(family = "Times"))


#scale_color_gradient2(midpoint = 1.8 , 
                        low = "goldenrod", 
                        mid = "goldenrod1",
                        high = "goldenrod4", 
                        space = "Lab",
                        name = "Canopy Biomass\n(Mg WW)",
                        breaks = c(1,5,10)) +

ggsave(file="ca_kelp_area_orange.svg", plot= kelp_area_p, width=10, height=10)


```


Plot annual/quarterly totals

```{r}

kelp_annual_quarterly_biomass_area <- read_csv(here("data","kelp_annual_quarterly_biomass_area.csv"))

kelp_annual_quarterly_biomass_area <- kelp_annual_quarterly_biomass_area %>% 
  mutate(quarter = as.factor(quarter))

kelp_biomass_CA_annual <- ggplot(data = kelp_annual_quarterly_biomass_area, 
       aes(x = interaction(year, 
                           quarter, 
                           lex.order = TRUE), 
           y = total_biomass_kg_ww, 
           group = 1)) +
  labs(y = "Canopy Biomass (kg WW)",
       x = "") +
  geom_line(colour = "blue") +
  coord_cartesian(ylim = c(800000, 500000000), expand = FALSE, clip = "off") +
  theme_bw() +
  scale_x_discrete(breaks = c("1990", "2020")) +
   theme(panel.background = element_rect(fill = "white", 
                                         color = "black", 
                                         size = 1.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = margin(1,1,1,1, "cm"),
        strip.background = element_rect(fill = "white", 
                                        color = "black"),
        legend.title = element_text(size = 20),
        axis.text = element_text(size = 20, 
                                 color = "black"),
        axis.title = element_text(size = 25),
        text = element_text(family = "Times"))


kelp_annual_quarterly_biomass_area <- kelp_annual_quarterly_biomass_area %>% 
  mutate(total_biomass_g_dw = total_biomass_kg_ww * 0.1 *1000) %>% 
  select(-total_biomass_kg_ww)


kelp_annual_quarterly_biomass_area %>% 
  mutate(quarter = as.numeric(quarter)) %>% 
  ggplot(aes(group = year)) +
  geom_point(aes(x = quarter, y = total_biomass_g_dw/1000/10000000, color = year)) +
  geom_line(aes(x = quarter, y = total_biomass_g_dw/1000/10000000, color = year),
            orientation = "x") +
   scico::scale_color_scico(palette = "tokyo", breaks = c(1990,2000,2010,2020)) +
  labs(y = expression(paste("Biomass (","10"^8," kg DW)")),
       x = "Quarter") +
  theme(panel.background = element_rect(fill = "white", 
                                         color = "black", 
                                         size = 1.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = margin(1,1,1,1, "cm"),
        strip.background = element_rect(fill = "white", 
                                        color = "black"),
        legend.title = element_text(size = 20),
        axis.text = element_text(size = 20, 
                                 color = "black"),
        axis.title = element_text(size = 25),
        text = element_text(family = "Times"))


kelp_annual_quarterly_biomass_area %>% 
  mutate(quarter = as.numeric(quarter)) %>% 
  ggplot(aes(group = year)) +
  geom_tile(aes(x = year, y = quarter, fill = total_biomass_g_dw)) +
  scico::scale_fill_scico(palette = "lajolla", breaks = c(1e8, 2e8,3e8,4e8)) +
  labs(fill = expression(paste("Biomass (","10"^8," kg DW)")),
       x = "Year",
       y = "Quarter") +
  theme(panel.background = element_rect(fill = "white", 
                                         color = "black", 
                                         size = 1.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = margin(1,1,1,1, "cm"),
        strip.background = element_rect(fill = "white", 
                                        color = "black"),
        legend.title = element_text(size = 20),
        axis.text = element_text(size = 20, 
                                 color = "black"),
        axis.title = element_text(size = 25),
        text = element_text(family = "Times"))


```
# One-Way ANOVA Quarterly Biomass

```{r}

aov_quarter_biomass <- aov(total_biomass_kg_ww ~ quarter, data = kelp_annual_quarterly_biomass_area)

summary(aov_quarter_biomass)


TukeyHSD(aov_quarter_biomass)

```


# Simple Extrapolation of DOC Production Rates 

```{r}

kelp_annual_quarterly_biomass_area <- kelp_annual_quarterly_biomass_area %>% 
  mutate(total_biomass_g_dw = total_biomass_kg_ww * 0.1 *1000) %>% 
  select(-total_biomass_kg_ww)


quarterly_DOC_production <- kelp_annual_quarterly_biomass_area %>% 
  mutate(DOC_production_all_mature = (((total_biomass_g_dw * (0.88*12*91.25))/1000/1000*12)/1000/1000/1000) + 
           (((total_biomass_g_dw * (3.3*12*91.25))/1000/1000*12)/1000/1000/1000),
         DOC_summer_senescence_10 = case_when(
           quarter %in% c("1","2","4") ~ (total_biomass_g_dw * ((2.3*24*91.25))/1000/1000*12)/1000/1000/1000,
           quarter == "3" ~ ((total_biomass_g_dw * 0.9 * ((2.3*24*91.25))/1000/1000*12)/1000/1000/1000) +
             ((total_biomass_g_dw * 0.1 * ((14.0*24*91.25))/1000/1000*12)/1000/1000/1000)),
         DOC_summer_senescence_20 = case_when(
           quarter %in% c("1","2","4") ~ (total_biomass_g_dw * ((2.3*24*91.25))/1000/1000*12)/1000/1000/1000,
           quarter == "3" ~ ((total_biomass_g_dw * 0.8 * ((2.3*24*91.25))/1000/1000*12)/1000/1000/1000) +
             ((total_biomass_g_dw * 0.2 * ((14.0*24*91.25))/1000/1000*12)/1000/1000/1000)),
         DOC_summer_senescence_30 = case_when(
           quarter %in% c("1","2","4") ~ (total_biomass_g_dw * ((2.3*24*91.25))/1000/1000*12)/1000/1000/1000,
           quarter == "3" ~ ((total_biomass_g_dw * 0.7 * ((2.3*24*91.25))/1000/1000*12)/1000/1000/1000) +
             ((total_biomass_g_dw * 0.3 * ((14.0*24*91.25))/1000/1000*12)/1000/1000/1000)),
         DOC_summer_senescence_40 = case_when(
           quarter %in% c("1","2","4") ~ (total_biomass_g_dw * ((2.3*24*91.25))/1000/1000*12)/1000/1000/1000,
           quarter == "3" ~ ((total_biomass_g_dw * 0.6 * ((2.3*24*91.25))/1000/1000*12)/1000/1000/1000) +
             ((total_biomass_g_dw * 0.4 * ((14.0*24*91.25))/1000/1000*12)/1000/1000/1000)),
         DOC_summer_senescence_50 = case_when(
           quarter %in% c("1","2","4") ~ (total_biomass_g_dw * ((2.3*24*91.25))/1000/1000*12)/1000/1000/1000,
           quarter == "3" ~ ((total_biomass_g_dw * 0.5 * ((2.3*24*91.25))/1000/1000*12)/1000/1000/1000) +
             ((total_biomass_g_dw * 0.5 * ((14.0*24*91.25))/1000/1000*12)/1000/1000/1000)),
         DOC_summer_senescence_60 = case_when(
           quarter %in% c("1","2","4") ~ (total_biomass_g_dw * ((2.3*24*91.25))/1000/1000*12)/1000/1000/1000,
           quarter == "3" ~ ((total_biomass_g_dw * 0.4 * ((2.3*24*91.25))/1000/1000*12)/1000/1000/1000) +
             ((total_biomass_g_dw * 0.6 * ((14.0*24*91.25))/1000/1000*12)/1000/1000/1000)),
         DOC_summer_senescence_70 = case_when(
           quarter %in% c("1","2","4") ~ (total_biomass_g_dw * ((2.3*24*91.25))/1000/1000*12)/1000/1000/1000,
           quarter == "3" ~ ((total_biomass_g_dw * 0.3 * ((2.3*24*91.25))/1000/1000*12)/1000/1000/1000) +
             ((total_biomass_g_dw * 0.7 * ((14.0*24*91.25))/1000/1000*12)/1000/1000/1000)),
         DOC_summer_senescence_80 = case_when(
           quarter %in% c("1","2","4") ~ (total_biomass_g_dw * ((2.3*24*91.25))/1000/1000*12)/1000/1000/1000,
           quarter == "3" ~ ((total_biomass_g_dw * 0.2 * ((2.3*24*91.25))/1000/1000*12)/1000/1000/1000) +
             ((total_biomass_g_dw * 0.8 * ((14.0*24*91.25))/1000/1000*12)/1000/1000/1000)),
         DOC_summer_senescence_90 = case_when(
           quarter %in% c("1","2","4") ~ (total_biomass_g_dw * ((2.3*24*91.25))/1000/1000*12)/1000/1000/1000,
           quarter == "3" ~ ((total_biomass_g_dw * 0.1 * ((2.3*24*91.25))/1000/1000*12)/1000/1000/1000) +
             ((total_biomass_g_dw * 0.9 * ((14.0*24*91.25))/1000/1000*12)/1000/1000/1000)))





doc_production_first_look <- quarterly_DOC_production %>% 
  group_by(year) %>% 
  summarize(biomass_C = sum(total_biomass_g_dw/1000/1000/1000*0.3),
            DOC_annual = sum(DOC_production_all_mature),
            DOC_annual_10 = sum(DOC_summer_senescence_10),
             DOC_annual_20 = sum(DOC_summer_senescence_20),
             DOC_annual_30 = sum(DOC_summer_senescence_30),
             DOC_annual_40 = sum(DOC_summer_senescence_40),
             DOC_annual_50 = sum(DOC_summer_senescence_50),
             DOC_annual_60 = sum(DOC_summer_senescence_60),
             DOC_annual_70 = sum(DOC_summer_senescence_70),
             DOC_annual_80 = sum(DOC_summer_senescence_80),
             DOC_annual_90 = sum(DOC_summer_senescence_90)) %>% 
  ggplot() +
  geom_line(aes(x = year, y = biomass_C), color = "black") +
  geom_line(aes(x = year, y = DOC_annual), color = "blue") +
  geom_line(aes(x = year, y = DOC_annual_10), color = "goldenrod1") +
  geom_line(aes(x = year, y = DOC_annual_90), color = "red") +
  labs(y = "Gg C",
       x = "") +
  scale_x_continuous(expand = c(0,0)) +
  theme(panel.background = element_rect(fill = "white", color = "black", size = 1.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = margin(1,1,1,1, "cm"),
        strip.background = element_rect(fill = "white", color = "black"),
        legend.key = element_rect(fill = "white"),
        legend.text = element_text(size = 20),
        legend.key.height = unit(0.8, "inch"),
        legend.key.width = unit(0.4, "inch"),
        legend.title = element_text(size = 24),
        axis.text = element_text(size = 30, color = "black"),
        axis.title = element_text(size = 25),
        text = element_text(family = "Times")) 


write.csv(quarterly_DOC_production, file = "/Users/chanceenglish/Desktop/Lab Shiz/ARPA-e/Giant_Kelp_DOC/Data/quarterly_DOC_production.csv", row.names = FALSE)



```

# Tom's Biomass Data

```{r}

biomass_phys <- read_csv(here("Data", "biomass_phys_state.csv"))


biomass_phys <- biomass_phys %>% 
  mutate(month_name = case_when(
    month == 1 ~ "Jan",
    month == 2 ~ "Feb",
    month == 3 ~ "Mar",
    month == 4 ~ "Apr",
    month == 5 ~ "May",
    month == 6 ~ "Jun",
    month == 7 ~ "Jul",
    month == 8 ~ "Aug",
    month == 9 ~ "Sep",
    month == 10 ~ "Oct",
    month == 11 ~ "Nov",
    month == 12 ~ "Dec"
  )) 

biomass_phys$month_name <- biomass_phys$month_name <- factor(biomass_phys$month_name, levels = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"))

```

# CA Wide DOC Production Rates

```{r}

monthly_DOC_production <- biomass_phys %>% 
  mutate(DOC_production_all_mature = ((((total_biomass*1000*0.12) * (0.9*12*30))/1000/1000*12)/1000/1000/1000) + 
           ((((total_biomass*1000*0.12) * (3.3*12*30))/1000/1000*12)/1000/1000/1000),
         DOC_production_senescent = (senescent_biomass*1000*0.12) * (((14.0*24*30))/1000/1000*12)/1000/1000/1000,
         DOC_production_mature = ((((mature_biomass*1000*0.12) * (0.9*12*30))/1000/1000*12)/1000/1000/1000) + 
           ((((mature_biomass*1000*0.12) * (3.3*12*30))/1000/1000*12)/1000/1000/1000),
         DOC_production_mature_senescent = DOC_production_senescent + DOC_production_mature,
         percent_biomass = DOC_production_mature_senescent/(total_biomass*0.12*0.3/1000/1000)*100)


doc_production_first_look <- monthly_DOC_production %>% 
  group_by(year) %>% 
  summarize(biomass_C = sum(total_biomass/1000/1000*0.3),
            DOC_annual_no_senescence = sum(DOC_production_all_mature),
            DOC_annual_w_senescence = sum(DOC_production_mature_senescent)) %>% 
  ggplot() +
  geom_line(aes(x = year, y = DOC_annual_no_senescence),
            color ="#266A25",
            size = 3) +
  geom_line(aes(x = year, y = DOC_annual_w_senescence), 
            color = "#BD9C3D",
            size = 3) +
  labs(x = "") +
  ylab(expression(DOC~Production~(Gg~C ~ yr^{-1})))+
  scale_x_continuous(expand = c(0,0)) +
  scale_y_continuous(breaks = c(0,5,10,15), limits = c(0,15)) +
  theme(panel.background = element_rect(fill = "white", color = "black", size = 1.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = margin(1,1,1,1, "cm"),
        strip.background = element_rect(fill = "white", color = "black"),
        legend.key = element_rect(fill = "white"),
        legend.text = element_text(size = 20),
        legend.key.height = unit(0.8, "inch"),
        legend.key.width = unit(0.4, "inch"),
        legend.title = element_text(size = 24),
        axis.text = element_text(size = 30, color = "black"),
        axis.title = element_text(size = 25),
        text = element_text(family = "Times")) 




```

# Annual DOC Production: Boxplot, Senescence vs. No Senescence

```{r}

library(ggpubr)

annual_DOC_production <- monthly_DOC_production %>% 
  group_by(year) %>% 
  summarize(biomass_C = sum(total_biomass/1000/1000*0.3),
            DOC_annual_no_senescence = sum(DOC_production_all_mature),
            DOC_annual_w_senescence = sum(DOC_production_mature_senescent)) %>% 
  ungroup() %>% 
  select(year, DOC_annual_no_senescence, DOC_annual_w_senescence) %>% 
  pivot_longer(!year, names_to = "w_wout_senescence", values_to = "annual_DOC_production") %>%
  mutate(senescence = case_when(
    w_wout_senescence == "DOC_annual_no_senescence" ~ "-Senescence",
    w_wout_senescence == "DOC_annual_w_senescence" ~ "+Senescence"
  ))



annual_DOC_production_boxplot <- annual_DOC_production %>% 
  ggplot() +
  geom_boxplot(aes(y = annual_DOC_production, x = senescence, fill = senescence)) +
   geom_point(aes(x = senescence, y = annual_DOC_production, color = senescence),
             position = position_jitterdodge()) +
  ylab(expression(DOC~Production~(Gg~C ~ yr^{-1})))+
  labs(x = "",
       fill = "") +
  scale_fill_manual(values = c("#266A25","#BD9C3D")) +
  scale_color_manual(values = c("darkgreen","darkgoldenrod")) +
  theme(panel.background = element_rect(fill = "white", 
                                        color = "black", 
                                        size = 1.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = margin(1,1,1,1, "cm"),
        strip.background = element_rect(fill = "white", 
                                        color = "black"),
        legend.key = element_rect(fill = "white"),
        legend.position = "none",
        legend.text = element_text(size = 15),
        legend.title = element_blank(),
        axis.text = element_text(size = 20, 
                                 color = "black"),
        axis.title = element_text(size = 24),
        text = element_text(family = "Times"))


```
# ANOVA DOC production w and w/out senescnece

```{r}


t.test_senescence_DOC_production <- t.test(data = annual_DOC_production, annual_DOC_production ~ senescence)

t.test_senescence_DOC_production)
```



# Percent Senescent

```{r}

percent_senescent <- biomass_phys %>%  
  ggplot(aes(x = month_name,
             y = percent_senescent)) +
  geom_point(size = 4) +
  labs(y = "Senescent Biomass (% Total)",
       x = "") +
  scale_y_continuous(breaks = c(0,25,50,75,100), limits = c(0,100)) +
  theme(panel.background = element_rect(fill = "white", color = "black", size = 1.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = margin(1,1,1,1, "cm"),
        strip.background = element_rect(fill = "white", color = "black"),
        legend.key = element_rect(fill = "white"),
        legend.text = element_text(size = 20),
        legend.key.height = unit(0.8, "inch"),
        legend.key.width = unit(0.4, "inch"),
        legend.title = element_text(size = 20),
        axis.text = element_text(size = 20, color = "black"),
        axis.text.x = element_text(angle = 45, vjust = 0.6),
        axis.title = element_text(size = 24),
        text = element_text(family = "Times")) 

total_biomass <- biomass_phys %>%  
  ggplot(aes(x = month_name,
             y = total_biomass/1000/1000,
             group = year)) +
  geom_point(size = 4) +
  geom_line(aes(x = month_name, y = total_biomass/1000/1000),
            orientation = "x") +
  labs(y = "Total Biomass (Gg WW)",
       x = "") +
  scale_y_continuous(breaks = c(0,100,200,300,400), limits = c(0,400)) +
  theme(panel.background = element_rect(fill = "white", color = "black", size = 1.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = margin(1,1,1,1, "cm"),
        strip.background = element_rect(fill = "white", color = "black"),
        legend.key = element_rect(fill = "white"),
        legend.text = element_text(size = 20),
        legend.key.height = unit(0.8, "inch"),
        legend.key.width = unit(0.4, "inch"),
        legend.title = element_text(size = 20),
        axis.text = element_text(size = 20, color = "black"),
        axis.text.x = element_text(angle = 45, vjust = 0.6),
        axis.title = element_text(size = 24),
        text = element_text(family = "Times"))
  
monthly_DOC_production_p <- monthly_DOC_production %>%  
  ggplot() +
  geom_point(aes(x = month_name,
             y = DOC_production_mature_senescent),
             size = 4) +
  labs(x = "") +
  ylab(expression(DOC~Production~(Gg~C ~ month^{-1})))+
  scale_y_continuous(breaks = c(0,1,2,3), limits = c(0,3)) +
  theme(panel.background = element_rect(fill = "white", color = "black", size = 1.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = margin(1,1,1,1, "cm"),
        strip.background = element_rect(fill = "white", color = "black"),
        legend.key = element_rect(fill = "white"),
        legend.text = element_text(size = 20),
        legend.key.height = unit(0.8, "inch"),
        legend.key.width = unit(0.4, "inch"),
        legend.title = element_text(size = 20),
        axis.text = element_text(size = 20, color = "black"),
        axis.text.x = element_text(angle = 45, vjust = 0.6),
        axis.title = element_text(size = 24),
        text = element_text(family = "Times")) 


percent_biomass <- monthly_DOC_production %>%  
  ggplot(aes(x = month_name,
             y = percent_biomass,
             group = year)) +
  geom_point(size = 4) +
  labs(y = "Monthyl DOC Production (%Biomass C)",
       x = "") +
  scale_y_continuous(breaks = c(0,10,20,30,40), limits = c(0,40)) +
  theme(panel.background = element_rect(fill = "white", color = "black", size = 1.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = margin(1,1,1,1, "cm"),
        strip.background = element_rect(fill = "white", color = "black"),
        legend.key = element_rect(fill = "white"),
        legend.text = element_text(size = 20),
        legend.key.height = unit(0.8, "inch"),
        legend.key.width = unit(0.4, "inch"),
        legend.title = element_text(size = 20),
        axis.text = element_text(size = 20, color = "black"),
        axis.text.x = element_text(angle = 45, vjust = 0.6),
        axis.title = element_text(size = 24),
        text = element_text(family = "Times"))

monthly_DOC_production %>% 
  group_by(year) %>% 
  mutate(DOC_annual_no_senescence = sum(DOC_production_all_mature),
         DOC_annual_w_senescence = sum(DOC_production_mature_senescent),
         DOC_annual_senescence = sum(DOC_production_senescent)) %>% 
  mutate(senescence_DOC_total_fraction = DOC_annual_senescence/DOC_annual_w_senescence,
         fold_change = DOC_annual_w_senescence/DOC_annual_no_senescence) %>% 
  ungroup() %>% 
  summarise(mean_senescence_fraction = mean(senescence_DOC_total_fraction),
            sd_senescece_fraction = sd(senescence_DOC_total_fraction),
            mean_fold_change = mean(fold_change),
            sd_fold_change = sd(fold_change))

  
monthyl_DOC_production_vs_biomass_plot <- monthly_DOC_production %>%  
  ggplot() +
  geom_point(aes(x = total_biomass/1000/1000,
             y = DOC_production_mature_senescent),
             size = 4) +
  labs(x = "Total Biomass (GgC Wet Weight)") +
  ylab(expression(DOC~Production~(Gg~C ~ month^{-1})))+
  scale_y_continuous(breaks = c(0,1,2,3), limits = c(0,3)) +
  theme(panel.background = element_rect(fill = "white", color = "black", size = 1.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = margin(1,1,1,1, "cm"),
        strip.background = element_rect(fill = "white", color = "black"),
        legend.key = element_rect(fill = "white"),
        legend.text = element_text(size = 20),
        legend.key.height = unit(0.8, "inch"),
        legend.key.width = unit(0.4, "inch"),
        legend.title = element_text(size = 20),
        axis.text = element_text(size = 20, color = "black"),
        axis.title = element_text(size = 24),
        text = element_text(family = "Times")) 

DOC_biomass_lm <- lmodel2(data = monthly_DOC_production, DOC_production_mature_senescent~total_biomass)

DOC_biomass_lm

```

# Average Standing biomass relative to maximum 

```{r}

biomass_phys %>% 
  select(total_biomass, month_name, year) %>% 
  mutate(percent_max_biomass = total_biomass / max(total_biomass) * 100) %>% 
  summarize(mean_percent_total_biomass = mean(percent_max_biomass),
            sd_mean_percent_biomass = sd(percent_max_biomass),
            median_percent_total_biomass = median(percent_max_biomass))





```





# Biomass min max

```{r}
min(biomass_phys$total_biomass)

max(biomass_phys$total_biomass)


max(monthly_DOC_production$percent_biomass)

min(monthly_DOC_production$percent_biomass)

```


# Monthyl DOC Production x Monthyl Biomass 


```{r}

monthly_DOC_production %>% 
  ggplot(x = total_biomass, y = DOC_production_mature_senescent) +
  geom_point()




```


# Bootstrapping: Senescent DOCex 


```{r}


senescent_kelp_DOC <-  MP_DOC_NPP_phys_env_sum %>% 
  filter(age_d > 50,
         flag != 2) %>% 
  select(DOC_umolC_g_hr)

median(senescent_kelp_DOC$DOC_umolC_g_hr) # 6.5

library(boot)

boot.median <- function(x,i) {
  median(x[i])
}

bootSenescentDOC <- boot(senescent_kelp_DOC$DOC_umolC_g_hr, boot.median, R = 100000)

bootSenescentDOC

boot.ci(bootSenescentDOC, type = "perc") # 95% CI = 4.6 - 12.7 umol C g hr

```


# Bootstrapping: Mature Dark DOC


```{r}


mature_DARK_DOC <-  MP_DOC_NPP_phys_env_sum %>% 
  filter(age_d < 50,
         flag != 2,
         PAR == 0) %>% 
  select(DOC_umolC_g_hr)

hist(mature_DARK_DOC$DOC_umolC_g_hr,  breaks = 10)

median(mature_DARK_DOC$DOC_umolC_g_hr) # 0.7
mean(mature_DARK_DOC$DOC_umolC_g_hr) # 0.9

library(boot)

boot.median <- function(x,i) {
  median(x[i])
}

bootMatureDOC_dark <- boot(mature_DARK_DOC$DOC_umolC_g_hr, boot.median, R = 100000)

bootMatureDOC_dark

boot.ci(bootMatureDOC_dark, type = "perc") # 95% CI = 0.2 - 1.3 umol C g hr

```


# Bootstrapping: Mature Light DOC


```{r}


mature_LIGHT_DOC <-  MP_DOC_NPP_phys_env_sum %>% 
  filter(age_d < 50,
         flag != 2,
         PAR > 300) %>% 
  select(DOC_umolC_g_hr)

hist(mature_LIGHT_DOC$DOC_umolC_g_hr,  breaks = 10)

median(mature_LIGHT_DOC$DOC_umolC_g_hr) # 3.2
mean(mature_LIGHT_DOC$DOC_umolC_g_hr) # 3.3

library(boot)

boot.median <- function(x,i) {
  median(x[i])
}

bootmature_LIGHT_DOC <- boot(mature_LIGHT_DOC$DOC_umolC_g_hr, boot.median, R = 100000)

bootmature_LIGHT_DOC # median +- se = 3.2 +- 0.3

boot.ci(bootmature_LIGHT_DOC, type = "perc") # 95% CI = 2.6 - 3.8 umol C g hr

```


# CA Wide DOC Production Rates

```{r}

monthly_DOC_production <- biomass_phys %>% 
  mutate(total_biomass = total_biomass*1000*0.12,
         senescent_biomass = senescent_biomass*1000*0.12,
         mature_biomass = mature_biomass*1000*0.12) %>% 
  mutate(DOC_production_all_mature = 
           (((total_biomass * (0.7*12*30))/1000/1000*12)/1000/1000/1000) + 
           (((total_biomass * (3.2*12*30))/1000/1000*12)/1000/1000/1000),
         
         DOC_production_all_mature_025 = 
           (((total_biomass * (0.2*12*30))/1000/1000*12)/1000/1000/1000) + 
           (((total_biomass * (2.6*12*30))/1000/1000*12)/1000/1000/1000),
         
         DOC_production_all_mature_975 = 
           (((total_biomass * (1.3*12*30))/1000/1000*12)/1000/1000/1000) + 
           (((total_biomass * (3.8*12*30))/1000/1000*12)/1000/1000/1000),
         
         DOC_production_senescent = 
           senescent_biomass * (((6.5*24*30))/1000/1000*12)/1000/1000/1000,
         
         DOC_production_senescent_025 = 
           senescent_biomass * (((4.6*24*30))/1000/1000*12)/1000/1000/1000,
         
         DOC_production_senescent_975 = 
           senescent_biomass * (((12.7*24*30))/1000/1000*12)/1000/1000/1000,
         
         DOC_production_mature = 
           (((mature_biomass * (0.7*12*30))/1000/1000*12)/1000/1000/1000) + 
           (((mature_biomass * (3.2*12*30))/1000/1000*12)/1000/1000/1000),
         
         DOC_production_mature_025 = 
           (((mature_biomass * (0.2*12*30))/1000/1000*12)/1000/1000/1000) + 
           (((mature_biomass* (2.6*12*30))/1000/1000*12)/1000/1000/1000),
         
         DOC_production_mature_975 = 
           (((mature_biomass * (1.3*12*30))/1000/1000*12)/1000/1000/1000) + 
           (((mature_biomass * (3.8*12*30))/1000/1000*12)/1000/1000/1000),
         
         
         DOC_production_mature_senescent = 
           DOC_production_senescent + DOC_production_mature,
         
         DOC_production_mature_senescent_025 = 
           DOC_production_senescent_025 + DOC_production_mature_025, 
         
         DOC_production_mature_senescent_975 = 
           DOC_production_senescent_975 + DOC_production_mature_975,
         
         senescence_percent_DOC = 
           (DOC_production_senescent / DOC_production_mature_senescent)*100)


doc_production_first_look <- monthly_DOC_production %>% 
  group_by(year) %>% 
  summarize(biomass_C = sum(total_biomass/1000/1000*0.3),
            DOC_annual_no_senescence = sum(DOC_production_all_mature),
            DOC_annual_no_senescence_025 = sum(DOC_production_all_mature_025),
            DOC_annual_no_senescence_975 = sum(DOC_production_all_mature_975),
            DOC_annual_w_senescence = sum(DOC_production_mature_senescent),
            DOC_annual_w_senescence_025 = sum(DOC_production_mature_senescent_025),
            DOC_annual_w_senescence_975 = sum(DOC_production_mature_senescent_975)) %>% 
  ggplot() +
  geom_line(aes(x = year, y = DOC_annual_no_senescence),
            color ="#266A25",
            size = 3) +
  geom_line(aes(x = year, y = DOC_annual_no_senescence_025),
            color ="#266A25",
            size = 1.5,
            linetype = "dotted") +
  geom_line(aes(x = year, y = DOC_annual_no_senescence_975),
            color ="#266A25",
            size = 1.5,
            linetype = "dotted") +
  geom_line(aes(x = year, y = DOC_annual_w_senescence), 
            color = "#BD9C3D",
            size = 3) +
  geom_line(aes(x = year, y = DOC_annual_w_senescence_025), 
            color = "#BD9C3D",
            size = 1.5,
            linetype = "dotted") +
  geom_line(aes(x = year, y = DOC_annual_w_senescence_975), 
            color = "#BD9C3D",
            size = 1,
            linetype = "dotted") +
  labs(x = "") +
  ylab(expression(DOC~Production~(Gg~C ~ yr^{-1})))+
  scale_x_continuous(expand = c(0,0)) +
  scale_y_continuous(breaks = c(0,5,10,15), limits = c(0,15)) +
  theme(panel.background = element_rect(fill = "white", color = "black", size = 1.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = margin(1,1,1,1, "cm"),
        strip.background = element_rect(fill = "white", color = "black"),
        legend.key = element_rect(fill = "white"),
        legend.text = element_text(size = 20),
        legend.key.height = unit(0.8, "inch"),
        legend.key.width = unit(0.4, "inch"),
        legend.title = element_text(size = 24),
        axis.text = element_text(size = 30, color = "black"),
        axis.title = element_text(size = 25),
        text = element_text(family = "Times")) 




```

# Annual DOC Production

```{r}
doc_production_annual <- monthly_DOC_production %>% 
  group_by(year) %>% 
  summarize(biomass_C = sum(total_biomass/1000/1000*0.3),
            DOC_annual_no_senescence = sum(DOC_production_all_mature),
            DOC_annual_no_senescence_025 = sum(DOC_production_all_mature_025),
            DOC_annual_no_senescence_975 = sum(DOC_production_all_mature_975),
            DOC_annual_w_senescence = sum(DOC_production_mature_senescent),
            DOC_annual_w_senescence_025 = sum(DOC_production_mature_senescent_025),
            DOC_annual_w_senescence_975 = sum(DOC_production_mature_senescent_975),
            DOC_annual_senescence = sum(DOC_production_senescent),
            percent_senescence = DOC_annual_senescence/DOC_annual_w_senescence,
            fold_change = DOC_annual_w_senescence/DOC_annual_no_senescence)


mean(doc_production_annual$percent_senescence)

sd(doc_production_annual$percent_senescence)
 
# Summary stats annual DOC production with senescence 
 
mean(doc_production_annual$DOC_annual_w_senescence)

sd(doc_production_annual$DOC_annual_w_senescence)

# Summary stats annual DOC production without senescence 

mean(doc_production_annual$DOC_annual_no_senescence)

sd(doc_production_annual$DOC_annual_no_senescence)

# Fold change with and without considering senescence

mean(doc_production_annual$fold_change)

sd

```

# Biomass Physiology Summary statistics

```{r}

biomass_phys %>% 
  mutate(season = case_when(
         month %in% c(12,1,2) ~ "Winter",
         month %in% c(3,4,5) ~ "Spring",
         month %in% c(6,7,8) ~ "Summer",
         month %in% c(9,10,11) ~ "Fall"
         )) %>% 
  group_by(season) %>% 
  summarize(mean_biomass = mean(total_biomass)/1000/1000,
            sd_biomass = sd(total_biomass)/1000/1000,
            mean_percent_senescent = mean(percent_senescent),
            sd_percent_senescent = sd(percent_senescent))



```

# Biomass January vs August 
```{r}

biomass_january <- biomass_phys$total_biomass[biomass_phys$month == 1]

  
biomass_august <- biomass_phys$total_biomass[biomass_phys$month == 8]


plot(biomass_january,biomass_august )


```


