---
title: "Kelp Metabolites"
output: html_document
date: "2025-08-01"
---


```{r setup, include=FALSE, echo=F, warning=F, message=F}
knitr::opts_chunk$set(echo = TRUE, message = F, echo = F, warning = F)
```

```{r, include=FALSE, echo=F, warning=F, message=F}



library(tidyverse)
library(lmodel2)
library(ggplot2)
library(readxl)
library(kableExtra)
library(scales)
library(factoextra)
library(mgcv)
library(janitor)
library(broom)
library(here)
library(rstatix)
library(ggpubr)
library(vegan)
library(ggbump)
library(RColorBrewer)
library(scico)
library(sicegar)
library(plotly)

library(treemap)

```


# Negative Mode

# Load in metadata feature quant table, and SIRIUS formula & compound class

```{r}

metadata_neg <- read_csv(here("Data", "metabolites", "NEG", "MP_Metabolites_Samples_Metadata_Negative.csv"))

fqt_neg <- read_csv(here("Data", "metabolites", "NEG","240910_Chance_kelp_GNPS_NEG_V2_quant.csv"))

canopus_formula_class_neg <- read_csv(here("Data", "metabolites", "NEG","canopus_formula_summary.csv"))

SIRIUS_formula_highscore <- read_csv(here("Data", "metabolites", "NEG","formula_identifications.csv"))

#SIRIUS_formula_highscore <- SIRIUS_formula_highscore %>% 
 # filter(SiriusScoreNormalized > 0.8)

```

# Merge metadata and fqt

```{r}

# Remove "Peak Area" from column names to match metadata 


fqt_neg <- fqt_neg %>%
  rename_all(~ gsub(" Peak area", "", .x))


# Reshape fqt, make row ID the rowname, make long based on column name 

fqt_neg_long <- fqt_neg %>% 
  select(`row ID`,`230823_NEG_B0.mzML`:`Chance_pooled_QC_NEG_4.mzML`) %>% 
  pivot_longer(!'row ID', names_to = "filename", values_to = "peak_area")

# Merge long fqt with metadata and remove non samples or blanks

fqt_long_metadata <- merge(fqt_neg_long, metadata_neg, by = "filename") %>% 
  filter(ATTRIBUTE_source %in% c("Ambient", "Kelp", "Blank", "LCMS Water"))




```

# Filter feature table 

```{r}

# Remove background features (found in process and analytical blanks)

filtered_ids <- fqt_long_metadata %>%
  filter(ATTRIBUTE_source %in% c("Blank", "LCMS Water") & peak_area > 0) %>%
  pull(`row ID`)

fqt_long_metadata_blanked <- fqt_long_metadata %>% 
  filter(! `row ID` %in% filtered_ids) %>% 
  filter(ATTRIBUTE_source %in% c("Ambient", "Kelp"))

# Remove transient features (found less than 3 times)


fqt_long_metadata_blanked_no_transient <- fqt_long_metadata_blanked[fqt_long_metadata_blanked$`row ID` %in% names(which(table(fqt_long_metadata_blanked$`row ID`) > 2)), ]


# Filter newly produced DOM (three the XIC peak area relative to the ambient water)


produced_DOM_ids <- fqt_long_metadata_blanked_no_transient %>%
  group_by(`row ID`,ATTRIBUTE_sample_date) %>% 
  filter(peak_area < 3*peak_area[ATTRIBUTE_blade == 0]) %>% 
  pull(`row ID`)

fqt_long_metadata_blanked_no_transient_produced_DOM <- fqt_long_metadata_blanked_no_transient %>% 
  filter(! `row ID` %in% produced_DOM_ids) %>% 
  filter(ATTRIBUTE_source == "Kelp")



```

# Merge filtered quant table with canopus compounds class 

```{r}

canopus_formula_class_neg <- canopus_formula_class_neg %>% 
  mutate('row ID' = mappingFeatureId) %>% 
  select(`row ID`, molecularFormula,`ClassyFire#superclass`, `ClassyFire#class`,`ClassyFire#subclass`, `ClassyFire#most specific class`, `ClassyFire#class Probability`, `ClassyFire#most specific class Probability`)

canopus_formula_class_neg_high_class_score <- canopus_formula_class_neg %>% 
  select(-`ClassyFire#class Probability`)

#filter(`ClassyFire#class Probability` >= 0.8) %>%

fqt_class_metadata_long <- merge(fqt_long_metadata_blanked_no_transient_produced_DOM, canopus_formula_class_neg_high_class_score, by = "row ID")

length(unique(fqt_class_metadata_long$`row ID`)) #3932 exudate features

# Metabolomics Feature Table for Corromics app

fqt_class_metadata_long_corromics <- fqt_class_metadata_long %>% 
  mutate(corromics_feature_ID = paste(`row ID`, `ClassyFire#superclass`,`ClassyFire#class`,`ClassyFire#subclass`,
        sep = "_")) %>% 
  select(corromics_feature_ID,
         filename,
         peak_area)


fqt_class_metadata_long_corromics_wide <- fqt_class_metadata_long_corromics %>% 
  pivot_wider(names_from = filename, 
              values_from = peak_area)

fqt_class_metadata_long_corromics_wide <- fqt_class_metadata_long_corromics_wide %>% 
  select(-`240901_NEG_B1.mzML`)

write.csv(fqt_class_metadata_long_corromics_wide, "corromics_metabolites.csv", row.names = FALSE)


```

# Create a read table equivalent to 16s, 


```{r}

columns_to_modify <- 18:63


fqt_class_metadata_read_table <- fqt_class_metadata_long %>% 
  pivot_wider(names_from = filename, values_from = peak_area) 



fqt_class_metadata_read_table <- fqt_class_metadata_read_table %>%
          mutate(across(19:64, ~replace_na(.x, 0)))



# Make rownames and then select only peakareas to calculate relative abundances 

fqt_class_metadata_read_table <- fqt_class_metadata_read_table %>% 
  mutate(rownumber = 1:nrow(fqt_class_metadata_read_table))

fqt_class_metadata_read_table_RA <- fqt_class_metadata_read_table %>% 
  column_to_rownames(var = "rownumber") %>% 
  select(`240616_NEG_B4.mzML`:`230905_NEG_B6.mzML`) %>% 
  select(-`240901_NEG_B1.mzML`)

#%>% select(-c(`230823_NEG_B1.mzML`,`230823_NEG_B2.mzML`,`230823_NEG_B3.mzML`))
  
# Calculate relative peak areas 

fqt_class_metadata_read_table_RA <- as.data.frame(lapply(fqt_class_metadata_read_table_RA[1:45], function(x) {(x/ sum(x))}))


fqt_class_metadata_read_table_RA_rowname_column <- fqt_class_metadata_read_table_RA %>% 
  rownames_to_column(var = "rownumber")

# Create complimentary metadata file for relative abundnace dataframe to be merged with 

fqt_class_metadata_read_table_rownumber <- fqt_class_metadata_read_table %>% 
  select(`row ID`:`ClassyFire#most specific class`, rownumber)


# Create metadata file wit relative abundnaces of each sample compounds class 

fqt_class_metadata_RA <- merge(fqt_class_metadata_read_table_rownumber,fqt_class_metadata_read_table_RA_rowname_column, by = "rownumber")

fqt_class_metadata_RA <- fqt_class_metadata_RA %>%
  rename_all(~ gsub("X2", "2", .x))

fqt_class_metadata_RA$smooshedclass <- do.call(paste, c(fqt_class_metadata_RA[c("ClassyFire#superclass", "ClassyFire#class", "ClassyFire#subclass", "ClassyFire#most specific class")], sep="_"))



```


# PREPARE data for PCoA using features ids instead of grouped specific class 

```{r}
fqt_class_metadata_RA_PCOA_1 <- fqt_class_metadata_RA %>% 
  select(`row ID`, `240616_NEG_B4.mzML`:`230905_NEG_B6.mzML`)

fqt_class_metadata_RA_PCOA_2  <- fqt_class_metadata_RA_PCOA_1 %>% 
pivot_longer(!c(`row ID`), names_to = "filename", values_to = "relative_peak_area")
 
fqt_class_metadata_RA_PCOA_3 <- merge(metadata_neg,fqt_class_metadata_RA_PCOA_2, by = "filename")

fqt_class_metadata_RA_PCOA_4 <- fqt_class_metadata_RA_PCOA_3 %>% 
  select(ATTRIBUTE_sample_date, ATTRIBUTE_phys_state, ATTRIBUTE_season, ATTRIBUTE_age_d, ATTRIBUTE_blade, `row ID`, relative_peak_area) %>% 
  unique() %>% 
  filter(ATTRIBUTE_season != "September")


fqt_class_metadata_RA_PCOA_5 <- fqt_class_metadata_RA_PCOA_4 %>% 
  pivot_wider(names_from = `row ID`, values_from = relative_peak_area, values_fn = sum)
  


fqt_class_metadata_RA_PCOA_5 <- fqt_class_metadata_RA_PCOA_5[, colSums(fqt_class_metadata_RA_PCOA_5 != 0) > 0]


ft_metab_numeric <- fqt_class_metadata_RA_PCOA_5[1:45,6:3707]


ft_metab_numeric_angtransformed <- asin(sqrt(ft_metab_numeric))


pos_metab_numeric_ft_z_scored <- as.data.frame(scale(ft_metab_numeric_angtransformed, center = FALSE, scale = TRUE))


bray_dist_matrix_ft <- vegdist(pos_metab_numeric_ft_z_scored, method = "bray")

PCoA_metab_ft  <-  cmdscale(bray_dist_matrix_ft)

str(PCoA_metab_ft)

head(PCoA_metab_ft)

colnames(PCoA_metab_ft) <- c("pcoa1", "pcoa2") 

PCoA_metab_ft <- PCoA_metab_ft%>%  
  as_tibble(rownames = "samples")

# Getting eigenvalues 

PCoA_metab_ft_eig  <-  cmdscale(bray_dist_matrix_ft, eig = TRUE, add = TRUE)

positions_ft <- PCoA_metab_ft_eig$points

head(positions_ft)

colnames(PCoA_metab_ft_eig$points) <- c("pcoa1", "pcoa2") 

100* PCoA_metab_ft_eig$eig / sum(PCoA_metab_ft_eig$eig)


# Merge with metadata 

fqt_class_metadata_RA_PCOA_5_rownmaes <- fqt_class_metadata_RA_PCOA_5 %>% 
  mutate(samples = 1:45)



PCoA_NEG_metab_metadata_ft <- merge(PCoA_metab_ft, fqt_class_metadata_RA_PCOA_5_rownmaes, by = "samples")


#Plot PCo 1 and PCo 2 by developmental stage

pcoa_neg_plot <- PCoA_NEG_metab_metadata_ft %>% 
  ggplot(aes(x = pcoa1,  y = pcoa2)) +
  geom_point(aes(shape = ATTRIBUTE_season, fill = ATTRIBUTE_phys_state),
             size = 5,
             alpha = 0.7) +
  scale_color_manual(values = c("black", "black")) +
  scale_fill_manual(values = c("#06558B", "#AA4613")) +
  scale_shape_manual(values = c(21,24)) +
  scale_y_continuous(labels = label_number(accuracy = 0.1)) + 
  labs(x = "PCo 1 (19.8%)",
       y = "PCo 2 (12.9%)") +
   theme(panel.background = element_rect(fill = "white", color = "black", size = 1.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = margin(1,1,1,1, "cm"),
        legend.key = element_rect(fill = "white",color = NA),
        legend.text = element_text(size = 20),
        legend.position = "right",
        legend.title = element_blank(),
        axis.text = element_text(size = 15, color = "black"),
        axis.title = element_text(size = 20),
        text = element_text(family = "Helvetica")) +
  stat_ellipse(aes(x = pcoa1,  
                   y = pcoa2, 
                   color = ATTRIBUTE_phys_state,
                   fill = ATTRIBUTE_phys_state),
               geom = "polygon", alpha = 0.2,
               level = 0.95) +
  guides(shape = guide_legend(override.aes = list(size = 5)))


# Permanova


# Variance stabilize and z-score the sample centric metabolites relative adundance data

POS_metab_c_4_permanova_ft <- as.data.frame(scale(asin(sqrt(fqt_class_metadata_RA_PCOA_5[1:45,6:3707])), scale = TRUE, center = FALSE))
  

# PERMANOVA of differences in metabolite composition by physiological state


POS_metab_phys_state_adonis_ft <- adonis2(POS_metab_c_4_permanova_ft~ATTRIBUTE_phys_state, data = fqt_class_metadata_RA_PCOA_5[1:45,], method = "bray")

POS_metab_phys_state_adonis_ft # R2 = 0.17 p = 0.001 F = 9.02


# PERMANOVA of differences in metabolite composition by season


POS_metab_season_adonis_ft <- adonis2(POS_metab_c_4_permanova_ft~ATTRIBUTE_season, data = fqt_class_metadata_RA_PCOA_5[1:45,], method = "bray")

POS_metab_season_adonis_ft # R2 = 0.12 p = 0.001 F = 5.6


# Run betadisper to measure if variance between physiolgical stage is sig different

bd_phys_state <- betadisper(bray_dist_matrix_ft, fqt_class_metadata_RA_PCOA_5$ATTRIBUTE_phys_state)

bd_phys_state

anova(bd_phys_state) # P = 0.01 significantly different variance between phys state

permutest(bd_phys_state) 



# Run betadisper to measure if variance between season is sig different

bd_season <- betadisper(bray_dist_matrix_ft, fqt_class_metadata_RA_PCOA_5$ATTRIBUTE_season)


permutest(bd_season) # P = 0.131 not significantly different variance between season

```


# Combine high-score SIRIUS forumlas with dataset


```{r}

SIRIUS_formulas <- SIRIUS_formula_highscore %>% 
  mutate('row ID' = mappingFeatureId) %>% 
  select(`row ID`, molecularFormula, SiriusScoreNormalized)


fqt_class_metadata_formula <- merge(SIRIUS_formulas, fqt_class_metadata_long, by = 'row ID')

fqt_class_metadata_formula <- fqt_class_metadata_formula %>% 
  select(-molecularFormula.y) %>% 
  mutate(molecularFormula = molecularFormula.x) %>% 
  select(-molecularFormula.x)

```


## Seperate out molecular fomrula into elements and ratios 


```{r}

library(CHNOSZ)

formulas_vector <- fqt_class_metadata_formula$molecularFormula


formulas <- makeup(formulas_vector, count.zero = TRUE)

df <- data.frame(matrix(unlist(formulas), nrow=length(formulas), byrow=TRUE), stringsAsFactors=FALSE)

element_column_names <- c("As","B","Br","C","Cl","F","H","I","N","O","P","S","Se","Si")

colnames(df) <- element_column_names

df_stoichiometry_molecular_formulas <- df %>% 
  mutate(molecularFormula = formulas_vector)


```


## Merge new Formula dataframs with parsed elements and stoichiometry with metadata 


```{r}

fqt_class_metadata_formula_stoichiometry <- merge(fqt_class_metadata_formula, df_stoichiometry_molecular_formulas, by = "molecularFormula")

fqt_class_metadata_formula_stoichiometry_unique <- fqt_class_metadata_formula_stoichiometry %>%
  distinct() %>% 
  filter(ATTRIBUTE_sample_date != "9/1/24")



```

## Calculate weighted C:N stoichiometries

```{r}

molecular_stoichiometryCN <- fqt_class_metadata_formula_stoichiometry_unique %>% 
  group_by(ATTRIBUTE_season, ATTRIBUTE_blade, ATTRIBUTE_age_d) %>% 
  mutate(weighted_CN = (sum(C*peak_area))/(sum(N*peak_area))) %>% 
  select(filename, ATTRIBUTE_season, ATTRIBUTE_tissue_CN, ATTRIBUTE_age_d, ATTRIBUTE_blade, ATTRIBUTE_phys_state, weighted_CN) %>% 
  unique()

write_csv(molecular_stoichiometryCN, "/Users/chanceenglish/Desktop/Lab Shiz/ARPA-e/Giant_Kelp_DOC/Data/metabolites/NEG/metabolite_weighted_CN_NEG.csv")

molecular_stoichiometryCN <- read_csv(here("Data", "metabolites", "NEG","metabolite_weighted_CN_NEG.csv"))

```

## Plot weighted stoichiometries over time between seasons 

```{r}

molecular_stoichiometryCN %>% 
  group_by(ATTRIBUTE_season, ATTRIBUTE_age_d) %>% 
  summarize(mean_CN = mean(weighted_CN), sd_CN = sd(weighted_CN)) %>% 
  ggplot(aes(x = ATTRIBUTE_age_d, y = mean_CN, color = ATTRIBUTE_season)) +
  geom_point(size = 4) +
  geom_errorbar(aes(ymin = mean_CN - sd_CN, ymax = mean_CN + sd_CN)) +
  labs(x = "Age (d)",
       y = "Weighted C:N") +
  theme(panel.background = element_rect(fill = "white", color = "black", size = 1.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = margin(1,1,1,1, "cm"),
        strip.background = element_rect(fill = "white", color = "black"),
        legend.key = element_rect(fill = "white"),
        legend.text = element_text(size = 15),
        legend.key.height = unit(0.5, "inch"),
        legend.key.width = unit(0.4, "inch"),
        legend.title = element_text(size = 15),
        axis.text = element_text(size = 15, color = "black"),
        axis.title = element_text(size = 15),
        text = element_text(family = "Times")) 


CNexo_CNtisssue_p <- molecular_stoichiometryCN %>% 
  ggplot(aes(x = ATTRIBUTE_tissue_CN, 
             y = weighted_CN, 
             shape = ATTRIBUTE_season, color = ATTRIBUTE_age_d)) +
  geom_point(size = 4,
             position = position_dodge(width = 0.1)) +
  geom_smooth(method = "lm",se = F, color = "black", size = 1) +
  labs(x = "Tissue Stoichiometry (C:N)",
       y = "Exometabolite Stoichiometry (C:N)",
      color = "Age (d)",
      shape = NULL) +
  coord_cartesian(expand = c(0,0)) +
  scico::scale_color_scico(palette = "vik", breaks = c(0,25,50,75,100)) +
  scale_y_continuous(breaks = c(0,5,10,15,20,25,30), limits = c(0,30)) +
  scale_x_continuous(breaks = c(0,5,10,15,20,25,30,35,40,45), limits = c(0,45)) +
  theme(panel.background = element_rect(fill = "white", color = "black", size = 1.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = margin(1,1,1,1, "cm"),
        strip.background = element_rect(fill = "white", color = "white"),
        legend.key = element_rect(fill = "white", color = NA),
        legend.text = element_text(size = 15),
        legend.key.height = unit(0.4, "inch"),
        legend.key.width = unit(0.2, "inch"),
        legend.title = element_text(size = 20),
        axis.text = element_text(size = 15, color = "black"),
        axis.title = element_text(size = 15),
        text = element_text(family = "Times")) +
  guides(shape = guide_legend(override.aes = list(size = 5)))

mature_CN_p <- molecular_stoichiometryCN %>% 
  filter(ATTRIBUTE_phys_state == "Mature") %>% 
  ggplot(aes(x = ATTRIBUTE_season, y = weighted_CN)) +
  geom_boxplot(aes(x = ATTRIBUTE_season, y = weighted_CN)) +
  geom_point(aes(x = ATTRIBUTE_season, y = weighted_CN), 
             position = position_jitterdodge(0.3)) +
  scale_y_continuous(breaks = c(5,10,15,20,25,30), limits = c(5,20)) +
  scale_fill_manual(values=c("forestgreen", "darkgoldenrod")) +
  labs(x = "",
       y = "Exometabolite C:N") +
        theme(panel.background = element_rect(fill = "white", color = "black", size = 1.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = margin(1,1,1,1, "cm"),
        strip.background = element_rect(fill = "white", color = "white"),
        legend.key = element_blank(),
        legend.text = element_text(size = 15),
        legend.key.height = unit(0.5, "inch"),
        legend.key.width = unit(0.4, "inch"),
        legend.title = element_blank(),
        axis.text.y = element_text(size = 20, color = "black"),
        axis.text.x = element_text(size = 24, color = "black"),
        axis.title = element_text(size = 24),
        text = element_text(family = "Times")) 


# T-test Mature kelp Exudate CN

molecular_stoichiometryCN_mature <- molecular_stoichiometryCN %>% 
  filter(ATTRIBUTE_phys_state == "Mature")

## Test for Normality


with(molecular_stoichiometryCN_mature, shapiro.test(weighted_CN[ATTRIBUTE_season == "Spring"])) # p = 0.4261 normal

with(molecular_stoichiometryCN_mature, shapiro.test(weighted_CN[ATTRIBUTE_season == "Summer"])) # p = 0.0538 normal

# Test for equal variances 

ftest.molecular_stoichiometryCN_mature <- var.test(weighted_CN ~ ATTRIBUTE_season, data = molecular_stoichiometryCN_mature)

# variances are equal

## Use Students t.test 

matureCN.t.test <- t.test(molecular_stoichiometryCN_mature$weighted_CN ~ molecular_stoichiometryCN_mature$ATTRIBUTE_season, var.equal = TRUE)

matureCN.t.test


# Run model II linear regressions between C:N of exudates and C:N of tissue 

molecular_stoichiometryCN_spring <- molecular_stoichiometryCN %>% 
  filter(ATTRIBUTE_season == "Spring")

spring_CNexo_CN_tissue_lm2 <- lmodel2(data = molecular_stoichiometryCN_spring,
                                          weighted_CN~ATTRIBUTE_tissue_CN)

spring_CNexo_CN_tissue_lm2 #R2 = 0.73, p < 0.001, spring ESI-

molecular_stoichiometryCN_summer <- molecular_stoichiometryCN %>% 
  filter(ATTRIBUTE_season == "Summer")

summer_CNexo_CN_tissue_lm2 <- lmodel2(data = molecular_stoichiometryCN_summer,
                                          weighted_CN~ATTRIBUTE_tissue_CN)

summer_CNexo_CN_tissue_lm2 #R2 = 0.4, p < 0.001, summer ESI-

              
```

## Calculate NOSC 

```{r}

molecular_stoichiometry_NOSC <- fqt_class_metadata_formula_stoichiometry_unique %>% 
  mutate(NOSC = (-((4*C + H - 3*N - 2*O + 5*P - 2*S)/C)+4)) %>%
  filter(NOSC != "Inf") %>% 
  group_by(ATTRIBUTE_season, ATTRIBUTE_blade, ATTRIBUTE_age_d) %>% 
  mutate(weighted_NOSC = (sum(NOSC*peak_area))/(sum(peak_area))) %>% 
  select(filename, ATTRIBUTE_season, ATTRIBUTE_tissue_CN, ATTRIBUTE_age_d, ATTRIBUTE_blade, ATTRIBUTE_phys_state, weighted_NOSC) %>% 
  unique()

molecular_stoichiometry_NOSC %>% 
  ggplot(aes(x = ATTRIBUTE_age_d, y = weighted_NOSC, colour = ATTRIBUTE_season)) +
  geom_point(size = 4) +
  labs(x = "Age_d",
       y = "Exudate NOSC") +
  theme(panel.background = element_rect(fill = "white", color = "black", size = 1.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = margin(1,1,1,1, "cm"),
        strip.background = element_rect(fill = "white", color = "black"),
        legend.key = element_rect(fill = "white",color = NA),
        legend.text = element_text(size = 15),
        legend.key.height = unit(0.5, "inch"),
        legend.key.width = unit(0.4, "inch"),
        legend.title = element_text(size = 15),
        axis.text = element_text(size = 15, color = "black"),
        axis.title = element_text(size = 15),
        text = element_text(family = "Times")) 



```

## Carbon to Br Ratios 

```{r}

molecular_stoichiometryCBr <- fqt_class_metadata_formula_stoichiometry_unique %>% 
  group_by(ATTRIBUTE_season, ATTRIBUTE_blade, ATTRIBUTE_age_d) %>% 
  mutate(weighted_CX = (sum(Br*peak_area))/((sum(C*peak_area)))) %>% 
  select(filename, ATTRIBUTE_season, ATTRIBUTE_tissue_CN, ATTRIBUTE_age_d, ATTRIBUTE_blade, ATTRIBUTE_phys_state, weighted_CX) %>% 
  unique()

cBR_p <- molecular_stoichiometryCBr %>% 
  group_by(ATTRIBUTE_season, ATTRIBUTE_age_d) %>% 
  summarize(mean_CBR = mean(weighted_CX),
            weighted_CX = weighted_CX) %>% 
  ggplot() +
  geom_point(aes(x = ATTRIBUTE_age_d, y = weighted_CX, shape = ATTRIBUTE_season)) +
  geom_point(aes(x = ATTRIBUTE_age_d, y = mean_CBR, shape = ATTRIBUTE_season), size = 4) +
  geom_line(aes(x = ATTRIBUTE_age_d, y = mean_CBR, shape = ATTRIBUTE_season ), size = 0.5) +
  labs(x = "Age (d)",
       y = "Exudate Br:C \n (Peak Area Weighted)",
       shape = NULL) +
  scale_shape_manual(values = c(1,2)) +
  scale_x_continuous(breaks = c(10,20,30,40,50,60,70,80,90), limits = c(10,90)) +
  scale_y_continuous(breaks = c(0,0.03,0.06,0.09,0.12,0.15), limits = c(0,0.15)) +
  coord_cartesian(expand = c(0,0)) +
   theme(panel.background = element_rect(fill = "white", color = "black", size = 1.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = margin(1,1,1,1, "cm"),
        strip.background = element_rect(fill = "white", color = "black"),
        legend.key = element_rect(fill = "white",color = NA),
        legend.text = element_text(size = 15),
        legend.key.height = unit(0.5, "inch"),
        legend.key.width = unit(0.4, "inch"),
        legend.title = element_blank(),
        legend.position = "right",
        axis.text = element_text(size = 15, color = "black"),
        axis.title = element_text(size = 20),
        text = element_text(family = "Helvetica")) +
   annotate("rect", xmin = 10, xmax = 50, ymin = 0, ymax = 0.15,
           alpha = .25,fill = "#06558B")  +
  annotate("rect", xmin = 50.1, xmax = 90, ymin = 0, ymax = 0.15,
           alpha = .25,fill = "#AA4613") 



# Test if significant increase in CBr between developmental stage


## Test for Normality


with(molecular_stoichiometryCBr, shapiro.test(weighted_CX[ATTRIBUTE_phys_state == "Senescent"])) # p <0.004= not-normal

with(molecular_stoichiometryCBr, shapiro.test(weighted_CX[ATTRIBUTE_phys_state == "Mature"])) # p < 0.001 = not-normal

# Weighted CBr

stoichiometryCBr_wilcox_test <- wilcox.test(molecular_stoichiometryCBr$weighted_CX[molecular_stoichiometryCBr$ATTRIBUTE_phys_state == "Mature"],molecular_stoichiometryCBr$weighted_CX[molecular_stoichiometryCBr$ATTRIBUTE_phys_state == "Senescent"])

stoichiometryCBr_wilcox_test # W = 15, p < 0.001

```

## Br Compounds 

```{r}

bromine_compounds <- fqt_class_metadata_formula_stoichiometry_unique %>% 
  filter(Br > 0, 
         peak_area > 0) %>% 
  mutate(HC = H/C,
         OC = O/C,
         Br = Br,
         Cl = Cl,
         I = I) %>% 
  filter(HC != "NaN",
         OC != "NaN",
         HC != Inf,
         OC != Inf) %>% 
  mutate(hasCl = case_when(Cl > 0 ~ "TRUE",
                           Cl == 0 ~ "FALSE"))

length(unique(bromine_compounds$`row ID`))

counts_Br <- table(bromine_compounds$Br)

proportions_Br <- as.data.frame(prop.table(counts_Br))



bromine_compounds_p <- bromine_compounds %>% 
  select(ATTRIBUTE_age_d, ATTRIBUTE_blade, ATTRIBUTE_phys_state,peak_area, HC, OC, Br) %>% 
  unique() %>% 
  ggplot(aes(x = HC, y = OC, size = peak_area, fill = ATTRIBUTE_phys_state)) +
  geom_point(shape = 21, color = "black", alpha = 0.5,
             position = position_jitter(width = 0.05, height = 0.05)) +
  labs(x = "O:C",
       y = "H:C",
       color = "",
       size = "Peak Area") +
  scale_fill_manual(values = c("#06558B","#AA4613")) +
  scale_size_continuous(range  = c(0.1, 15), 
                        limits = c(5e4, 5e7), 
                        breaks = c(5e4,5e5,5e6,5e7)) +
  scale_x_continuous(limits = c(0,1), breaks = c(0,0.2,0.4,0.6,0.8,1.0)) +
  scale_y_continuous(limits = c(0,2.5), breaks = c(0,0.5,1.0,1.5,2.0,2.5)) +
  theme(panel.background = element_rect(fill = "white", color = "black", size = 1.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = margin(1,1,1,1, "cm"),
        strip.background = element_rect(fill = "white", color = "black"),
        legend.key = element_rect(fill = "white", color = NA),
        legend.text = element_text(size = 15),
        legend.key.height = unit(0.5, "inch"),
        legend.key.width = unit(0.4, "inch"),
        legend.title = element_text(size = 15),
        axis.text = element_text(size = 15, color = "black"),
        axis.title = element_text(size = 15),
        text = element_text(family = "Helvetica")) +
  guides(fill=guide_legend(override.aes=list(size=5), title = "Developmental Stage"),
         shape=guide_legend(override.aes=list(size=5), title = "Season")) 



bromine_compounds



png(filename = "bromine_compounds_treemap_output.png", width = 800, height = 600, units = "px")

bromine_compounds %>% 
  mutate(`ClassyFire#class` = ifelse(`ClassyFire#class` == "NA", `ClassyFire#superclass`, `ClassyFire#class`)) %>% 
  treemap(vColor = "ClassyFire#superclass",
          index= c("ClassyFire#superclass","ClassyFire#class"),
          fontcolor.labels = c("transparent", "black"),
            vSize="peak_area",
            type="categorical",
          overlap.labels = 1,
          border.col = c("black", "white"),
          bg.labels = c("transparent"),
          title = "",
          border.lwds = c(2, 2))

dev.off()



```

## Carbon to Cl


```{r}

molecular_stoichiometryCCl <- fqt_class_metadata_formula_stoichiometry_unique %>% 
  group_by(ATTRIBUTE_season, ATTRIBUTE_blade, ATTRIBUTE_age_d) %>% 
  mutate(weighted_CX = (sum(Cl*peak_area))/((sum(C*peak_area)))) %>% 
  select(filename, ATTRIBUTE_season, ATTRIBUTE_tissue_CN, ATTRIBUTE_age_d, ATTRIBUTE_blade, ATTRIBUTE_phys_state, weighted_CX) %>% 
  unique()

cCl_p <- molecular_stoichiometryCCl %>% 
  group_by(ATTRIBUTE_season, ATTRIBUTE_age_d) %>% 
  summarize(mean_Cl = mean(weighted_CX),
            weighted_CX = weighted_CX) %>% 
  ggplot() +
  geom_point(aes(x = ATTRIBUTE_age_d, y = weighted_CX, shape = ATTRIBUTE_season)) +
  geom_point(aes(x = ATTRIBUTE_age_d, y = mean_Cl, shape = ATTRIBUTE_season), size = 4) +
  geom_line(aes(x = ATTRIBUTE_age_d, y = mean_Cl, shape = ATTRIBUTE_season ), size = 0.5) +
  labs(x = "Age (d)",
       y = "Exudate Cl:C \n (Peak Area Weighted)",
       shape = NULL) +
  scale_shape_manual(values = c(1,2)) +
  scale_x_continuous(breaks = c(10,20,30,40,50,60,70,80,90), limits = c(10,90)) +
  scale_y_continuous(breaks = c(0,0.03,0.06,0.09,0.12,0.15), limits = c(0,0.15)) +
  coord_cartesian(expand = c(0,0)) +
   theme(panel.background = element_rect(fill = "white", color = "black", size = 1.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = margin(1,1,1,1, "cm"),
        strip.background = element_rect(fill = "white", color = "black"),
        legend.key = element_rect(fill = "white",color = NA),
        legend.text = element_text(size = 15),
        legend.key.height = unit(0.5, "inch"),
        legend.key.width = unit(0.4, "inch"),
        legend.title = element_blank(),
        legend.position = "right",
        axis.text = element_text(size = 15, color = "black"),
        axis.title = element_text(size = 20),
        text = element_text(family = "Helvetica")) +
   annotate("rect", xmin = 10, xmax = 50, ymin = 0, ymax = 0.15,
           alpha = .25,fill = "#06558B")  +
  annotate("rect", xmin = 50.1, xmax = 90, ymin = 0, ymax = 0.15,
           alpha = .25,fill = "#AA4613") 
```


## Carbon to I


```{r}

molecular_stoichiometryCI <- fqt_class_metadata_formula_stoichiometry_unique %>% 
  group_by(ATTRIBUTE_season, ATTRIBUTE_blade, ATTRIBUTE_age_d) %>% 
  mutate(weighted_CX = (sum(I*peak_area))/((sum(C*peak_area)))) %>% 
  select(filename, ATTRIBUTE_season, ATTRIBUTE_tissue_CN, ATTRIBUTE_age_d, ATTRIBUTE_blade, ATTRIBUTE_phys_state, weighted_CX) %>% 
  unique()

cI_p <- molecular_stoichiometryCI %>% 
  group_by(ATTRIBUTE_season, ATTRIBUTE_age_d) %>% 
  summarize(mean_CI = mean(weighted_CX),
            weighted_CX = weighted_CX) %>% 
  ggplot() +
  geom_point(aes(x = ATTRIBUTE_age_d, y = weighted_CX, shape = ATTRIBUTE_season)) +
  geom_point(aes(x = ATTRIBUTE_age_d, y = mean_CI, shape = ATTRIBUTE_season), size = 4) +
  geom_line(aes(x = ATTRIBUTE_age_d, y = mean_CI, shape = ATTRIBUTE_season ), size = 0.5) +
  labs(x = "Age (d)",
       y = "Exudate I:C \n (Peak Area Weighted)",
       shape = NULL) +
  scale_shape_manual(values = c(1,2)) +
  scale_x_continuous(breaks = c(10,20,30,40,50,60,70,80,90), limits = c(10,90)) +
  scale_y_continuous(breaks = c(0,0.03,0.06,0.09,0.12,0.15), limits = c(0,0.15)) +
  coord_cartesian(expand = c(0,0)) +
   theme(panel.background = element_rect(fill = "white", color = "black", size = 1.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = margin(1,1,1,1, "cm"),
        strip.background = element_rect(fill = "white", color = "black"),
        legend.key = element_rect(fill = "white",color = NA),
        legend.text = element_text(size = 15),
        legend.key.height = unit(0.5, "inch"),
        legend.key.width = unit(0.4, "inch"),
        legend.title = element_blank(),
        legend.position = "right",
        axis.text = element_text(size = 15, color = "black"),
        axis.title = element_text(size = 20),
        text = element_text(family = "Helvetica")) +
   annotate("rect", xmin = 10, xmax = 50, ymin = 0, ymax = 0.15,
           alpha = .25,fill = "#06558B")  +
  annotate("rect", xmin = 50.1, xmax = 90, ymin = 0, ymax = 0.15,
           alpha = .25,fill = "#AA4613") 
```


## Modified Aromaticity 

```{r}

# Calculate modified aromaticity via Koch and Dittmar (2016)

AI_mod_metadata <- fqt_class_metadata_formula_stoichiometry_unique %>% 
  mutate(DBE = (1+C -(0.5*O) - S - (0.5*(N + P + H))),
         AI_mod = DBE / (C - (0.5*O) - N - S - P)) %>%  
  group_by(ATTRIBUTE_season, ATTRIBUTE_blade, ATTRIBUTE_age_d, ATTRIBUTE_sample_date) %>% 
  filter(AI_mod > 0) %>% 
  mutate(weighted_AI_mod = (sum(AI_mod*peak_area))/(sum(peak_area))) %>%
  select(ATTRIBUTE_season,ATTRIBUTE_blade, ATTRIBUTE_age_d,weighted_AI_mod) %>% 
  unique() 



modified_aromaticity_weighted <- AI_mod_metadata %>% 
  ggplot(aes(x = ATTRIBUTE_age_d, y = weighted_AI_mod, colour = ATTRIBUTE_season)) +
  geom_point(size = 4) +
  labs(x = "Age (d)",
       y = "Modified Aromaticity (Peak Area Weighted)") +
  scale_y_continuous() +
  geom_smooth(se = F)+
  scale_color_manual(values=c("dodgerblue1", "red4")) +
  theme(panel.background = element_rect(fill = "white", color = "black", size = 1.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = margin(1,1,1,1, "cm"),
        strip.background = element_rect(fill = "white", color = "black"),
        legend.key = element_rect(fill = "white",color = NA),
        legend.text = element_text(size = 15),
        legend.key.height = unit(0.5, "inch"),
        legend.key.width = unit(0.4, "inch"),
        legend.title = element_blank(),
        axis.text = element_text(size = 15, color = "black"),
        axis.title = element_text(size = 15),
        text = element_text(family = "Times")) 
  
# Calculate the percentage of peak area with AI > 0.5

highAI_peak_area_sum <- fqt_class_metadata_formula_stoichiometry_unique %>% 
  mutate(DBE = (1+C -(0.5*O) - S - (0.5*(N + P + H))),
         AI_mod = DBE / (C - (0.5*O) - N - S - P)) %>%  
  group_by(ATTRIBUTE_season, ATTRIBUTE_blade, ATTRIBUTE_age_d, ATTRIBUTE_sample_date) %>% 
  filter(AI_mod > 0) %>% 
  summarize(percent_high_AI = sum(peak_area[AI_mod > 0.5]/sum(peak_area))) %>% 
  ungroup() %>% 
  group_by(ATTRIBUTE_season, ATTRIBUTE_age_d) %>% 
  summarize(percent_high_AI_peak_area = mean(percent_high_AI), sd_percent_high_AI_peak_area = sd(percent_high_AI))

highAI_peak_area_sum %>% 
  ggplot(aes(x = ATTRIBUTE_age_d, y = percent_high_AI_peak_area, colour = ATTRIBUTE_season)) +
  geom_point(size = 4) +
  labs(x = "Age (d)",
       y = "High Aromaticity (% Peak Area)") +
  scale_y_continuous() +
  scale_color_manual(values=c("dodgerblue1", "red4")) +
  theme(panel.background = element_rect(fill = "white", color = "black", size = 1.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = margin(1,1,1,1, "cm"),
        strip.background = element_rect(fill = "white", color = "black"),
        legend.key = element_rect(fill = "white",color = NA),
        legend.text = element_text(size = 15),
        legend.key.height = unit(0.5, "inch"),
        legend.key.width = unit(0.4, "inch"),
        legend.title = element_blank(),
        axis.text = element_text(size = 15, color = "black"),
        axis.title = element_text(size = 15),
        text = element_text(family = "Times")) 
  


```

# Proportion of formulas

```{r}


formulas_simple_NEG <- fqt_class_metadata_formula_stoichiometry_unique %>%
   mutate(isCHON = case_when(
      C>0 & H >0 & O >0 & N > 0 & peak_area > 0 ~ TRUE,
      TRUE ~ FALSE
   )) %>% 
  mutate(isCHOBr = case_when(
    C > 0 & H >0 & O > 0 & Br > 0 & peak_area > 0 ~ TRUE,
    TRUE ~ FALSE
  )) %>% 
  mutate(isCHO = case_when(
    As < 1 & B < 1 & Br < 1 & C > 0 & Cl < 1 & F < 1 & H > 0 & I < 1 & N < 1 & O > 0 & P < 1 & S < 1 & Se < 1 & Si < 1 & peak_area > 0 ~ TRUE,
    TRUE ~ FALSE
  )) %>% 
  mutate(isCHOS = case_when(
    C > 0 & H >0 & O > 0 & S > 0 & peak_area > 0 ~ TRUE,
    TRUE ~ FALSE))  %>% 
  filter(peak_area > 0) %>% 
  group_by(ATTRIBUTE_season, ATTRIBUTE_phys_state, ATTRIBUTE_blade, ATTRIBUTE_age_d) %>% 
  summarize(CHO = mean(isCHO, na.rm = TRUE),
            "CHOBr" = mean(isCHOBr, na.rm = TRUE),
            "CHON" = mean(isCHON, na.rm = TRUE),
            "CHOS" = mean(isCHOS, na.rm = TRUE)) %>% 
  pivot_longer(
    cols = c(CHO, "CHOBr", "CHON", "CHOS"), 
    names_to = "formula_class",     
    values_to = "Proportion"      
  )
     
my_pallet <- c(c("#001260", "#AA4613"))

library(ggsignif)
library(ggpubr)

my_comparisons <- list( c("0.5", "1"), c("1", "2"), c("0.5", "2"))


     
formula_p_NEG_season <- ggboxplot(formulas_simple_NEG,
                  x = "formula_class",
                  y = "Proportion", 
                  color = "ATTRIBUTE_phys_state",
                  shape = "ATTRIBUTE_season",
                  palette = my_pallet,
                  add = "jitter") +
  stat_compare_means(aes(x = formula_class, 
                   y = Proportion,
                   group = ATTRIBUTE_phys_state),
                   label = "p.signif",
                   label.y = c(0.5, 0.4, 0.9, 0.5),
                   size = 6) +
  labs(x = "",
       y = "Proportion of Formulas (%)",
       fill = "") + 
  facet_wrap( ~ ATTRIBUTE_season) +
  theme(panel.background = element_rect(fill = "white", color = "black", size = 1.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = margin(1,1,1,1, "cm"),
        strip.background = element_rect(fill = "white", color = "black"),
        legend.key = element_rect(fill = "white",color = NA),
        legend.text = element_text(size = 15),
        legend.key.height = unit(0.5, "inch"),
        legend.key.width = unit(0.4, "inch"),
        legend.position = "right",
        legend.title = element_blank(),
        axis.text = element_text(size = 15, color = "black"),
        axis.title = element_text(size = 15),
        text = element_text(family = "Helvetica")) +
  coord_cartesian(expand = c(0,1)) +
  scale_y_continuous(limits = c(0,1), breaks = c(0,0.2,0.4,0.6,0.8,1.0)) +
  guides()


formula_p_NEG_dev_stage <- ggboxplot(formulas_simple_NEG,
                  x = "formula_class",
                  y = "Proportion", 
                  color = "ATTRIBUTE_phys_state",
                  shape = "ATTRIBUTE_season",
                  palette = my_pallet,
                  add = "jitter") +
  stat_compare_means(aes(x = formula_class, 
                   y = Proportion,
                   group = ATTRIBUTE_season),
                   label = "p.signif",
                   label.y = c(0.5, 0.4, 0.9, 0.5),
                   size = 6) +
  labs(x = "",
       y = "Proportion of Formulas (%)",
       fill = "") + 
  facet_wrap( ~ ATTRIBUTE_phys_state) +
  theme(panel.background = element_rect(fill = "white", color = "black", size = 1.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = margin(1,1,1,1, "cm"),
        strip.background = element_rect(fill = "white", color = "black"),
        legend.key = element_rect(fill = "white",color = NA),
        legend.text = element_text(size = 15),
        legend.key.height = unit(0.5, "inch"),
        legend.key.width = unit(0.4, "inch"),
        legend.position = "right",
        legend.title = element_blank(),
        axis.text = element_text(size = 15, color = "black"),
        axis.title = element_text(size = 15),
        text = element_text(family = "Helvetica")) +
  coord_cartesian(expand = c(0,1)) +
  scale_y_continuous(limits = c(0,1), breaks = c(0,0.2,0.4,0.6,0.8,1.0)) +
  guides()


formula_p_NEG <- ggboxplot(formulas_simple_NEG,
                  x = "formula_class",
                  y = "Proportion", 
                  color = "ATTRIBUTE_phys_state",
                  shape = "ATTRIBUTE_season",
                  palette = my_pallet,
                  add = "jitter") +
  stat_compare_means(aes(x = formula_class, 
                   y = Proportion,
                   group = ATTRIBUTE_phys_state),
                   label = "p.signif",
                   label.y = c(0.5, 0.4, 0.9, 0.5),
                   size = 6) +
  labs(x = "",
       y = "Proportion of Formulas (%)",
       fill = "") +
  theme(panel.background = element_rect(fill = "white", color = "black", size = 1.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = margin(1,1,1,1, "cm"),
        strip.background = element_rect(fill = "white", color = "black"),
        legend.key = element_rect(fill = "white",color = NA),
        legend.text = element_text(size = 15),
        legend.key.height = unit(0.5, "inch"),
        legend.key.width = unit(0.4, "inch"),
        legend.position = "right",
        legend.title = element_blank(),
        axis.text = element_text(size = 15, color = "black"),
        axis.title = element_text(size = 15),
        text = element_text(family = "Helvetica")) +
  coord_cartesian(expand = c(0,1)) +
  scale_y_continuous(limits = c(0,1), breaks = c(0,0.2,0.4,0.6,0.8,1.0)) +
  guides()


# Summary stats 

formulas_simple_POS %>% 
  group_by(formula_simple, ATTRIBUTE_phys_state) %>% 
  summarize(min_p = min(prop_formula),
            max_p = max(prop_formula),
            mean_p = mean(prop_formula),
            sd_p = sd(prop_formula))
     
     


# Sumamry stats 

summary_stoichiometry_table <- formulas_simple_NEG %>% 
  group_by(formula_class, ATTRIBUTE_phys_state) %>% 
  summarize(min_p = min(Proportion),
            max_p = max(Proportion),
            mean_p = mean(Proportion),
            sd_p = sd(Proportion))

```


# Peak Areas 

```{r}

peakarea_DOC <- fqt_class_metadata_long %>% 
  filter(!ATTRIBUTE_LC_vial_name %in% c("230823 B1", "230823 B2", "230823 B3", "Sample")) %>% 
  group_by(ATTRIBUTE_season, ATTRIBUTE_age_d, ATTRIBUTE_blade) %>% 
  summarize(XIC_sum = sum(peak_area),
            ATTRIBUTE_DOC_prePPL_uMC = ATTRIBUTE_DOC_prePPL_uMC)

peakarea_DOC %>% 
  ggplot(aes(x = ATTRIBUTE_DOC_prePPL_uMC, y = XIC_sum)) +
  geom_point(aes(color = ATTRIBUTE_age_d)) +
  geom_abline(intercept = -1219231364, slope =  16812722.0)
  
lmodel2(data = peakarea_DOC, XIC_sum~ATTRIBUTE_DOC_prePPL_uMC)

```

# Enriched Kelp Exudate Feature Ids 

```{r}

fqt_class_metadata_RA_PCOA_feature_list <- fqt_class_metadata_RA_PCOA_4 %>% 
  select(`row ID`, ATTRIBUTE_phys_state) %>% 
  unique() %>% 
  mutate(featureID = `row ID`) 

write_csv(fqt_class_metadata_RA_PCOA_feature_list, "/Users/chanceenglish/Desktop/Lab Shiz/ARPA-e/Giant_Kelp_DOC/Data/metabolites/NEG/fqt_class_metadata_RA_PCOA_feature_list.csv")

```


# FBMN Results for exudate features w/ subnetwork IDs, merge with Relative peak areas and metadata

```{r}

FBMN_results <- read_csv(here("Data", "metabolites", "NEG","FBMN_wNIST_cytoscape_results.csv"))

FBMN_results_simple <- FBMN_results %>% 
  select(featureID, component, IsSingleNode, library_compound_name) %>% 
  mutate(`row ID` = featureID) %>% 
  select(-featureID)


fqt_class_metadata_RA_long <- fqt_class_metadata_RA %>% 
  pivot_longer(cols = c(`240616_NEG_B4.mzML`:`230905_NEG_B6.mzML`),
               names_to = "filename",
               values_to = "rpa") %>% 
  unique()

fqt_class_metadata_RA_long <- fqt_class_metadata_RA_long %>% 
  filter(ATTRIBUTE_season %in% c("Spring", "Summer"))


fqt_class_metadata_RA_subnetwork_sum <- merge(fqt_class_metadata_RA_long, FBMN_results_simple, by = "row ID") %>% 
  unique()


#fqt_class_metadata_RA_subnetwork_sum <- fqt_class_metadata_RA_subnetwork_sum %>% 
  filter(!ATTRIBUTE_LC_vial_name %in% c("230823 B1","230823 B2","230823 B3"))

  

fqt_class_metadata_RA_subnetwork_sum2 <- fqt_class_metadata_RA_subnetwork_sum %>% 
  group_by(component, ATTRIBUTE_season, ATTRIBUTE_phys_state, ATTRIBUTE_blade, ATTRIBUTE_age_d) %>% 
  summarize(subnetwork_rpa = sum(rpa)) %>% 
  ungroup()

  
# Wilcox paired test, test if sub networks are significantly higher or lower between developmental stages


subnetwork_RA_phys_state_wilcox_test <- fqt_class_metadata_RA_subnetwork_sum2 %>% 
  filter(ATTRIBUTE_season != "September") %>% 
  select(component, ATTRIBUTE_phys_state, subnetwork_rpa) %>% 
  nest(data = c(ATTRIBUTE_phys_state, subnetwork_rpa)) %>% 
  mutate(model = map(data, ~wilcox.test(subnetwork_rpa ~ ATTRIBUTE_phys_state, .)), 
         tidy = map(model, broom::tidy)) %>% 
  select(component, tidy) %>% 
  unnest(tidy) %>% 
  filter(p.value != "NA") %>% 
  mutate(adjusted_p.value = p.adjust(p.value, method = "BH")) %>% 
  filter(adjusted_p.value != "NaN")


# How many sub networks are significant 

length(subnetwork_RA_phys_state_wilcox_test$component[subnetwork_RA_phys_state_wilcox_test$adjusted_p.value < 0.05]) # 209 significant

# How many subnetworks in total 

length(subnetwork_RA_phys_state_wilcox_test$component) # 436 total


# Pull ids of enriched subnetworks and make csv for import to cytoscape

phys_state_sig_subnetworks <- subnetwork_RA_phys_state_wilcox_test %>%
  filter(adjusted_p.value < 0.05) %>% 
  pull(`component`)


sig_phys_state_subnetworks <- as.data.frame(phys_state_sig_subnetworks)

sig_phys_state_subnetworks <- sig_phys_state_subnetworks %>% 
  mutate(signif_phys_state = "TRUE",
         component = phys_state_sig_subnetworks) %>% 
  select(-phys_state_sig_subnetworks)

sig_phys_state_networks <- merge(sig_phys_state_subnetworks, fqt_class_metadata_RA_subnetwork_sum, by = "component") %>% 
  select(`row ID`, component, signif_phys_state)

write_csv(sig_phys_state_networks, "/Users/chanceenglish/Desktop/Lab Shiz/ARPA-e/Giant_Kelp_DOC/Data/metabolites/NEG/sig_phys_state_networks.csv")


subnetwork_RA_phys_state_wilcox_sig <- subnetwork_RA_phys_state_wilcox_test %>% 
  filter(adjusted_p.value < 0.05)

subnetwork_RA_phys_state_wilcox_sig_compounds <- merge(subnetwork_RA_phys_state_wilcox_sig, fqt_class_metadata_RA_subnetwork_sum_consensus_class, by = "component")



# Wilcox, test if sub networks are significantly higher or lower between seasons


subnetwork_RA_season_wilcox_test <- fqt_class_metadata_RA_subnetwork_sum2 %>% 
  filter(ATTRIBUTE_season != "September") %>% 
  select(component, ATTRIBUTE_season, subnetwork_rpa) %>% 
  nest(data = c(ATTRIBUTE_season, subnetwork_rpa)) %>% 
  mutate(model = map(data, ~wilcox.test(subnetwork_rpa ~ ATTRIBUTE_season, .)), 
         tidy = map(model, broom::tidy)) %>% 
  select(component, tidy) %>% 
  unnest(tidy) %>% 
  filter(p.value != "NA") %>% 
  mutate(adjusted_p.value = p.adjust(p.value, method = "BH")) %>% 
  filter(adjusted_p.value != "NaN")


# How many sub networks are significant 

length(subnetwork_RA_season_wilcox_test$component[subnetwork_RA_season_wilcox_test$adjusted_p.value < 0.05]) # 111 significant

# How many subnetworks in total 

length(subnetwork_RA_season_wilcox_test$component) # 436 total


# Pull ids of enriched subnetworks and make csv for import to cytoscape


season_sig_subnetworks <- subnetwork_RA_season_wilcox_test %>%
  filter(adjusted_p.value < 0.05) %>% 
  pull(`component`)


sig_season_networks <- as.data.frame(season_sig_subnetworks)

sig_season_networks <- sig_season_networks %>% 
  mutate(signif_season = "TRUE",
         component = season_sig_subnetworks) %>% 
  select(-season_sig_subnetworks)

sig_season_networks <- merge(sig_season_networks, fqt_class_metadata_RA_subnetwork_sum, by = "component") %>% 
  select(`row ID`, component, signif_season)

write_csv(sig_season_networks, "/Users/chanceenglish/Desktop/Lab Shiz/ARPA-e/Giant_Kelp_DOC/Data/metabolites/NEG/sig_season_networks.csv")


# What subnetworks are enrcihed between spring and summer in the mature kelp exudates

## Wilcox paired test, test if sub networks are significantly higher or lower between developmental stages


subnetwork_RA_season_mature_wilcox_test <- fqt_class_metadata_RA_subnetwork_sum2 %>% 
  filter(ATTRIBUTE_season != "September",
         ATTRIBUTE_phys_state == "Mature") %>% 
  select(component, ATTRIBUTE_season,subnetwork_rpa) %>% 
  nest(data = c(ATTRIBUTE_season, subnetwork_rpa)) %>% 
  mutate(model = map(data, ~wilcox.test(subnetwork_rpa ~ ATTRIBUTE_season, .)), 
         tidy = map(model, broom::tidy)) %>% 
  select(component, tidy) %>% 
  unnest(tidy) %>% 
  filter(p.value != "NA") %>% 
  mutate(adjusted_p.value = p.adjust(p.value, method = "BH")) %>% 
  filter(adjusted_p.value != "NaN")


# How many sub networks are significant 

length(subnetwork_RA_season_mature_wilcox_test$component[subnetwork_RA_season_mature_wilcox_test$adjusted_p.value < 0.05]) # 147 significant

# How many subnetworks in total 

length(subnetwork_RA_season_mature_wilcox_test$component) # 506 total


# Pull ids of enriched subnetworks and make csv for import to cytoscape

season_mature_sig_subnetworks <- subnetwork_RA_season_mature_wilcox_test %>%
  filter(adjusted_p.value < 0.05) %>% 
  pull(`component`)


season_mature_sig_subnetworks <- as.data.frame(season_mature_sig_subnetworks)

season_mature_sig_subnetworks <- season_mature_sig_subnetworks %>% 
  mutate(signif_season_mature = "TRUE",
         component = season_mature_sig_subnetworks) %>% 
  select(-season_mature_sig_subnetworks)

sig_season_mature_networks <- merge(season_mature_sig_subnetworks, fqt_class_metadata_RA_subnetwork_sum, by = "component") %>% 
  select(`row ID`, component, signif_season_mature)

sig_season_mature_networks <- sig_season_mature_networks %>% 
  mutate(component2 = component)


write_csv(sig_season_mature_networks, "/Users/chanceenglish/Desktop/Lab Shiz/ARPA-e/Giant_Kelp_DOC/Data/metabolites/NEG/sig_season_mature_networks.csv")

```

# Plot amino acids, peptides, analogues and halogenated aromatics, phenols, aryls, benzenoids

```{r}

AAPA_p <- fqt_class_metadata_RA_subnetwork_sum %>% 
  filter(`ClassyFire#subclass` == "Amino acids, peptides, and analogues", 
         ATTRIBUTE_season != "September") %>% 
  group_by(ATTRIBUTE_age_d, ATTRIBUTE_season, ATTRIBUTE_blade) %>% 
  summarize(sum_rpa = sum(rpa)) %>% 
  ungroup() %>% 
  group_by(ATTRIBUTE_age_d, ATTRIBUTE_season) %>% 
  mutate(mean_rpa = mean(sum_rpa),
         sd_rpa = sd(sum_rpa)) %>% 
  distinct() %>% 
  ggplot() +
  geom_point(aes(x = ATTRIBUTE_age_d, y = sum_rpa*100, shape = ATTRIBUTE_season)) +
  geom_point(aes(x = ATTRIBUTE_age_d, y = mean_rpa*100, shape = ATTRIBUTE_season), size = 4) +
  geom_line(aes(x = ATTRIBUTE_age_d, y = mean_rpa*100, shape = ATTRIBUTE_season ), size = 0.5) +
  labs(x = "Age (d)",
       y = "Amino Acids, Peptides, analogues \n (% RPA)",
       shape = NULL) +
  scale_shape_manual(values = c(1,2)) +
  scale_x_continuous(breaks = c(10,20,30,40,50,60,70,80,90), limits = c(10,90)) +
  scale_y_continuous(breaks = c(0,10,20,30,40), limits = c(0,40)) +
  coord_cartesian(expand = c(0,0)) +
   theme(panel.background = element_rect(fill = "white", color = "black", size = 1.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = margin(1,1,1,1, "cm"),
        strip.background = element_rect(fill = "white", color = "black"),
        legend.key = element_rect(fill = "white",color = NA),
        legend.text = element_text(size = 15),
        legend.key.height = unit(0.5, "inch"),
        legend.key.width = unit(0.4, "inch"),
        legend.title = element_blank(),
        legend.position = "right",
        axis.text = element_text(size = 15, color = "black"),
        axis.title = element_text(size = 20),
        text = element_text(family = "Helvetica")) +
   annotate("rect", xmin = 10, xmax = 50, ymin = 0, ymax = 40,
           alpha = .25,fill = "#06558B")  +
  annotate("rect", xmin = 50.1, xmax = 90, ymin = 0, ymax = 40,
           alpha = .25,fill = "#AA4613") 



halo_aro_p <- fqt_class_metadata_RA_subnetwork_sum %>% 
  filter(`ClassyFire#subclass` %in% c("Halophenols", "Aryl chlorides", "Aryl bromides", "Aryl iodides", "1,4−dihydroxy−2−halobenzenoids"), 
         ATTRIBUTE_season != "September") %>% 
  group_by(ATTRIBUTE_age_d, ATTRIBUTE_season, ATTRIBUTE_blade) %>% 
  summarize(sum_rpa = sum(rpa)) %>% 
  ungroup() %>% 
  group_by(ATTRIBUTE_age_d, ATTRIBUTE_season) %>% 
  mutate(mean_rpa = mean(sum_rpa),
         sd_rpa = sd(sum_rpa)) %>% 
  distinct() %>% 
  ggplot() +
  geom_point(aes(x = ATTRIBUTE_age_d, y = sum_rpa*100, shape = ATTRIBUTE_season)) +
  geom_point(aes(x = ATTRIBUTE_age_d, y = mean_rpa*100, shape = ATTRIBUTE_season), size = 4) +
  geom_line(aes(x = ATTRIBUTE_age_d, y = mean_rpa*100, shape = ATTRIBUTE_season ), size = 0.5) +
  scale_x_continuous(breaks = c(10,20,30,40,50,60,70,80,90), limits = c(10,90)) +
  scale_y_continuous(breaks = c(0,10,20,30,40), limits = c(0,40)) +
  labs(x = "Age (d)",
       y = "Halogenated Aromatics (% RPA)",
       shape = NULL) +
  coord_cartesian(expand = c(0,0)) +
  scale_shape_manual(values = c(1,2)) +
   theme(panel.background = element_rect(fill = "white", color = "black", size = 1.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = margin(1,1,1,1, "cm"),
        strip.background = element_rect(fill = "white", color = "black"),
        legend.key = element_rect(fill = "white",color = NA),
        legend.text = element_text(size = 15),
        legend.key.height = unit(0.5, "inch"),
        legend.key.width = unit(0.4, "inch"),
        legend.title = element_blank(),
        legend.position = "right",
        axis.text = element_text(size = 15, color = "black"),
        axis.title = element_text(size = 20),
        text = element_text(family = "Helvetica")) +
   annotate("rect", xmin = 10, xmax = 50, ymin = 0, ymax = 40,
           alpha = .25,fill = "#06558B")  +
  annotate("rect", xmin = 50.1, xmax = 90, ymin = 0, ymax = 40,
           alpha = .25,fill = "#AA4613") 



my_colors <- scico(7, palette = "vik")
scales::show_col(my_colors)


```


# Select subnetworks that are signifcantly different between developmental stage  

```{r}


Subnetwork_1850_rpa_p <- fqt_class_metadata_RA_subnetwork_sum %>% 
  filter(component == 1850) %>% 
  group_by(ATTRIBUTE_phys_state, ATTRIBUTE_season, ATTRIBUTE_age_d, ATTRIBUTE_blade) %>% 
  summarize(sum_component = sum(rpa)) %>% 
  ungroup() %>% 
  ggplot() + 
  geom_boxplot(aes(x = ATTRIBUTE_phys_state, y = sum_component*100)) +
  geom_point(aes(x = ATTRIBUTE_phys_state, y = sum_component*100), 
             position = position_jitterdodge(0.3)) +
  scale_y_continuous() +
  scale_fill_manual(values=c("dodgerblue1", "red4")) +
  labs(x = "",
       y = "Subnetwork 1850 (% Peak Area)") +
        theme(panel.background = element_rect(fill = "white", color = "black", size = 1.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = margin(1,1,1,1, "cm"),
        strip.background = element_rect(fill = "white", color = "white"),
        legend.key = element_blank(),
        legend.text = element_text(size = 8),
        legend.key.height = unit(0.5, "inch"),
        legend.key.width = unit(0.4, "inch"),
        legend.title = element_blank(),
        axis.text = element_text(size = 20, color = "black"),
        axis.title = element_text(size = 20),
        text = element_text(family = "Times")) 


Subnetwork_389_rpa_p <- fqt_class_metadata_RA_subnetwork_sum %>% 
  filter(component == 389) %>% 
  group_by(ATTRIBUTE_phys_state, ATTRIBUTE_season, ATTRIBUTE_age_d, ATTRIBUTE_blade) %>% 
  summarize(sum_component = sum(rpa)) %>% 
  ungroup() %>% 
  ggplot() + 
  geom_boxplot(aes(x = ATTRIBUTE_phys_state, y = sum_component*100)) +
  geom_point(aes(x = ATTRIBUTE_phys_state, y = sum_component*100), 
             position = position_jitterdodge(0.3)) +
  scale_y_continuous() +
  scale_fill_manual(values=c("dodgerblue1", "red4")) +
  labs(x = "",
       y = "Subnetwork 389 (% Peak Area)") +
        theme(panel.background = element_rect(fill = "white", color = "black", size = 1.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = margin(1,1,1,1, "cm"),
        strip.background = element_rect(fill = "white", color = "white"),
        legend.key = element_blank(),
        legend.text = element_text(size = 8),
        legend.key.height = unit(0.5, "inch"),
        legend.key.width = unit(0.4, "inch"),
        legend.title = element_blank(),
        axis.text = element_text(size = 20, color = "black"),
        axis.title = element_text(size = 20),
        text = element_text(family = "Times")) 

Subnetwork_693_rpa_p <- fqt_class_metadata_RA_subnetwork_sum %>% 
  filter(component == 693) %>% 
  group_by(ATTRIBUTE_phys_state, ATTRIBUTE_season, ATTRIBUTE_age_d, ATTRIBUTE_blade) %>% 
  summarize(sum_component = sum(rpa)) %>% 
  ungroup() %>% 
  ggplot() + 
  geom_boxplot(aes(x = ATTRIBUTE_phys_state, y = sum_component*100)) +
  geom_point(aes(x = ATTRIBUTE_phys_state, y = sum_component*100), 
             position = position_jitterdodge(0.3)) +
  scale_y_continuous() +
  scale_fill_manual(values=c("dodgerblue1", "red4")) +
  labs(x = "",
       y = "Subnetwork 693 (% Peak Area)") +
        theme(panel.background = element_rect(fill = "white", color = "black", size = 1.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = margin(1,1,1,1, "cm"),
        strip.background = element_rect(fill = "white", color = "white"),
        legend.key = element_blank(),
        legend.text = element_text(size = 15),
        legend.key.height = unit(0.5, "inch"),
        legend.key.width = unit(0.4, "inch"),
        legend.title = element_blank(),
        axis.text = element_text(size = 20, color = "black"),
        axis.title = element_text(size = 20),
        text = element_text(family = "Times")) 




```


# Subnetwork relative bundance across age stacked bar plot 

```{r}

library(reshape2)

# Identify subnetworks with an average of 1% in at least one age group

sig_subnetworks_one_percent <- fqt_class_metadata_RA_subnetwork_sum2 %>% 
  group_by(ATTRIBUTE_age_d, component) %>% 
  summarise(avg_rpa = mean(subnetwork_rpa), .groups = "drop") %>% 
  ungroup() %>% 
  group_by(ATTRIBUTE_age_d, component) %>% 
  filter(any(avg_rpa > 0.01)) %>% 
  mutate(component = as.factor(component)) %>% 
  ungroup() %>% 
  group_by(component) %>% 
  filter(ATTRIBUTE_age_d != is.na(ATTRIBUTE_age_d))


sig_subnetworks_one_percent_component <- sig_subnetworks_one_percent$component


# Select subnetworks with more than 1% mean peak area per age 


fqt_class_metadata_RA_subnetwork_sum3 <- fqt_class_metadata_RA_subnetwork_sum2 %>% 
  filter(component %in% sig_subnetworks_one_percent_component)

# Filter subnetworks into a consensus class for the stacked barplot 


fqt_class_metadata_RA_subnetwork_sum_consensus_class <- fqt_class_metadata_RA_subnetwork_sum %>% 
  group_by(component, `ClassyFire#subclass`, `ClassyFire#class`) %>% 
  summarise(Totalsum = sum(rpa), .groups = 'drop') %>%
  ungroup() %>% 
  group_by(component) %>% 
  slice_max(Totalsum, n = 1, with_ties = FALSE)
  

fqt_class_metadata_RA_subnetwork_sum3_compounds_classes <- merge(fqt_class_metadata_RA_subnetwork_sum_consensus_class, fqt_class_metadata_RA_subnetwork_sum3, by = "component")

# Merge significance results with the peak area data and subnetwork 

fqt_class_metadata_RA_subnetwork_sum3_compounds_classes <- fqt_class_metadata_RA_subnetwork_sum3_compounds_classes %>% 
  mutate(significantly_enriched = ifelse(
    component %in% subnetwork_RA_phys_state_wilcox_sig$component,
    "bold",
    "plain"
  ))

# Create unique identifier with subnetwork ID and consensus class
  
fqt_class_metadata_RA_subnetwork_sum3_compounds_classes$com_cla_subcla <- do.call(paste, c(fqt_class_metadata_RA_subnetwork_sum3_compounds_classes[c("component","ClassyFire#class", "ClassyFire#subclass")], sep=";")) 
  
fqt_class_metadata_RA_subnetwork_sum3_compounds_classes <- fqt_class_metadata_RA_subnetwork_sum3_compounds_classes %>% 
  group_by(component) %>% 
  mutate(prop_16 = sum(subnetwork_rpa[ATTRIBUTE_age_d %in% c(16,30,37, 43)], na.rm= T)/sum(subnetwork_rpa, na.rm=T),
         ATTRIBUTE_age_d = as.factor(ATTRIBUTE_age_d))


# Factor age for stacked bar plot

fqt_class_metadata_RA_subnetwork_sum3_compounds_classes$ATTRIBUTE_age_d <- factor(fqt_class_metadata_RA_subnetwork_sum3_compounds_classes$ATTRIBUTE_age_d, levels = c("16","30","37","43","64","77","78"))



# Make noramlized stacked barplot showing relative contribution of subnetworks at specific ages

face_vector <- fqt_class_metadata_RA_subnetwork_sum3_compounds_classes$significantly_enriched


norm_bar_plot_component_p <- fqt_class_metadata_RA_subnetwork_sum3_compounds_classes %>% 
  filter(significantly_enriched == "bold") %>% 
  ggplot(aes(y = reorder(com_cla_subcla, prop_16, decreasing=T),
                             x = subnetwork_rpa, 
                             fill = ATTRIBUTE_age_d)) +
  geom_bar(position = "fill", stat = "identity") +
  labs(x = "Peak Area Normalized",
       y = "Subnetwork",
       fill = "Age (d)") +
  coord_cartesian(expand = c(0,0)) +
  scale_fill_manual(values = c("#001260", "#06558B", "#71A7C4", "#EBE5E0","#AA4613","#590007","#590007")) +
  scale_x_continuous() + 
   theme(panel.background = element_rect(fill = "white", color = "black", size = 1.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = margin(1,1,1,1, "cm"),
        strip.background = element_rect(fill = "white", color = "black"),
        legend.key = element_rect(fill = "white", color = NA),
        legend.text = element_text(size = 15),
        legend.position = "none",
        legend.key.height = unit(1, "inch"),
        legend.key.width = unit(0.4, "inch"),
        legend.title = element_text(size = 15),
        axis.text.y = element_text(size = 15, color = "black"),
        axis.text.x = element_text(size = 15, 
                                   color = "black",
                                   face = face_vector),
        axis.title = element_text(size = 20),
        text = element_text(family = "Helvetica")) 


ggsave("norm_bar_plot_component_p_sig_and_non_sig.pdf", plot = norm_bar_plot_component_p, path = "/Users/chanceenglish/Desktop/Lab Shiz/ARPA-e/Giant_Kelp_DOC/Figures/HQ Figs Metabolites/", width = 16, height = 15, device='pdf', dpi=250, units = "in")
  

# Complimentary dotplot showing range of relative peak areas

norm_bar_plot_component_rpa_p <- fqt_class_metadata_RA_subnetwork_sum3_compounds_classes %>% 
    filter(significantly_enriched == "bold") %>% 
 ggplot(aes(y = reorder(com_cla_subcla, prop_16, decreasing=T),
                             x = subnetwork_rpa*100)) +
  geom_point(aes(fill = ATTRIBUTE_age_d,
                 shape = ATTRIBUTE_season), 
             size = 5,
             alpha = 0.7) +
  geom_line(color ="black", size = 0.2) +
  labs(x = "Peak Area (%)",
       y = "Subnetwork",
       color = NULL,
       shape = NULL) +
  scale_shape_manual(values = c(21,24)) +
  scale_fill_manual(values = c("#001260", "#06558B", "#71A7C4", "#EBE5E0","#AA4613","#590007","#590007")) +
  scale_x_log10(breaks = c(0,0.001,0.01,0.1,1,10,100),
                    expand = expansion(mult = c(0, 0.05))) +
   theme(panel.background = element_rect(fill = "white", color = "black", size = 1),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = margin(1,1,1,1, "cm"),
        strip.background = element_rect(fill = "white", color = "black"),
        legend.key = element_rect(fill = "white", color = NA),
        legend.text = element_text(size = 15),
        legend.position = "right",
        legend.key.height = unit(0.5, "inch"),
        legend.key.width = unit(0.2, "inch"),
        legend.title = element_text(size = 15),
        axis.text.x = element_text(size = 15, color = "black"),
        axis.text.y = element_blank(),
        axis.title.y = element_blank(),
        axis.title = element_text(size = 20),
        text = element_text(family = "Helvetica"))+
  guides(fill = "none") +
  guides(shape = guide_legend(override.aes = list(size = 5))) 

ggsave("norm_bar_plot_component_rpa_sig_and_non_sig_p.pdf", plot = norm_bar_plot_component_rpa_p, path = "/Users/chanceenglish/Desktop/Lab Shiz/ARPA-e/Giant_Kelp_DOC/Figures/HQ Figs Metabolites/", width = 12, height = 15, device='pdf', dpi=250, units = "in")


# Filter subnetworks into a consensus class for the stacked barplot 

fqt_class_metadata_RA_subnetwork_sum_consensus_class <- fqt_class_metadata_RA_subnetwork_sum %>% 
  group_by(component, `ClassyFire#subclass`, `ClassyFire#class`) %>% 
  summarise(Totalsum = sum(rpa), .groups = 'drop') #%>%
  slice_max(Totalsum, n = 1, with_ties = FALSE)
  



```



# Van Krevelen Plots

```{r}

molecular_stoichiometry_VanK <- fqt_class_metadata_formula_stoichiometry_unique %>% 
  mutate(HC = (H*peak_area)/(C*peak_area),
         OC = (O*peak_area)/(C*peak_area),
         Br = Br,
         peak_area = peak_area) %>% 
  filter(HC != "NaN",
         OC != "NaN",
         HC != Inf,
         OC != Inf)


molecular_stoichiometry_VanK_sum <- as.data.frame(molecular_stoichiometry_VanK %>% 
  group_by(ATTRIBUTE_phys_state) %>% 
  summarize(mean_HC = mean((H*peak_area)/(C*peak_area)),
            sd_HC = sd((H*peak_area)/(C*peak_area)),
            mean_OC = mean((O*peak_area)/(C*peak_area)),
            sd_OC = sd((O*peak_area)/(C*peak_area))))
 

VanKrev_neg_p <-ggplot() +
  geom_point(aes(x = molecular_stoichiometry_VanK$OC, 
                     molecular_stoichiometry_VanK$HC, 
                     colour = molecular_stoichiometry_VanK$ATTRIBUTE_phys_state,
                 size = molecular_stoichiometry_VanK$peak_area, 
                 shape = molecular_stoichiometry_VanK$ATTRIBUTE_season),
             alpha = 0.2) +
  labs(x = "O:C",
       y = "H:C",
       color = "") +
  scale_color_manual(values = c("grey","orangered")) +
  geom_point(aes(x = molecular_stoichiometry_VanK_sum$mean_OC,
                 y = molecular_stoichiometry_VanK_sum$mean_HC,
                 fill = molecular_stoichiometry_VanK_sum$ATTRIBUTE_phys_state),
             size = 7,
             shape = 23,
             color = "black") +
  scale_fill_manual(values = c("grey","orangered")) +
  scale_size_continuous(range  = c(0.1, 15), 
                        limits = c(5e4, 5e7), 
                        breaks = c(5e4,5e5,5e6,5e7)) +
  scale_x_continuous(limits = c(0,1), breaks = c(0,0.2,0.4,0.6,0.8,1.0)) +
  scale_y_continuous(limits = c(0,2.5), breaks = c(0,0.5,1.0,1.5,2.0,2.5)) +
  theme(panel.background = element_rect(fill = "white", color = "black", size = 1.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = margin(1,1,1,1, "cm"),
        strip.background = element_rect(fill = "white", color = "black"),
        legend.key = element_rect(fill = "white", color = NA),
        legend.text = element_text(size = 15),
        legend.key.height = unit(0.5, "inch"),
        legend.key.width = unit(0.4, "inch"),
        legend.title = element_text(size = 15),
        axis.text = element_text(size = 15, color = "black"),
        axis.title = element_text(size = 15),
        text = element_text(family = "Helvetica")) +
  scale_size(guide = 'none') +
  scale_fill_discrete(guide = "none") +
  guides(color=guide_legend(override.aes=list(size=5), title = "Developmental Stage"),
         shape=guide_legend(override.aes=list(size=5), title = "Season")) 


molecular_stoichiometry_VanK_sum <- as.data.frame(molecular_stoichiometry_VanK %>% 
  group_by(ATTRIBUTE_phys_state) %>% 
  summarize(mean_HC = mean((H*peak_area)/(C*peak_area)),
            sd_HC = sd((H*peak_area)/(C*peak_area)),
            mean_OC = mean((O*peak_area)/(C*peak_area)),
            sd_OC = sd((O*peak_area)/(C*peak_area))))



```

# Figure 1 : 

## A

```{r}

# Load LTER bottom temp data

LTER_bottom_temp <- read_csv(here("Data", "Bottom_temp_all_years_20240802.csv"))

library(lubridate)

LTER_bottom_temp_MK <- LTER_bottom_temp %>% 
  filter(SITE == "MOHK") 

class(LTER_bottom_temp_MK$DATE_LOCAL)


colors <- c("#001260", "#06558B", "#71A7C4", "#EBE5E0","#AA4613","#590007","#590007")   


# Get measured nutrients from bottle data

LTER_bottom_data_nutrients <- read_xlsx("/Users/chanceenglish/Desktop/Lab Shiz/ARPA-e/Giant_Kelp_DOC/Data/lter_bottom_data.xlsx")

LTER_bottom_data_nutrients <- LTER_bottom_data_nutrients %>% 
  filter(Station == "MK",
         `Target Depth (m)` == 1) %>% 
  mutate(`yyyy-mm-dd` = as.character(`yyyy-mm-dd`))

LTER_bottom_data_nutrients$`NO2+NO3 (umol/l)`[LTER_bottom_data_nutrients$`NO2+NO3 (umol/l)` == "BDL"] <- "0.1"
  
LTER_bottom_data_nutrients <- rename(LTER_bottom_data_nutrients, DATE_LOCAL = "yyyy-mm-dd")

LTER_bottom_data_nutrients <- LTER_bottom_data_nutrients %>% 
  mutate(DATE_LOCAL = as.Date(DATE_LOCAL),
         `NO2+NO3 (umol/l)` = as.numeric(`NO2+NO3 (umol/l)`))

LTER_bottom_data_nutrients_sample_dates <- LTER_bottom_data_nutrients %>% 
  filter(`decimal year` > 2023.178081 & `decimal year` < 2024.521859)

class(LTER_bottom_data_nutrients$DATE_LOCAL)


# Merge temperature and nitrate bottle data to build GAM for Mohawk Reef

LTER_bottom_temp_MK_daily_mean_nitrate <- LTER_bottom_temp_MK %>% 
  mutate(temp_C = TEMP_C)



LTER_bottom_temp_MK_daily_mean_nitrate <- LTER_bottom_temp_MK %>% 
  group_by(DATE_LOCAL) %>% 
  summarize(temp_C = mean(TEMP_C)) %>% 
  mutate(T2N_nitrate = predict(gam_model_mk, newdata = .))

nuts_comparisons <- merge(LTER_bottom_temp_MK_daily_mean_nitrate, LTER_bottom_data_nutrients, by = "DATE_LOCAL")

nuts_comparisons <- nuts_comparisons %>% 
  filter(!`NO2+NO3 (umol/l)` == is.na(`NO2+NO3 (umol/l)`)) %>% 
  unique()



# GAM specific to mohawk reef data 

nuts_comparisons %>% 
  ggplot(aes(x = temp_C, y = `NO2+NO3 (umol/l)`)) +
  geom_point(shape = 21,
             color = "black",
             size = 2) +
  labs(x = "Temperature (ºC)",
       y = "Nitrate (µM)") +
  scale_x_continuous(breaks = c(10,12,14,16,18,20,22), limits = c(10,22)) +
  theme(panel.background = element_rect(fill = "white", color = "black", size = 1.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = margin(1,1,1,1, "cm"),
        legend.key = element_rect(fill = "white"),
        legend.text = element_text(size = 20),
        legend.key.height = unit(0.8, "inch"),
        legend.key.width = unit(0.4, "inch"),
        legend.title = element_text(size = 24),
        axis.title.y.right = element_text(color = "blue", size = 20),
        axis.text.y = element_text(size = 15, color = "black"),
        axis.title.y.left = element_text(size = 20),
        axis.text.x = element_text(size = 15 , color = "black"),
        axis.title.x = element_text(size = 20),
        text = element_text(family = "Helvetica"))

# Plot all temp and nitrate data 

nuts_comparisons %>% 
  ggplot(aes(x = temp_C, y = `NO2+NO3 (umol/l)`)) +
  geom_point(size = 1) 
  
# Fit gam for NO3 and temperature at Mohwak Reef
  
gam_model_mk <- gam(nuts_comparisons$`NO2+NO3 (umol/l)` ~ s(temp_C, k = 10),
                 data = nuts_comparisons)

summary(gam_model_mk)

gam.check(gam_model_mk)

plot(gam_model_mk)

plot(gam_model_mk, pch = 1, 
     cex = 1, 
     residuals = T, 
     pages = 1, 
     cex.lab = 1.5,
     cex.axis = 1.5,
     ylab = "Additive Effect on Nitrate",
     xlab = "Temperature (ºC)",
     family = "Helvetica")

# Calculate daily average temperature and T2N nitrate from MK GAM model

LTER_bottom_temp_MK_daily_mean_nitrate <- LTER_bottom_temp_MK %>% 
  group_by(DATE_LOCAL) %>% 
  summarize(temp_C = mean(TEMP_C)) %>% 
  mutate(T2N_nitrate = predict(gam_model_mk, newdata = .))


LTER_bottom_temp_MK_study_dates <- LTER_bottom_temp_MK %>% 
  filter(DATE_LOCAL > "2023-03-01" & DATE_LOCAL < "2024-08-01") %>% 
  group_by(DATE_LOCAL) %>% 
   summarize(temp_C = mean(TEMP_C)) %>% 
   mutate(T2N_nitrate = predict(gam_model_mk, newdata = .))



# Plot temperature and nutrients over study period

bottom_temp <- ggplot() +
  geom_line(aes(x = LTER_bottom_temp_MK_study_dates$DATE_LOCAL, 
                y = LTER_bottom_temp_MK_study_dates$temp_C),size = 0.5, color = "black") +
  geom_line(aes(x = LTER_bottom_temp_MK_study_dates$DATE_LOCAL, 
                y = LTER_bottom_temp_MK_study_dates$T2N_nitrate), size = 0.5, color = "blue") +
  geom_point(aes(x = LTER_bottom_data_nutrients_sample_dates$DATE_LOCAL,
                 y = LTER_bottom_data_nutrients_sample_dates$`NO2+NO3 (umol/l)`),
             shape = 13,
             color = "blue",
             size = 5) +
  labs(y = "Temp (ºC)",
       x = "") +
  annotate("rect", xmin = ymd('2023-08-09'),
                    xmax = ymd('2023-10-10'),
                    ymin = -Inf,
                    ymax = Inf,
             alpha = 0.25, fill="grey50") +
  annotate("rect", xmin = ymd('2024-04-17'),
                    xmax = ymd('2024-06-16'),
                    ymin = -Inf,
                    ymax = Inf,
             alpha = 0.25, fill="grey50") +
  annotate("segment", 
           x = ymd("2023-08-09"), 
           xend = ymd("2023-08-09"), 
           y = 0, 
           yend = 20,
           colour = "#001260",
           linetype = "dashed",
           size = 1) +
   annotate("segment", 
           x = ymd("2023-08-23"), 
           xend = ymd("2023-08-23"), 
           y = 0, 
           yend = 20,
           colour =  "#06558B",
           linetype = "dashed",
           size = 1) +
   annotate("segment", 
           x = ymd("2023-09-05"), 
           xend = ymd("2023-09-05"), 
           y = 0, 
           yend = 20,
           colour =  "#71A7C4",
           linetype = "dashed",
           size = 1) +
   annotate("segment", 
           x = ymd("2023-09-26"), 
           xend = ymd("2023-09-26"), 
           y = 0, 
           yend = 20,
           colour = "#AA4613",
           linetype = "dashed",
           size = 1) +
  annotate("segment", 
           x = ymd("2023-10-10"), 
           xend = ymd("2023-10-10"), 
           y = 0, 
           yend = 20,
           colour = "#590007",
           linetype = "dashed",
           size = 1) +
  annotate("segment", 
           x = ymd("2024-04-17"), 
           xend = ymd("2024-04-17"), 
           y = 0, 
           yend = 20,
           colour = "#001260",
           linetype = "dashed",
           size = 1) +
  annotate("segment", 
           x = ymd("2024-05-07"), 
           xend = ymd("2024-05-07"), 
           y = 0, 
           yend = 20,
           colour = "#71A7C4",
           linetype = "dashed",
           size = 1) +
  annotate("segment", 
           x = ymd("2024-06-16"), 
           xend = ymd("2024-06-16"), 
           y = 0, 
           yend = 20,
           colour = "#590007",
           linetype = "dashed",
           size = 1) +
  scale_y_continuous(breaks = c(0,5,10,15,20), 
                     limits = c(0,20), 
                     expand = c(0,0),
                     sec.axis = sec_axis( trans=~.*1, name="Nitrate (µM)")) +
  scale_x_date(date_breaks = "1 months", date_labels = "%b %y", expand = c(0,0)) +
  theme(panel.background = element_rect(fill = "white", color = "black", size = 1.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = margin(1,1,1,1, "cm"),
        legend.key = element_rect(fill = "white"),
        legend.text = element_text(size = 20),
        legend.key.height = unit(0.8, "inch"),
        legend.key.width = unit(0.4, "inch"),
        legend.title = element_text(size = 24),
        axis.title.y.right = element_text(color = "blue", size = 20),
        axis.text.y = element_text(size = 15, color = "black"),
        axis.title.y.left = element_text(size = 20),
        axis.text.x = element_text(size = 15 , color = "black", angle = 25, vjust = 0.5),
        axis.title.x = element_text(size = 20),
        text = element_text(family = "Helvetica"))

LTER_bottom_temp_MK_study_dates_sum <- 
  LTER_bottom_temp_MK_study_dates %>% 
  filter(DATE_LOCAL %in% c("2023-08-09","2023-08-23","2023-09-05","2023-09-26","2023-10-10","2024-04-17","2024-05-07","2024-05-28", "2024-06-16"))



# Compare measured and T2N modeled Nitrate concentrations at study site

nuts_comparisons_MK_gam <- nuts_comparisons %>% 
filter(DATE_LOCAL > "2023-03-01" & DATE_LOCAL < "2024-08-01") %>% 
  group_by(DATE_LOCAL) %>% 
   summarize(temp_C = mean(temp_C),
             `NO2+NO3 (umol/l)` = `NO2+NO3 (umol/l)`) %>% 
   mutate(T2N_nitrate_MK_GAM = predict(gam_model_mk, newdata = .))


t2n_measuredN_lm2 <- lmodel2(T2N_nitrate_MK_GAM ~ `NO2+NO3 (umol/l)`, data = nuts_comparisons_MK_gam)

t2n_measuredN_lm2 # T2N and measured NO3, r2 = 0.74, p < 0.001, y = 0.83x + 0.26

nuts_comparisons_MK_gam_this_study <- nuts_comparisons_MK_gam %>% 
  mutate(sample_dates = case_when(
    DATE_LOCAL > "2023-03-01" & DATE_LOCAL < "2024-08-01" ~ "During this study",
    TRUE ~ "All other samples"
  )) %>% 
  filter(sample_dates == "During this study")


t2n_comp_p <- nuts_comparisons_MK_gam %>% 
  ggplot(aes(y = T2N_nitrate_MK_GAM, x =`NO2+NO3 (umol/l)`)) +
  geom_point(shape = 21,
             color = "black",
             size = 4) +
  labs(x = "Measured Nitrate (µM)",
       y = "T2N Nitrate (µM)") +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed", size = 1) +
  geom_abline(slope = 0.85, y = 0.79, size = 1) +
  theme(panel.background = element_rect(fill = "white", color = "black", size = 1),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = margin(1,1,1,1, "cm"),
        legend.key = element_rect(fill = "white"),
        legend.text = element_text(size = 20),
        legend.key.height = unit(0.8, "inch"),
        legend.key.width = unit(0.4, "inch"),
        legend.title = element_text(size = 24),
        axis.title.y.right = element_text(color = "blue", size = 20),
        axis.text.y = element_text(size = 15, color = "black"),
        axis.title.y.left = element_text(size = 20),
        axis.text.x = element_text(size = 15 , color = "black"),
        axis.title.x = element_text(size = 20),
        text = element_text(family = "Helvetica"))

t2n_comp_p_this_study <- nuts_comparisons_MK_gam_this_study %>% 
  ggplot(aes(y = T2N_nitrate_MK_GAM, x =`NO2+NO3 (umol/l)`)) +
  geom_point(shape = 21,
             size = 4, 
             color = "black") +
  labs(x = "Measured Nitrate (µM)",
       y = "T2N Nitrate (µM)") +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed", size = 1) +
  geom_abline(slope = 0.85, y = 0.79, size = 1) +
  theme(panel.background = element_rect(fill = "white", color = "black", size = 1.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = margin(1,1,1,1, "cm"),
        legend.key = element_rect(fill = "white"),
        legend.text = element_text(size = 20),
        legend.key.height = unit(0.8, "inch"),
        legend.key.width = unit(0.4, "inch"),
        legend.title = element_text(size = 24),
        axis.title.y.right = element_text(color = "blue", size = 20),
        axis.text.y = element_text(size = 15, color = "black"),
        axis.title.y.left = element_text(size = 20),
        axis.text.x = element_text(size = 15 , color = "black"),
        axis.title.x = element_text(size = 20),
        text = element_text(family = "Helvetica"))


ggsave("T2N_comparison.pdf", plot = t2n_comp_p, path = "/Users/chanceenglish/Desktop/Lab Shiz/ARPA-e/Giant_Kelp_DOC/Figures/HQ Figs Metabolites/", width = 4, height = 4, device='pdf', dpi=250, units = "in")
  

```

## B

```{r}

MP_DOC_NPP_phys_env_sum <- read_csv(here("Data", "MP_DOC_NPP_phys_env_sum.csv"))

MP_DOC_NPP_phys_env_sum_chlval <- MP_DOC_NPP_phys_env_sum %>% 
  select(age_d,
         season,
         blade,
         date,
         Chl_C) %>% 
  unique() 


Chl_C_age_summer <- MP_DOC_NPP_phys_env_sum %>% 
  filter(season == "Summer") %>% 
  group_by(age_d) %>% 
  filter(Chl_C != "NA", 
         lightlevel_timepoint %in% c(1,2)) %>% 
  summarise(Chl_C_avg = mean(Chl_C), 
            sd_Chl_C = sd(Chl_C),
            season = season) %>% 
  ungroup() 




Chl_C_age_spring <- MP_DOC_NPP_phys_env_sum %>% 
  filter(season == "Spring") %>% 
  group_by(age_d) %>% 
  filter(Chl_C != "NA", 
         lightlevel_timepoint %in% c(1,2)) %>% 
  summarise(Chl_C_avg = mean(Chl_C), 
            sd_Chl_C = sd(Chl_C),
            season = season) %>% 
  ungroup() 



 Chl_C_age <- MP_DOC_NPP_phys_env_sum %>% 
  group_by(age_d) %>% 
  filter(Chl_C != "NA", 
         lightlevel_timepoint %in% c(1,2)) %>% 
  summarise(Chl_C_avg = mean(Chl_C), 
            sd_Chl_C = sd(Chl_C)) %>% 
  ungroup() %>% 
  ggplot(aes(x = age_d, 
             y = Chl_C_avg*1000)) +
  geom_point(size = 6) +
  geom_sigmoid(aes(y = Chl_C_avg[age_d==min(age_d)]*1000, 
                   yend = Chl_C_avg[age_d==max(age_d)]*1000, 
                   x = min(age_d), 
                   xend =max(age_d)), size = 1) +
  ylab(expression(Chl:C~(mg^{"1"} ~ g^{"-1"}))) +
  labs(x = "Age (d)") + 
  scale_y_continuous(labels = label_number(accuracy = 1), 
                     breaks = c(0,2,4,6,8,10), limits = c(0,10)) +
  geom_errorbar(aes(x = age_d, 
                    y = Chl_C_avg*1000, 
                    ymin =  Chl_C_avg*1000 - sd_Chl_C*1000, 
                    ymax = Chl_C_avg*1000 + sd_Chl_C*1000), 
                width = 0) +
  theme(panel.background = element_rect(fill = "white", 
                                        color = "black", 
                                        size = 1.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = margin(1,1,1,1, "cm"),
        strip.background = element_rect(fill = "white", 
                                        color = "black"),
        legend.key = element_rect(fill = "white"),
        legend.text = element_text(size = 20),
        legend.title = element_text(size = 20),
        axis.text = element_text(size = 15, 
                                 color = "black"),
        axis.title = element_text(size = 20),
        text = element_text(family = "Times"))

 
 
  
Chl_C_age_cohorts <- ggplot() +
  geom_point(aes(x = Chl_C_age_summer$age_d, 
             y = Chl_C_age_summer$Chl_C_avg*1000), 
             shape = 24, 
             size = 5) +
  geom_point(aes(x = Chl_C_age_spring$age_d, 
             y = Chl_C_age_spring$Chl_C_avg*1000),
             shape = 21, 
             size = 5) +
  geom_sigmoid(aes(y = Chl_C_age_summer$Chl_C_avg[Chl_C_age_summer$age_d==min(Chl_C_age_summer$age_d)]*1000, 
                   yend = Chl_C_age_summer$Chl_C_avg[Chl_C_age_summer$age_d==max(Chl_C_age_summer$age_d)]*1000, 
                   x = min(Chl_C_age_summer$age_d), 
                   xend = 100), 
               size = 1) +
  geom_point(aes(x = MP_DOC_NPP_phys_env_sum_chlval$age_d,
                 y = MP_DOC_NPP_phys_env_sum_chlval$Chl_C*1000,
                 shape = MP_DOC_NPP_phys_env_sum_chlval$season)) +
  ylab(expression(Chl:C~(mg^{"1"} ~ g^{"-1"}))) +
  labs(x = "Age (d)",
       shape = NULL) + 
  geom_sigmoid(aes(y = Chl_C_age_spring$Chl_C_avg[Chl_C_age_spring$age_d==min(Chl_C_age_spring$age_d)]*1000, 
                   yend = Chl_C_age_summer$Chl_C_avg[Chl_C_age_summer$age_d==max(Chl_C_age_summer$age_d)]*1000, 
                   x = min(Chl_C_age_spring$age_d), 
                   xend = 100), size = 1, shape = 16) +
  geom_vline(xintercept = 50, linetype = "dashed", size = 0.5) +
  ylab(expression(Chl:C~(mg^{"1"} ~ g^{"-1"}))) +
  labs(x = "Age (d)") + 
  scale_y_continuous(labels = label_number(accuracy = 1), 
                     breaks = c(0,5,10,15,20,25), 
                     limits = c(0,25)) +
  scale_shape_manual(labels = c("Spring", "Summer"), 
                     values = c(21,24)) +
  labs(color = "",
       shape = "Season") +
  coord_cartesian(expand = c(0,0)) +
  scale_x_continuous(breaks = c(25,50,75,100), limits = c(10,100)) +
  theme(panel.background = element_rect(fill = "white", 
                                        color = "black", 
                                        size = 1.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = margin(1,1,1,1, "cm"),
        strip.background = element_rect(fill = "white", 
                                        color = "black"),
        legend.key = element_rect(fill = "white"),
        legend.text = element_text(size = 20),
        legend.title = element_text(size = 20),
        legend.position = "none",
        axis.text = element_text(size = 15, 
                                 color = "black"),
        axis.title = element_text(size = 20),
        text = element_text(family = "Helvetica")) +
   annotate("rect", xmin = 10, xmax = 50, ymin = 0, ymax = 25,
           alpha = .25,fill = "#06558B")  +
  annotate("rect", xmin = 50.1, xmax = 100, ymin = 0, ymax = 25,
           alpha = .25,fill = "#AA4613") 








```

## C

```{r}

# C

MP_DOC_NPP_phys_env_sum_mean <- MP_DOC_NPP_phys_env_sum %>% 
  filter(season %in% c("Spring", "Summer")) %>% 
  filter(flag != 2) %>% 
  filter(lightlevel_timepoint %in% c(5,6)) %>% 
  select(age_d, NPP_umolC_g_hr, season) %>% 
  group_by(season, age_d) %>% 
  summarize(meanPmax = mean(NPP_umolC_g_hr))

MP_DOC_NPP_phys_env_sum_pmax <- MP_DOC_NPP_phys_env_sum %>% 
  filter(season %in% c("Spring", "Summer")) %>% 
  filter(flag != 2) %>% 
  filter(lightlevel_timepoint %in% c(5,6)) %>% 
  select(age_d, NPP_umolC_g_hr, season)
  
MP_Pmax_Age_p <- ggplot() +
  geom_point(aes(y = MP_DOC_NPP_phys_env_sum_pmax$NPP_umolC_g_hr, 
                    x = MP_DOC_NPP_phys_env_sum_pmax$age_d,
                    shape = MP_DOC_NPP_phys_env_sum_pmax$season)) +
  geom_point(aes(y = MP_DOC_NPP_phys_env_sum_mean$meanPmax,
                 x = MP_DOC_NPP_phys_env_sum_mean$age_d,
                 shape = MP_DOC_NPP_phys_env_sum_mean$season),
             size = 5) +
  ylab(expression(P[max]~(µmolC ~ g[DW]^{"-1"} ~ hr^{"-1"}))) +
   geom_vline(xintercept = 50, linetype = "dashed", size = 0.5) +
  labs(color = "",
       x = "Age (d)",
       shape = "",
       color = NULL) +
  scale_shape_manual(values = c(21,24)) +
  geom_abline(slope = -3.22, intercept = 260.73, size = 1, color = "black", linetype = "dashed") +
  geom_abline(slope = -1.34, intercept = 176.64, size = 1, color = "black") +
 scale_x_continuous(breaks = c(25,50,75,100), limits = c(10,100)) +
  scale_y_continuous(limits = c(-50,300), breaks = c(0,100,200,300)) +
  geom_hline(yintercept = 0, color = "black", size= 1, linetype = "dashed") +
  theme(panel.background = element_rect(fill = "white", 
                                        color = "black", 
                                        size = 1.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = margin(1,1,1,1, "cm"),
        legend.key.height = unit(0.7, "inch"),
        legend.key.width = unit(0.4, "inch"),
        legend.key = element_rect(fill = "white",color = NA),
        strip.background = element_rect(fill = "white", 
                                        color = "black"),
        legend.text = element_text(size = 20),
        legend.position = "right",
        legend.title = element_text(size = 20),
        axis.text = element_text(size = 15, 
                                 color = "black"),
        axis.title = element_text(size = 20),
        text = element_text(family = "Helvetica")) +
  guides(shape = guide_legend(override.aes = list(size = 5))) +
  annotate("rect", xmin = -Inf, xmax = 50, ymin = -Inf, ymax = Inf,
           alpha = .25,fill = "#06558B")  +
  annotate("rect", xmin = 50.1, xmax = Inf, ymin = -Inf, ymax = Inf,
           alpha = .25,fill = "#AA4613") 




```

## Merge A,B,C together 

```{r}

library(cowplot)

bottom_row <- plot_grid(Chl_C_age_cohorts, 
                        MP_Pmax_Age_p, 
                        ncol = 2,
                        nrow = 1,
                        labels = c("B.", "C."),
                         label_fontfamily = "Helvetica",
                        label_size = 24,
                        rel_widths = c(1,1.5))


figure_1 <- plot_grid(bottom_temp, 
                      bottom_row,
                      label_fontfamily = "Helvetica", 
                      ncol = 1,
                      nrow = 2,
                      labels = c("A.",""),
                      rel_widths = c(3,1),
                      label_size = 24)


ggsave("figure_1.pdf", plot = figure_1, path = "/Users/chanceenglish/Desktop/Lab Shiz/ARPA-e/Giant_Kelp_DOC/Figures/HQ Figs Metabolites/", width = 12, height = 12, device='pdf', dpi=250, units = "in")



 ```

# Figure 2

## A

```{r}

pcoa_pos_plot_figure2A <- PCoA_NEG_metab_metadata_ft_pos %>% 
  ggplot(aes(x = pcoa1,  y = pcoa2)) +
  geom_point(aes(shape = ATTRIBUTE_season, fill = ATTRIBUTE_phys_state),
             size = 5,
             alpha = 0.7) +
  scale_color_manual(values = c("black", "black")) +
  scale_fill_manual(values = c("#06558B", "#AA4613")) +
  scale_shape_manual(values = c(21,24)) +
  scale_y_continuous(labels = label_number(accuracy = 0.1)) + 
  labs(x = "PCo 1 (21.5%)",
       y = "PCo 2 (16.1%)") +
   theme(panel.background = element_rect(fill = "white", color = "black", size = 1.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = margin(1,1,1,1, "cm"),
        legend.key = element_rect(fill = "white",color = NA),
        legend.text = element_text(size = 20),
        legend.position = "none",
        legend.title = element_blank(),
        axis.text = element_text(size = 15, color = "black"),
        axis.title = element_text(size = 20),
        text = element_text(family = "Helvetica")) +
  stat_ellipse(aes(x = pcoa1,  
                   y = pcoa2, 
                   color = ATTRIBUTE_phys_state,
                   fill = ATTRIBUTE_phys_state),
               geom = "polygon", alpha = 0.2,
               level = 0.95) +
  guides(shape = guide_legend(override.aes = list(size = 5)))



```


## B

```{r}

pcoa_neg_plot_figure2B <- PCoA_NEG_metab_metadata_ft %>% 
  ggplot(aes(x = pcoa1,  y = pcoa2)) +
  geom_point(aes(shape = ATTRIBUTE_season, fill = ATTRIBUTE_phys_state),
             size = 5,
             alpha = 0.7) +
  scale_color_manual(values = c("black", "black")) +
  scale_fill_manual(values = c("#06558B", "#AA4613")) +
  scale_shape_manual(values = c(21,24)) +
  scale_y_continuous(labels = label_number(accuracy = 0.1)) + 
  labs(x = "PCo 1 (19.8%)",
       y = "PCo 2 (12.9%)") +
   theme(panel.background = element_rect(fill = "white", color = "black", size = 1.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = margin(1,1,1,1, "cm"),
        legend.key = element_rect(fill = "white",color = NA),
        legend.text = element_text(size = 20),
        legend.position = "right",
        legend.title = element_blank(),
        axis.text = element_text(size = 15, color = "black"),
        axis.title = element_text(size = 20),
        text = element_text(family = "Helvetica")) +
  stat_ellipse(aes(x = pcoa1,  
                   y = pcoa2, 
                   color = ATTRIBUTE_phys_state,
                   fill = ATTRIBUTE_phys_state),
               geom = "polygon", alpha = 0.2,
               level = 0.95) +
  guides(shape = guide_legend(override.aes = list(size = 5)))



```


## A,B combined 

```{r}

figure2 <- plot_grid(pcoa_pos_plot_figure2A, 
                        pcoa_neg_plot, 
                        ncol = 2,
                        nrow = 1,
                        labels = c("A.", "B."),
                         label_fontfamily = "Helvetica",
                        label_size = 24,
                        rel_widths = c(1,1.3))

```

# Figure 3

## A and B

```{r}

formula_p_pos <- ggboxplot(formulas_simple_POS,
                   x = "formula_class",
                  y = "Proportion", 
                  color = "ATTRIBUTE_phys_state",
                  shape = "ATTRIBUTE_season",
                  palette = my_pallet,
                  add = "jitter") +
  stat_compare_means(aes(x = formula_class, 
                   y = Proportion,
                   group = ATTRIBUTE_phys_state),
                   size = 6) +
  labs(x = "",
       y = "Proportion of Formulas",
       fill = "") +
  theme(panel.background = element_rect(fill = "white", color = "black", size = 1.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = margin(1,1,1,1, "cm"),
        strip.background = element_rect(fill = "white", color = "black"),
        legend.key = element_rect(fill = "white",color = NA),
        legend.text = element_text(size = 15),
        legend.key.height = unit(0.5, "inch"),
        legend.key.width = unit(0.4, "inch"),
        legend.position = "none",
        legend.title = element_blank(),
        axis.text = element_text(size = 15, color = "black"),
        axis.title = element_text(size = 15),
        text = element_text(family = "Helvetica")) +
  coord_cartesian(expand = c(0,1)) +
  scale_y_continuous(limits = c(0,1), breaks = c(0,0.2,0.4,0.6,0.8,1.0)) +
  guides(shape = guide_legend(override.aes = list(size = 5))) +
  guides(color = guide_legend(override.aes = list(shape = NA)))



formula_p_NEG <- ggboxplot(formulas_simple_NEG,
                  x = "formula_class",
                  y = "Proportion", 
                  color = "ATTRIBUTE_phys_state",
                  shape = "ATTRIBUTE_season",
                  palette = my_pallet,
                  add = "jitter") +
  stat_compare_means(aes(x = formula_class, 
                   y = Proportion,
                   group = ATTRIBUTE_phys_state),
                   size = 6) +
  labs(x = "",
       y = "Proportion of Formulas",
       fill = "") +
  theme(panel.background = element_rect(fill = "white", color = "black", size = 1.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = margin(1,1,1,1, "cm"),
        strip.background = element_rect(fill = "white", color = "black"),
        legend.key = element_rect(fill = "white",color = NA),
        legend.text = element_text(size = 15),
        legend.key.height = unit(0.5, "inch"),
        legend.key.width = unit(0.4, "inch"),
        legend.position = "right",
        legend.title = element_blank(),
        axis.text = element_text(size = 15, color = "black"),
        axis.title = element_text(size = 15),
        text = element_text(family = "Helvetica")) +
  coord_cartesian(expand = c(0,1)) +
  scale_y_continuous(limits = c(0,1), breaks = c(0,0.2,0.4,0.6,0.8,1.0)) +
  guides(shape = guide_legend(override.aes = list(size = 5))) +
  guides(color = guide_legend(override.aes = list(shape = NA))) 


fig3_top_row <- plot_grid(formula_p_pos, 
                        exo_CN_tissue_CN_pos_p, 
                        ncol = 1,
                        nrow = 2,
                        align = "v",
                        labels = c("A.", "C."),
                         label_fontfamily = "Helvetica",
                        label_size = 24,
                        rel_widths = c(1,1))





```

## C and D


```{r}



CNexo_CNtisssue_p_NEG <- molecular_stoichiometryCN %>% 
  ggplot(aes(x = ATTRIBUTE_tissue_CN, y = weighted_CN, shape = ATTRIBUTE_season, color = ATTRIBUTE_age_d)) +
 geom_point(aes(shape = ATTRIBUTE_season, 
                fill = ATTRIBUTE_age_d),
             size = 5,
             alpha = 0.7,
            color = "black") +
  scale_shape_manual(values = c(21,24)) +
  scale_y_continuous(labels = label_number(accuracy = 0.1)) + 
  geom_smooth(method = "lm",se = F, color = "black", size = 1) +
  labs(x = "Tissue C:N",
       y = "Exometabolite C:N (weighted)",
      fill = "Age (d)",
      shape = NULL) +
  coord_cartesian(expand = c(0,0)) +
  scico::scale_fill_scico(palette = "vik", breaks = c(0,25,50,75,100)) +
  scale_y_continuous(breaks = c(0,5,10,15,20,25,30), limits = c(0,30)) +
  scale_x_continuous(breaks = c(0,5,10,15,20,25,30,35,40,45), limits = c(0,45)) +
  theme(panel.background = element_rect(fill = "white", color = "black", size = 1.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = margin(1,1,1,1, "cm"),
        strip.background = element_rect(fill = "white", color = "white"),
        legend.key = element_rect(fill = "white", color = NA),
        legend.text = element_text(size = 15),
        legend.key.height = unit(0.4, "inch"),
        legend.key.width = unit(0.2, "inch"),
        legend.position = "right",
        legend.title = element_text(size = 20),
        axis.text = element_text(size = 15, color = "black"),
        axis.title = element_text(size = 15),
        text = element_text(family = "Helvetica")) +
  guides(shape = guide_legend(override.aes = list(size = 5)))



exo_CN_tissue_CN_pos_p <- molecular_stoichiometryCN_POS %>% 
  ggplot(aes(x = ATTRIBUTE_tissue_CN, y = weighted_CN, shape = ATTRIBUTE_season)) +
 geom_point(aes(shape = ATTRIBUTE_season, 
                fill = ATTRIBUTE_age_d),
             size = 5,
             alpha = 0.7,
            color = "black") +
  scale_shape_manual(values = c(21,24)) +
  scale_y_continuous(labels = label_number(accuracy = 0.1)) + 
  geom_smooth(method = "lm",se = F, color = "black", size = 1) +
  labs(x = "Tissue C:N",
       y = "Exometabolite C:N (weighted)",
      color = "Age (d)",
      shape = NULL) +
  scico::scale_fill_scico(palette = "vik", breaks = c(0,25,50,75,100)) +
  coord_cartesian(expand = c(0,0)) +
 scale_y_continuous(breaks = c(0,5,10,15,20,25,30), limits = c(0,30)) +
  scale_x_continuous(breaks = c(0,5,10,15,20,25,30,35,40,45), limits = c(0,45)) +
  theme(panel.background = element_rect(fill = "white", color = "black", size = 1.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = margin(1,1,1,1, "cm"),
        strip.background = element_rect(fill = "white", color = "white"),
        legend.key = element_rect(fill = "white", color = NA),
        legend.text = element_text(size = 15),
        legend.key.height = unit(0.4, "inch"),
        legend.key.width = unit(0.2, "inch"),
        legend.position = "none",
        legend.title = element_text(size = 20),
        axis.text = element_text(size = 15, color = "black"),
        axis.title = element_text(size = 15),
        text = element_text(family = "Helvetica")) +
  guides(shape = guide_legend(override.aes = list(size = 5)))



fig3_bottom_row <- plot_grid(formula_p_NEG,
                             CNexo_CNtisssue_p_NEG, 
                        ncol = 1,
                        nrow = 2,
                        align = "v",
                        labels = c("B.", "D."),
                         label_fontfamily = "Helvetica",
                        label_size = 24,
                        rel_widths = c(1,1))


```

## A, B, C, D

```{r}



fig3 <- plot_grid(fig3_top_row,
                  fig3_bottom_row,
                  ncol = 2,
                  align = "hv",
                  axis = "bt",
                         label_fontfamily = "Helvetica",
                        label_size = 24,
                  rel_widths = c(1.1,1.5))


ggsave("fig3.pdf", plot = fig3, path = "/Users/chanceenglish/Desktop/Lab Shiz/ARPA-e/Giant_Kelp_DOC/Figures/HQ Figs Metabolites/", width = 12, height = 12, device='pdf', dpi=250, units = "in")



```


# Figure 5

## A

```{r}

AAPA_p <- fqt_class_metadata_RA_subnetwork_sum %>% 
  filter(`ClassyFire#subclass` == "Amino acids, peptides, and analogues", 
         ATTRIBUTE_season != "September") %>% 
  group_by(ATTRIBUTE_age_d, ATTRIBUTE_season, ATTRIBUTE_blade) %>% 
  summarize(sum_rpa = sum(rpa)) %>% 
  ungroup() %>% 
  group_by(ATTRIBUTE_age_d, ATTRIBUTE_season) %>% 
  mutate(mean_rpa = mean(sum_rpa),
         sd_rpa = sd(sum_rpa)) %>% 
  distinct() %>% 
  ggplot() +
  geom_point(aes(x = ATTRIBUTE_age_d, y = sum_rpa*100, shape = ATTRIBUTE_season)) +
  geom_point(aes(x = ATTRIBUTE_age_d, y = mean_rpa*100, shape = ATTRIBUTE_season), size = 5) +
  geom_line(aes(x = ATTRIBUTE_age_d, y = mean_rpa*100, shape = ATTRIBUTE_season ), size = 0.5) +
  labs(x = "Age (d)",
       y = "Amino Acids, Peptides, analogues \n (% RPA)",
       shape = NULL) +
  scale_shape_manual(values = c(1,2)) +
  scale_x_continuous(breaks = c(10,20,30,40,50,60,70,80,90), limits = c(10,90)) +
  scale_y_continuous(breaks = c(0,10,20,30,40), limits = c(0,40)) +
  coord_cartesian(expand = c(0,0)) +
   theme(panel.background = element_rect(fill = "white", color = "black", size = 1.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = margin(1,1,1,1, "cm"),
        strip.background = element_rect(fill = "white", color = "black"),
        legend.key = element_rect(fill = "white",color = NA),
        legend.text = element_text(size = 15),
        legend.key.height = unit(0.5, "inch"),
        legend.key.width = unit(0.4, "inch"),
        legend.title = element_blank(),
        legend.position = "none",
        axis.text = element_text(size = 15, color = "black"),
        axis.title = element_text(size = 20),
        text = element_text(family = "Helvetica")) +
   annotate("rect", xmin = 10, xmax = 50, ymin = 0, ymax = 40,
           alpha = .25,fill = "#06558B")  +
  annotate("rect", xmin = 50.1, xmax = 90, ymin = 0, ymax = 40,
           alpha = .25,fill = "#AA4613") 




```


## B

```{r}

halo_aro_p <- fqt_class_metadata_RA_subnetwork_sum %>% 
  filter(`ClassyFire#subclass` %in% c("Halophenols", "Aryl chlorides", "Aryl bromides", "Aryl iodides", "1,4−dihydroxy−2−halobenzenoids"), 
         ATTRIBUTE_season != "September") %>% 
  group_by(ATTRIBUTE_age_d, ATTRIBUTE_season, ATTRIBUTE_blade) %>% 
  summarize(sum_rpa = sum(rpa)) %>% 
  ungroup() %>% 
  group_by(ATTRIBUTE_age_d, ATTRIBUTE_season) %>% 
  mutate(mean_rpa = mean(sum_rpa),
         sd_rpa = sd(sum_rpa)) %>% 
  distinct() %>% 
  ggplot() +
  geom_point(aes(x = ATTRIBUTE_age_d, y = sum_rpa*100, shape = ATTRIBUTE_season)) +
  geom_point(aes(x = ATTRIBUTE_age_d, y = mean_rpa*100, shape = ATTRIBUTE_season), size = 5) +
  geom_line(aes(x = ATTRIBUTE_age_d, y = mean_rpa*100, shape = ATTRIBUTE_season ), size = 0.5) +
  scale_x_continuous(breaks = c(10,20,30,40,50,60,70,80,90), limits = c(10,90)) +
  scale_y_continuous(breaks = c(0,10,20,30,40), limits = c(0,40)) +
  labs(x = "Age (d)",
       y = "Halogenated Aromatics (% RPA)",
       shape = NULL) +
  coord_cartesian(expand = c(0,0)) +
  scale_shape_manual(values = c(1,2)) +
   theme(panel.background = element_rect(fill = "white", color = "black", size = 1.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = margin(1,1,1,1, "cm"),
        strip.background = element_rect(fill = "white", color = "black"),
        legend.key = element_rect(fill = "white",color = NA),
        legend.text = element_text(size = 15),
        legend.key.height = unit(0.5, "inch"),
        legend.key.width = unit(0.4, "inch"),
        legend.title = element_blank(),
        legend.position = "none",
        axis.text = element_text(size = 15, color = "black"),
        axis.title = element_text(size = 20),
        text = element_text(family = "Helvetica")) +
   annotate("rect", xmin = 10, xmax = 50, ymin = 0, ymax = 40,
           alpha = .25,fill = "#06558B")  +
  annotate("rect", xmin = 50.1, xmax = 90, ymin = 0, ymax = 40,
           alpha = .25,fill = "#AA4613") 




```


## C

```{r}

cBR_p <- molecular_stoichiometryCBr %>% 
  group_by(ATTRIBUTE_season, ATTRIBUTE_age_d) %>% 
  summarize(mean_CBR = mean(weighted_CX),
            weighted_CX = weighted_CX) %>% 
  ggplot() +
  geom_point(aes(x = ATTRIBUTE_age_d, y = weighted_CX, shape = ATTRIBUTE_season)) +
  geom_point(aes(x = ATTRIBUTE_age_d, y = mean_CBR, shape = ATTRIBUTE_season), size = 5) +
  geom_line(aes(x = ATTRIBUTE_age_d, y = mean_CBR, shape = ATTRIBUTE_season ), size = 0.5) +
  labs(x = "Age (d)",
       y = "Exudate Br:C \n (Peak Area Weighted)",
       shape = NULL) +
  scale_shape_manual(values = c(1,2)) +
  scale_x_continuous(breaks = c(10,20,30,40,50,60,70,80,90), limits = c(10,90)) +
  scale_y_continuous(breaks = c(0,0.03,0.06,0.09,0.12,0.15), limits = c(0,0.15)) +
  coord_cartesian(expand = c(0,0)) +
   theme(panel.background = element_rect(fill = "white", color = "black", size = 1.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = margin(1,1,1,1, "cm"),
        strip.background = element_rect(fill = "white", color = "black"),
        legend.key = element_rect(fill = "white",color = NA),
        legend.text = element_text(size = 15),
        legend.key.height = unit(0.5, "inch"),
        legend.key.width = unit(0.4, "inch"),
        legend.title = element_blank(),
        legend.position = "right",
        axis.text = element_text(size = 15, color = "black"),
        axis.title = element_text(size = 20),
        text = element_text(family = "Helvetica")) +
   annotate("rect", xmin = 10, xmax = 50, ymin = 0, ymax = 0.15,
           alpha = .25,fill = "#06558B")  +
  annotate("rect", xmin = 50.1, xmax = 90, ymin = 0, ymax = 0.15,
           alpha = .25,fill = "#AA4613") 



```

## combined 

```{r}

figure5 <- plot_grid(AAPA_p,
                     halo_aro_p,
                     cBR_p,
                     ncol = 3,
                     nrow = 1,
                     labels = c("A.", "B.","C."),
                     label_fontfamily = "Helvetica",
                     label_size = 24,
                     rel_widths = c(1,1,1.5))


ggsave("figure5.pdf", plot = figure5, path = "/Users/chanceenglish/Desktop/Lab Shiz/ARPA-e/Giant_Kelp_DOC/Figures/HQ Figs Metabolites/", width = 16, height = 6, device='pdf', dpi=250, units = "in")

```

# Figure 6

## A

```{r}

bioavailability_p <- DOM_remin %>% 
  filter(kelp_collection_date != 240211) %>% 
  ggplot(aes(x = days, y = DOC_uMC, fill = age_d, shape = treatment)) +
  geom_point(color = "black", size = 4, 
             position = position_jitter(width = 0.5, height = 0.5),
             alpha = 0.5) +
   labs(x = "Days",
       y = "DOC (µM C)",
       fill = "Age (d)",
       shape = NULL) +
  scale_y_break(c(125, 225)) +
  scale_shape_manual(values = c(25,22)) +
  scico::scale_fill_scico(palette = "vik", breaks = c(0,25,50,75,100)) +
  scale_x_continuous(limits = c(0,100)) +
  scale_y_continuous(limits = c(50,250), breaks = c(50,75,100,125,150,175,200,225,250)) +
  theme(panel.background = element_rect(fill = "white", color = "black", size = 1.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = margin(1,1,1,1, "cm"),
        strip.background = element_rect(fill = "white", color = "black"),
        legend.key = element_rect(fill = "white", color = NA),
        legend.text = element_text(size = 15),
        legend.position = "right",
        legend.key.height = unit(0.5, "inch"),
        legend.key.width = unit(0.2, "inch"),
        legend.title = element_text(size = 15),
        axis.text.x = element_text(size = 15, color = "black"),
        axis.text.y = element_text(size = 15, color = "black"),
        axis.title.y = element_text(size = 20, color = "black", angle = 90, vjust = 0.5),
        axis.text.y.right = element_blank(),
        axis.title = element_text(size = 20),
        text = element_text(family = "Helvetica")) 



```


## B

```{r}

norm_bioavailability_p <- DOM_remin_norm %>% 
  filter(age_d != 14) %>% 
  ggplot(aes(x = days, y = DOC_norm, fill = age_d)) +
  geom_point(color = "black", 
             size = 4, 
             shape = 22,
             position = position_jitter(width = 0.5, height = 0.5),
             alpha = 0.5) +
   labs(x = "Days",
       y = "DOC Normalized (% Initial)",
       fill = "Age (d)",
       shape = NULL) +
  scico::scale_fill_scico(palette = "vik", breaks = c(0,25,50,75,100)) +
  scale_x_continuous(limits = c(0,100)) +
  scale_y_continuous(limits = c(0,100), breaks = c(0,25,50,75,100)) +
  theme(panel.background = element_rect(fill = "white", color = "black", size = 1.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = margin(1,1,1,1, "cm"),
        strip.background = element_rect(fill = "white", color = "black"),
        legend.key = element_rect(fill = "white", color = NA),
        legend.text = element_text(size = 15),
        legend.position = "right",
        legend.key.height = unit(0.5, "inch"),
        legend.key.width = unit(0.2, "inch"),
        legend.title = element_text(size = 15),
        axis.text.x = element_text(size = 15, color = "black"),
        axis.text.y = element_text(size = 15, color = "black"),
        axis.title.y = element_text(size = 20, color = "black"),
        axis.title = element_text(size = 20),
        text = element_text(family = "Helvetica"))


```


## Combined

```{r}

figure6 <- plot_grid(bioavailability_p,
                     norm_bioavailability_p,
                     ncol = 2,
                     nrow = 1,
                     labels = c("A.", "B."),
                     label_fontfamily = "Helvetica",
                     label_size = 24,
                     rel_widths = c(1,1))



```


# Old Data Analysis 

## Aggregate relative peak areas by most specifc class

```{r}

agg_by_mostspecificclass <- aggregate(fqt_class_metadata_RA[,19:61], 
                        by = list(fqt_class_metadata_RA$smooshedclass), 
                        FUN = sum) 


agg_by_mostspecificclass <- agg_by_mostspecificclass %>% 
  mutate(smooshedclass = Group.1) %>% 
  select(-Group.1) %>% 
  separate(smooshedclass, into = c("super_class", "class", "subclass", "most_specific_class"), sep = "_")




```


## Merge specific class aggreagated dataframe with metadata 

```{r}

agg_by_mostspecificclass_long <- agg_by_mostspecificclass %>% 
  pivot_longer(!c(super_class, class, subclass, most_specific_class), names_to = "filename", values_to = "relative_peak_area")


agg_specific_class_w_metadata <- merge(metadata_neg,agg_by_mostspecificclass_long, by = "filename")

# Remove the 9/1/24 sample: this was not part of the experiment 

crude_kelp_exudate <- agg_specific_class_w_metadata %>% 
  filter(ATTRIBUTE_sample_date == "9/1/24")


agg_specific_class_w_metadata <- agg_specific_class_w_metadata %>% 
  filter(ATTRIBUTE_sample_date != "9/1/24")



```

## Summarize by class and subclass for stacked barplot

```{r}

# Agg and sum by class level

agg_metadata_class_level <- agg_specific_class_w_metadata %>% 
  group_by(ATTRIBUTE_sample_date, ATTRIBUTE_age_d, ATTRIBUTE_season, ATTRIBUTE_blade, class) %>% 
  summarize(class_rpa = sum(relative_peak_area),
            ATTRIBUTE_phys_state = ATTRIBUTE_phys_state,
            super_class = super_class) %>% 
  filter(class_rpa > 0.01)



 agg_metadata_class_level_sum <- agg_metadata_class_level %>% 
  group_by(ATTRIBUTE_sample_date, ATTRIBUTE_age_d,class) %>% 
  summarize(mean_pa = mean(class_rpa),
            sd_pa = sd(class_rpa),
            ATTRIBUTE_phys_state = ATTRIBUTE_phys_state,
            super_class = super_class) %>% 
   unique()
 
 
# Agg and sum by subclass level

 
agg_metadata_subclass_level <- agg_specific_class_w_metadata %>% 
  group_by(ATTRIBUTE_sample_date, ATTRIBUTE_age_d, ATTRIBUTE_season, ATTRIBUTE_blade,subclass, ATTRIBUTE_phys_state) %>% 
  summarize(subclass_rpa = sum(relative_peak_area))

agg_metadata_subclass_level_sum <- agg_metadata_subclass_level %>% 
  group_by(ATTRIBUTE_sample_date, ATTRIBUTE_age_d,subclass) %>% 
  summarize(mean_pa = mean(subclass_rpa),
            sd_pa = sd(subclass_rpa),
            phys_state = ATTRIBUTE_phys_state)

```

## Class level sum plots

```{r}

agg_metadata_class_level %>% 
  filter(class == "Phenols") %>% 
  ggplot(aes(x = ATTRIBUTE_age_d, y = class_rpa, color = ATTRIBUTE_season)) +
  geom_point(size = 4) +
  labs(x = "Age (d)",
       y = "Phenols (% RPA)") +
  theme(panel.background = element_rect(fill = "white", color = "black", size = 1.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = margin(1,1,1,1, "cm"),
        strip.background = element_rect(fill = "white", color = "black"),
        legend.key = element_rect(fill = "white"),
        legend.text = element_text(size = 15),
        legend.key.height = unit(0.5, "inch"),
        legend.key.width = unit(0.4, "inch"),
        legend.title = element_text(size = 15),
        axis.text = element_text(size = 15, color = "black"),
        axis.title = element_text(size = 15),
        text = element_text(family = "Times")) 
  

agg_metadata_class_level_Phys_sum <- agg_metadata_class_level %>% 
  group_by(ATTRIBUTE_phys_state, class) %>% 
  summarize(mean_rpa = mean(class_rpa),
            sd_rpa = sd(class_rpa),
            ATTRIBUTE_phys_state = ATTRIBUTE_phys_state,
            super_class = super_class) %>% 
  unique() %>% 
  ungroup() %>% 
  mutate(class = ifelse(class == "NA", super_class, class))


```

## Tree Plots

```{r}

agg_metadata_class_level_Phys_sum <- agg_metadata_class_level %>% 
  group_by(ATTRIBUTE_phys_state, class) %>% 
  summarize(mean_rpa = mean(class_rpa),
            sd_rpa = sd(class_rpa),
            ATTRIBUTE_phys_state = ATTRIBUTE_phys_state,
            super_class = super_class) %>% 
  unique() %>% 
  ungroup() %>% 
  mutate(class = ifelse(class == "NA", super_class, class))


mature_look <- agg_metadata_class_level_Phys_sum %>% 
  mutate(class = factor(class)) %>% 
  filter(ATTRIBUTE_phys_state == "Mature")

my_palette <- colorRampPalette(brewer.pal(10, "Set2"))(10)

png(filename = "treemap_output_mature.png", width = 800, height = 600, units = "px")

agg_metadata_class_level_Phys_sum %>% 
  mutate(class = factor(class)) %>% 
  filter(ATTRIBUTE_phys_state == "Mature") %>% 
  treemap(vColor = "super_class",
          index= c("super_class","class"),
          fontcolor.labels = c("transparent", "black"),
            vSize="mean_rpa",
            type="categorical",
          overlap.labels = 1,
          palette = my_palette,
          border.col = c("black", "white"),
          bg.labels = c("transparent"),
          title = "Mature Exudates",
          border.lwds = c(2, 2))

dev.off()

## Create treemap of senescent exudates 

png(filename = "treemap_output_senescent.png", width = 800, height = 600, units = "px")

agg_metadata_class_level_Phys_sum %>% 
  mutate(class = factor(class)) %>% 
  filter(ATTRIBUTE_phys_state == "Senescent") %>% 
  treemap(vColor = "super_class",
          index= c("super_class","class"),
          fontcolor.labels = c("transparent", "black"),
            vSize="mean_rpa",
            type="categorical",
          overlap.labels = 1,
          palette = my_palette,
          border.col = c("black", "white"),
          bg.labels = c("transparent"),
          title = "Senescent Exudates",
          title.legend = "Superclass",
          border.lwds = c(2, 1))

dev.off()


```


## Amino acids, peptides, and analogues 

```{r}

agg_metadata_subclass_level <- agg_specific_class_w_metadata %>% 
  group_by(ATTRIBUTE_sample_date, ATTRIBUTE_age_d, ATTRIBUTE_season,ATTRIBUTE_blade, subclass) %>% 
  summarize(subclass_rpa = sum(relative_peak_area))

agg_metadata_subclass_level_sum <- agg_metadata_subclass_level %>% 
  group_by(ATTRIBUTE_sample_date, ATTRIBUTE_age_d, ATTRIBUTE_season,subclass) %>% 
  summarize(mean_pa = mean(subclass_rpa),
            sd_pa = sd(subclass_rpa),
            season = ATTRIBUTE_season)


amino_acid_p <- agg_metadata_subclass_level_sum %>% 
  filter(subclass == "Amino acids, peptides, and analogues") %>% 
  ggplot(aes(x = ATTRIBUTE_age_d, y = mean_pa*100, shape = season)) +
  geom_point(size = 4) +
  labs(x = "Age (d)",
       y = "Amino Acids, Peptides, analogues \n (% RPA)",
       shape = NULL) +
  geom_line(size =1.5) +
  scale_x_continuous(limits = c(10, 90), breaks = c(10,30,50,70,90)) +
  scale_y_continuous(limits = c(0, 60), breaks = c(0,20,40,60)) +
  geom_errorbar(aes(ymin = mean_pa*100 - sd_pa*100, ymax = mean_pa*100 + sd_pa*100), width = 0, alpha = 0.5, color = "black") +
 theme(panel.background = element_rect(fill = "white", color = "black", size = 1.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = margin(1,1,1,1, "cm"),
        strip.background = element_rect(fill = "white", color = "black"),
        legend.key = element_rect(fill = "white",color = NA),
        legend.text = element_text(size = 15),
        legend.key.height = unit(0.5, "inch"),
        legend.key.width = unit(0.4, "inch"),
        legend.title = element_blank(),
        legend.position = "none",
        axis.text = element_text(size = 15, color = "black"),
        axis.title = element_text(size = 20),
        text = element_text(family = "Times")) 



```

## Halophenols 

```{r}


halopehnols_p <- agg_metadata_subclass_level_sum %>% 
  filter(subclass == "Halophenols") %>% 
  ggplot(aes(x = ATTRIBUTE_age_d, y = mean_pa*100, shape = season)) +
  geom_point(size = 5) +
  geom_line(size = 1.5) +
  labs(x = "Age (d)",
       y = "Halophenols (RPA %)",
       shape = NULL) +
  geom_errorbar(aes(ymin = mean_pa*100 - sd_pa*100, ymax = mean_pa*100 + sd_pa*100), width = 0, alpha = 0.5) +
  scale_x_continuous(limits = c(10, 90), breaks = c(10,30,50,70,90)) +
  scale_y_continuous(limits = c(0, 20), breaks = c(0,5,10,15,20)) +
  theme(panel.background = element_rect(fill = "white", color = "black", size = 1.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = margin(1,1,1,1, "cm"),
        strip.background = element_rect(fill = "white", color = "black"),
        legend.key = element_rect(fill = "white",color = NA),
        legend.text = element_text(size = 15),
        legend.key.height = unit(0.5, "inch"),
        legend.key.width = unit(0.4, "inch"),
        legend.title = element_blank(),
        legend.position = "none",
        axis.text = element_text(size = 15, color = "black"),
        axis.title = element_text(size = 20),
        text = element_text(family = "Times")) 




```


## Phenols: most specific class

```{r}


agg_metadata_mspclass_level <- agg_specific_class_w_metadata %>% 
  group_by(ATTRIBUTE_sample_date, ATTRIBUTE_age_d, ATTRIBUTE_season, ATTRIBUTE_blade, most_specific_class) %>% 
  summarize(class_rpa = sum(relative_peak_area)) %>% 
  filter(class_rpa > 0.01)

agg_metadata_mspclass_level_sum <- agg_metadata_mspclass_level %>% 
  group_by(ATTRIBUTE_sample_date, ATTRIBUTE_age_d,ATTRIBUTE_season, most_specific_class) %>% 
  summarize(mean_pa = mean(class_rpa),
            sd_pa = sd(class_rpa)) 

agg_metadata_mspclass_level_sum %>% 
  filter(most_specific_class == "O-bromophenols") %>% 
  ggplot(aes(x = ATTRIBUTE_age_d, y = mean_pa, color = ATTRIBUTE_season)) +
  geom_point(size = 4)

# Agg by class

agg_metadata_class_level <- agg_specific_class_w_metadata %>% 
  group_by(ATTRIBUTE_sample_date, ATTRIBUTE_age_d, ATTRIBUTE_season, ATTRIBUTE_blade, class) %>% 
  summarize(class_rpa = sum(relative_peak_area)) %>% 
  filter(class_rpa > 0.01)

agg_metadata_class_level_sum <- agg_metadata_class_level %>% 
  group_by(ATTRIBUTE_sample_date, ATTRIBUTE_age_d,ATTRIBUTE_season, class) %>% 
  summarize(mean_pa = mean(class_rpa),
            sd_pa = sd(class_rpa)) 

agg_metadata_class_level_sum %>% 
  filter(class == "Phenols") %>% 
  ggplot(aes(x = ATTRIBUTE_age_d, y = mean_pa, color = ATTRIBUTE_season)) +
  geom_point(size = 4) +
  labs(x = "Age (d)",
       y = "Phenols (% Relative Peak Area)")


```

## Prepare data for PCoA and PERMANOVA for dev stage using most specific class grouping

```{r}

agg_specific_class_w_metadata_pca_prep <- agg_specific_class_w_metadata %>% 
  select(ATTRIBUTE_sample_date, ATTRIBUTE_phys_state, ATTRIBUTE_season, ATTRIBUTE_age_d, ATTRIBUTE_blade, most_specific_class, relative_peak_area) 

  
agg_specific_class_w_metadata_pca_shape <- agg_specific_class_w_metadata_pca_prep %>% 
  spread(key = most_specific_class, value = relative_peak_area)


agg_specific_class_w_metadata_pca_shape <- agg_specific_class_w_metadata_pca_shape[, colSums(agg_specific_class_w_metadata_pca_shape != 0) > 0]


neg_metab_numeric <- agg_specific_class_w_metadata_pca_shape[1:42,6:360]

neg_metab_numeric_angtransformed <- asin(sqrt(neg_metab_numeric))

neg_metab_numeric_z_scored <- as.data.frame(scale(neg_metab_numeric_angtransformed, center = TRUE, scale = TRUE))


sugneg_metab.pca1 <- prcomp(neg_metab_numeric_z_scored, scale = FALSE)

scree_plot_neg <- fviz_eig(sugneg_metab.pca1)

sugneg_metab.pca1_df <- as.data.frame(sugneg_metab.pca1)

summary(sugneg_metab.pca1)

get_eig(sugneg_metab.pca1)

eigenvals(sugneg_metab.pca1)

print(sugneg_metab.pca1)

as.matrix(sugneg_metab.pca1)

var <- get_pca_var(sugneg_metab.pca1)

names(var)

head(var$coord)

var_import <- var$coord

```

## Principle COORDINATE Analysis (better than PCA because you can use Bray Curtis which is better for zero inflated data which is common in metabolite/microbiome data) 

```{r}

# Use the sample-centric relative abundance normalized feature table that have been arcsine transformed


bray_dist_matrix <- vegdist(neg_metab_numeric_angtransformed, method = "bray")

PCoA_NEG_metab  <-  cmdscale(bray_dist_matrix)

str(PCoA_NEG_metab)

head(PCoA_NEG_metab)

colnames(PCoA_NEG_metab) <- c("pcoa1", "pcoa2") 

PCoA_NEG_metab <- PCoA_NEG_metab %>%  
  as_tibble(rownames = "samples")

# Getting eigenvalues 

PCoA_NEG_metab_eig  <-  cmdscale(bray_dist_matrix, eig = TRUE, add = TRUE)

positions <- PCoA_NEG_metab_eig$points

head(positions)

colnames(PCoA_NEG_metab_eig$points) <- c("pcoa1", "pcoa2") 

100* PCoA_NEG_metab_eig$eig / sum(PCoA_NEG_metab_eig$eig)


# Merge with metadata 

agg_specific_class_w_metadata_pca_shape_rownames <- agg_specific_class_w_metadata_pca_shape %>% 
  mutate(samples = 1:42)

PCoA_NEG_metab_metadata <- merge(PCoA_NEG_metab, agg_specific_class_w_metadata_pca_shape_rownames, by = "samples")


#Plot PCo 1 and PCo 2 by developmental stage

PCoA_NEG_metab_metadata %>% 
  ggplot(aes(x = pcoa1,  y = pcoa2)) +
  geom_point(aes(color = ATTRIBUTE_phys_state, shape = ATTRIBUTE_season),
             size = 5) +
  scale_color_manual(values = c("grey", "orangered")) +
  scale_fill_manual(values = c("grey", "orangered")) +
  scale_y_continuous(labels = label_number(accuracy = 0.1)) + 
  labs(x = "PCo 1 (30.7%)",
       y = "PCo 2 (11.3%)") +
   theme(panel.background = element_rect(fill = "white", color = "black", size = 1.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = margin(1,1,1,1, "cm"),
        legend.key = element_rect(fill = "white",color = NA),
        legend.text = element_text(size = 20),
        legend.position = "right",
        legend.title = element_blank(),
        axis.text = element_text(size = 15, color = "black"),
        axis.title = element_text(size = 20),
        text = element_text(family = "Helvetica")) +
  stat_ellipse(aes(x = pcoa1,  
                   y = pcoa2, 
                   color = ATTRIBUTE_phys_state,
                   fill = ATTRIBUTE_phys_state),
               geom = "polygon", alpha = 0.2) +
  guides(shape = guide_legend(override.aes = list(size = 5)))


#Plot PCo 1 and PCo 2 by Season 

PCoA_NEG_metab_metadata %>% 
  ggplot(aes(x = pcoa1,  y = pcoa2)) +
  geom_point(aes(color = ATTRIBUTE_season, shape = ATTRIBUTE_phys_state),
             size = 5) +
  scale_color_manual(values = c("dodgerblue", "red")) +
  scale_fill_manual(values = c("dodgerblue", "red")) +
  scale_y_continuous(labels = label_number(accuracy = 0.1)) + 
  labs(x = "PCo 1 (30.7%)",
       y = "PCo 2 (11.3%)") +
   theme(panel.background = element_rect(fill = "white", color = "black", size = 1.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = margin(1,1,1,1, "cm"),
        legend.key = element_rect(fill = "white",color = NA),
        legend.text = element_text(size = 20),
        legend.position = "right",
        legend.title = element_blank(),
        axis.text = element_text(size = 15, color = "black"),
        axis.title = element_text(size = 20),
        text = element_text(family = "Helvetica")) +
  stat_ellipse(aes(x = pcoa1,  
                   y = pcoa2, 
                   color = ATTRIBUTE_season,
                   fill = ATTRIBUTE_season),
               geom = "polygon", alpha = 0.2) +
  guides(shape = guide_legend(override.aes = list(size = 5)))


# Mature Data Only by Season


PCoA_NEG_metab_metadata %>% 
  filter(ATTRIBUTE_phys_state == "Mature") %>% 
  ggplot(aes(x = pcoa1,  y = pcoa2)) +
  geom_point(aes(color = ATTRIBUTE_season),
             size = 5) +
  scale_color_manual(values = c("grey", "orangered")) +
  scale_fill_manual(values = c("grey", "orangered")) +
  scale_y_continuous(labels = label_number(accuracy = 0.1)) + 
  labs(x = "PCo 1 (30.7%)",
       y = "PCo 2 (11.3%)") +
   theme(panel.background = element_rect(fill = "white", color = "black", size = 1.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = margin(1,1,1,1, "cm"),
        legend.key = element_rect(fill = "white",color = NA),
        legend.text = element_text(size = 20),
        legend.position = "right",
        legend.title = element_blank(),
        axis.text = element_text(size = 15, color = "black"),
        axis.title = element_text(size = 20),
        text = element_text(family = "Helvetica")) +
  stat_ellipse(aes(x = pcoa1,  
                   y = pcoa2, 
                   color = ATTRIBUTE_season,
                   fill = ATTRIBUTE_season),
               geom = "polygon", alpha = 0.2) +
  guides(shape = guide_legend(override.aes = list(size = 5)))


# Senescent Data Only by Season

PCoA_NEG_metab_metadata %>% 
  filter(ATTRIBUTE_phys_state == "Senescent") %>% 
  ggplot(aes(x = pcoa1,  y = pcoa2)) +
  geom_point(aes(color = ATTRIBUTE_season),
             size = 5) +
  scale_color_manual(values = c("grey", "orangered")) +
  scale_fill_manual(values = c("grey", "orangered")) +
  scale_y_continuous(labels = label_number(accuracy = 0.1)) + 
  labs(x = "PCo 1 (30.7%)",
       y = "PCo 2 (11.3%)") +
   theme(panel.background = element_rect(fill = "white", color = "black", size = 1.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = margin(1,1,1,1, "cm"),
        legend.key = element_rect(fill = "white",color = NA),
        legend.text = element_text(size = 20),
        legend.position = "right",
        legend.title = element_blank(),
        axis.text = element_text(size = 15, color = "black"),
        axis.title = element_text(size = 20),
        text = element_text(family = "Helvetica")) +
  stat_ellipse(aes(x = pcoa1,  
                   y = pcoa2, 
                   color = ATTRIBUTE_season,
                   fill = ATTRIBUTE_season),
               geom = "polygon", alpha = 0.2) +
  guides(shape = guide_legend(override.aes = list(size = 5)))


```

## Permanova


```{r}

# Variance stabilize the sample centric metabolites relative adundance data

NEG_metab_c_4_permanova <- asin(sqrt(agg_specific_class_w_metadata_pca_shape[1:42,6:360]))
  

# PERMANOVA of differences in metabolite composition by physiological state


NEG_metab_phys_state_adonis <- adonis2(NEG_metab_c_4_permanova~ATTRIBUTE_phys_state, data = agg_specific_class_w_metadata_pca_shape[1:42,], method = "bray")

NEG_metab_phys_state_adonis # R2 = 0.30 p = 0.001 F = 17.027 stronger driver


# PERMANOVA of differences in metabolite composition by season

NEG_metab_season_adonis <- adonis2(NEG_metab_c_4_permanova~ATTRIBUTE_season, data = agg_specific_class_w_metadata_pca_shape[1:42,], method = "bray")

NEG_metab_season_adonis # R2 = 0.30 p = 0.001 F = 4.756, weaker driver than dev stage

# PERMANOVA of differences in metabolite composition by season : Mature Kelp

agg_specific_class_w_metadata_pca_shape_mature <- agg_specific_class_w_metadata_pca_shape %>% 
  filter(ATTRIBUTE_phys_state == "Mature")

NEG_metab_c_4_permanova_mature <- asin(sqrt(agg_specific_class_w_metadata_pca_shape_mature[1:24,6:360]))

NEG_metab_phys_state_adonis_mature <- adonis2(NEG_metab_c_4_permanova_mature~ATTRIBUTE_season, data = agg_specific_class_w_metadata_pca_shape_mature[1:24,], method = "bray")

NEG_metab_phys_state_adonis_mature # R2 = 0.26 p = 0.001 F = 7.9476


# PERMANOVA of differences in metabolite composition by season : Senescent Kelp

agg_specific_class_w_metadata_pca_shape_senescent <- agg_specific_class_w_metadata_pca_shape %>% 
  filter(ATTRIBUTE_phys_state == "Senescent")

NEG_metab_c_4_permanova_senescent <- asin(sqrt(agg_specific_class_w_metadata_pca_shape_senescent[1:18,6:360]))

NEG_metab_phys_state_adonis_senescent <- adonis2(NEG_metab_c_4_permanova_senescent~ATTRIBUTE_season, data = agg_specific_class_w_metadata_pca_shape_senescent[1:18,], method = "bray")

NEG_metab_phys_state_adonis_senescent # R2 = 0.31 p = 0.001 F = 7.3469

```
