---
title: "metabolites_POS"
output: html_document
date: "2025-08-08"
---

```{r setup, include=FALSE, echo=F, warning=F, message=F}
knitr::opts_chunk$set(echo = TRUE, message = F, echo = F, warning = F)
```

```{r, include=FALSE, echo=F, warning=F, message=F}



library(tidyverse)
library(lmodel2)
library(ggplot2)
library(readxl)
library(kableExtra)
library(scales)
library(factoextra)
library(mgcv)
library(janitor)
library(broom)
library(here)
library(rstatix)
library(ggpubr)
library(vegan)
library(ggbump)
library(RColorBrewer)
library(scico)
library(sicegar)

library(plotly)

```


# Positive Mode

# Load in metadata feature quant table, and SIRIUS formula & compound class

```{r}

metadata_pos <- read_csv(here("Data", "metabolites", "POS", "MP_Metabolites_Samples_Metadata.csv"))

fqt_pos <- read_csv(here("Data", "metabolites", "POS","240909_Chance_kelp_GNPS_V2_quant.csv"))

canopus_formula_class_pos <- read_csv(here("Data", "metabolites", "POS","canopus_formula_summary.csv"))

SIRIUS_formula_highscore_POS <- read_csv(here("Data", "metabolites", "POS","formula_identifications.csv"))

#SIRIUS_formula_highscore_POS <- SIRIUS_formula_highscore_POS %>% 
  filter(SiriusScoreNormalized >= 0.8)
```


# Merge metadata and fqt

```{r}

# Remove "Peak Area" from column names to match metadata 


fqt_pos <- fqt_pos %>%
  rename_all(~ gsub(" Peak area", "", .x))


# Reshape fqt, make row ID the rowname, make long based on column name 

fqt_pos_long <- fqt_pos %>% 
  select(`row ID`,`230809_B0.mzML`:`Chance_pooled_QC_3.mzML`) %>% 
  pivot_longer(!'row ID', names_to = "filename", values_to = "peak_area")

# Merge long fqt with metadata and remove non samples or blanks

fqt_long_metadata_pos <- merge(fqt_pos_long, metadata_pos, by = "filename") %>% 
  filter(ATTRIBUTE_source %in% c("Ambient", "Kelp", "Blank", "LCMS Water"))




```

# Filter feature table 

```{r}

# Remove background features (found in process and analytical blanks)

filtered_ids_pos <- fqt_long_metadata_pos %>%
  filter(ATTRIBUTE_source %in% c("Blank", "LCMS Water") & peak_area > 0) %>%
  pull(`row ID`)

fqt_long_metadata_blanked_pos <- fqt_long_metadata_pos %>% 
  filter(! `row ID` %in% filtered_ids_pos) %>% 
  filter(ATTRIBUTE_source %in% c("Ambient", "Kelp"))

# Remove transient features (found less than 3 times)


fqt_long_metadata_blanked_no_transient_pos <- fqt_long_metadata_blanked_pos[fqt_long_metadata_blanked_pos$`row ID` %in% names(which(table(fqt_long_metadata_blanked_pos$`row ID`) > 2)), ]


# Filter newly produced DOM (three the XIC peak area relative to the ambient water)
# Also remove acetamides


produced_DOM_ids_pos <- fqt_long_metadata_blanked_no_transient_pos %>%
  group_by(`row ID`,ATTRIBUTE_sample_date) %>% 
  filter(peak_area < 3*peak_area[ATTRIBUTE_blade == 0]) %>% 
  pull(`row ID`)


fqt_long_metadata_blanked_no_transient_produced_DOM_pos <- fqt_long_metadata_blanked_no_transient_pos %>% 
  filter(! `row ID` %in% produced_DOM_ids_pos) %>% 
  filter(ATTRIBUTE_source == "Kelp")



```

# Merge filtered quant table with canopus compounds class 

```{r}

canopus_formula_class_pos <- canopus_formula_class_pos %>% 
  mutate('row ID' = mappingFeatureId) %>% 
  select(`row ID`, molecularFormula,`ClassyFire#superclass`, `ClassyFire#class`,`ClassyFire#subclass`, `ClassyFire#most specific class`, `ClassyFire#class Probability`, `ClassyFire#most specific class Probability`)


canopus_formula_class_pos_high_class_score <- canopus_formula_class_pos %>% 
  select(-`ClassyFire#class Probability`)

#filter(`ClassyFire#class Probability` >= 0.8) %>% 

fqt_class_metadata_long_pos <- merge(fqt_long_metadata_blanked_no_transient_produced_DOM_pos, canopus_formula_class_pos_high_class_score, by = "row ID")

length(unique(fqt_class_metadata_long_pos$`row ID`)) #5580 exudate features

```

# Create a read table equivalent to 16s, 


```{r}


fqt_class_metadata_read_table_pos <- fqt_class_metadata_long_pos %>% 
  pivot_wider(names_from = filename, values_from = peak_area) 



fqt_class_metadata_read_table_pos <- fqt_class_metadata_read_table_pos %>%
          mutate(across(19:63, ~replace_na(.x, 0)))



# Make rownames and then select only peakareas to calculate relative abundances 

fqt_class_metadata_read_table_pos <- fqt_class_metadata_read_table_pos %>% 
  mutate(rownumber = 1:nrow(fqt_class_metadata_read_table_pos))

fqt_class_metadata_read_table_RA_pos <- fqt_class_metadata_read_table_pos %>%
  column_to_rownames(var = "rownumber") %>% 
  select(`240417_B2.mzML`:`240616_B5.mzML`)

# %>% # select(-c(`230823_B1.mzML`,`230823_B2.mzML`,`230823_B3.mzML`))
  
# Calculate relative peak areas 

fqt_class_metadata_read_table_RA_pos <- as.data.frame(lapply(fqt_class_metadata_read_table_RA_pos[1:45], function(x) {(x/ sum(x))}))


fqt_class_metadata_read_table_RA_rowname_column_pos <- fqt_class_metadata_read_table_RA_pos %>% 
  rownames_to_column(var = "rownumber")

# Create complimentary metadata file for relative abundnace dataframe to be merged with 

fqt_class_metadata_read_table_rownumber_pos <- fqt_class_metadata_read_table_pos %>% 
  select(`row ID`:`ClassyFire#most specific class`, rownumber)


# Create metadata file wit relative abundnaces of each sample compounds class 

fqt_class_metadata_RA_pos <- merge(fqt_class_metadata_read_table_rownumber_pos,fqt_class_metadata_read_table_RA_rowname_column_pos, by = "rownumber")

fqt_class_metadata_RA_pos <- fqt_class_metadata_RA_pos %>%
  rename_all(~ gsub("X2", "2", .x))

fqt_class_metadata_RA_pos$smooshedclass <- do.call(paste, c(fqt_class_metadata_RA_pos[c("ClassyFire#superclass", "ClassyFire#class", "ClassyFire#subclass", "ClassyFire#most specific class")], sep="_"))



```

# Prepare data for PCoA using features ids instead of grouped specific class

```{r}
fqt_class_metadata_RA_pos_PCOA_1 <- fqt_class_metadata_RA_pos %>% 
  select(`row ID`, `240417_B2.mzML`:`240616_B5.mzML`)

fqt_class_metadata_RA_pos_PCOA_2  <- fqt_class_metadata_RA_pos_PCOA_1 %>% 
pivot_longer(!c(`row ID`), names_to = "filename", values_to = "relative_peak_area")
 
fqt_class_metadata_RA_pos_PCOA_3 <- merge(metadata_pos,fqt_class_metadata_RA_pos_PCOA_2, by = "filename")

fqt_class_metadata_RA_pos_PCOA_4 <- fqt_class_metadata_RA_pos_PCOA_3 %>% 
  select(ATTRIBUTE_sample_date, ATTRIBUTE_phys_state, ATTRIBUTE_season, ATTRIBUTE_age_d, ATTRIBUTE_blade, `row ID`, relative_peak_area) %>% 
  unique()


fqt_class_metadata_RA_pos_PCOA_5 <- fqt_class_metadata_RA_pos_PCOA_4 %>% 
  pivot_wider(names_from = `row ID`, values_from = relative_peak_area, values_fn = max)

fqt_class_metadata_RA_pos_PCOA_40463 <- fqt_class_metadata_RA_pos_PCOA_5 %>% 
  select(`40463`, ATTRIBUTE_age_d, ATTRIBUTE_season)


fqt_class_metadata_RA_pos_PCOA_5 <- fqt_class_metadata_RA_pos_PCOA_5[, colSums(fqt_class_metadata_RA_pos_PCOA_5 != 0) > 0]

pos_ft_metab_numeric <- fqt_class_metadata_RA_pos_PCOA_5[1:45,6:7350]


pos_ft_metab_numeric_angtransformed <- asin(sqrt(pos_ft_metab_numeric))

pos_metab_numeric_ft_z_scored <- as.data.frame(scale(pos_ft_metab_numeric_angtransformed, center = FALSE, scale = TRUE))


bray_dist_matrix_ft_pos <- vegdist(pos_metab_numeric_ft_z_scored, method = "bray")

PCoA_metab_ft_pos  <-  cmdscale(bray_dist_matrix_ft_pos)

str(PCoA_metab_ft_pos)

head(PCoA_metab_ft_pos)

colnames(PCoA_metab_ft_pos) <- c("pcoa1", "pcoa2") 

PCoA_metab_ft_pos <- PCoA_metab_ft_pos %>%  
  as_tibble(rownames = "samples")

# Getting eigenvalues 

PCoA_metab_ft_eig_pos  <-  cmdscale(bray_dist_matrix_ft_pos, eig = TRUE, add = TRUE)

positions_ft_pos <- PCoA_metab_ft_eig_pos$points

head(positions_ft_pos)

colnames(PCoA_metab_ft_eig_pos$points) <- c("pcoa1", "pcoa2") 

100* PCoA_metab_ft_eig_pos$eig / sum(PCoA_metab_ft_eig_pos$eig)


# Merge with metadata 

fqt_class_metadata_RA_pos_PCOA_5_rownames_pos <- fqt_class_metadata_RA_pos_PCOA_5 %>% 
  mutate(samples = 1:45)

PCoA_NEG_metab_metadata_ft_pos <- merge(PCoA_metab_ft_pos, fqt_class_metadata_RA_pos_PCOA_5_rownames_pos, by = "samples")


#Plot PCo 1 and PCo 2 by developmental stage

pcoa_pos_plot <- PCoA_NEG_metab_metadata_ft_pos %>% 
  ggplot(aes(x = pcoa1,  y = pcoa2)) +
  geom_point(aes(shape = ATTRIBUTE_season, fill = ATTRIBUTE_phys_state),
             size = 5,
             alpha = 0.7) +
  scale_color_manual(values = c("black", "black")) +
  scale_fill_manual(values = c("#06558B", "#AA4613")) +
  scale_shape_manual(values = c(21,24)) +
  scale_y_continuous(labels = label_number(accuracy = 0.1)) + 
  labs(x = "PCo 1 (21.5%)",
       y = "PCo 2 (16.1%)") +
   theme(panel.background = element_rect(fill = "white", color = "black", size = 1.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = margin(1,1,1,1, "cm"),
        legend.key = element_rect(fill = "white",color = NA),
        legend.text = element_text(size = 20),
        legend.position = "right",
        legend.title = element_blank(),
        axis.text = element_text(size = 15, color = "black"),
        axis.title = element_text(size = 20),
        text = element_text(family = "Helvetica")) +
  stat_ellipse(aes(x = pcoa1,  
                   y = pcoa2, 
                   color = ATTRIBUTE_phys_state,
                   fill = ATTRIBUTE_phys_state),
               geom = "polygon", alpha = 0.2,
               level = 0.95) +
  guides(shape = guide_legend(override.aes = list(size = 5)))


# Permanova


# Variance stabilize the sample centric metabolites relative adundance data

POS_metab_c_4_permanova_ft <- as.data.frame(scale(asin(sqrt(fqt_class_metadata_RA_pos_PCOA_5[1:45,6:7350])), center = FALSE, scale = TRUE))
  

# PERMANOVA of differences in metabolite composition by physiological state


POS_metab_phys_state_adonis_ft <- adonis2(POS_metab_c_4_permanova_ft~ATTRIBUTE_phys_state, data = fqt_class_metadata_RA_pos_PCOA_5[1:45,], method = "bray")

POS_metab_phys_state_adonis_ft # R2 = 0.13 p = 0.001 F = 6.24


# PERMANOVA of differences in metabolite composition by season


POS_metab_season_adonis_ft <- adonis2(POS_metab_c_4_permanova_ft~ATTRIBUTE_season, data = fqt_class_metadata_RA_pos_PCOA_5[1:45,], method = "bray")

POS_metab_season_adonis_ft # R2 = 0.11 p = 0.001 F = 5.5


# Run betadisper to measure if variance between physiolgical stage is sig different

bd_phys_state_pos <- betadisper(bray_dist_matrix_ft_pos, fqt_class_metadata_RA_pos_PCOA_5$ATTRIBUTE_phys_state)

bd_phys_state_pos

permutest(bd_phys_state_pos) # P = 0.03 significantly different variance between season


# Run betadisper to measure if variance between season is sig different

bd_season_pos <- betadisper(bray_dist_matrix_ft_pos, fqt_class_metadata_RA_pos_PCOA_5$ATTRIBUTE_season)

bd_season_pos

permutest(bd_season_pos) # P = 0.054, not significantly different variance between season




```


# Combine high-score SIRIUS forumlas with dataset


```{r}

SIRIUS_formulas_POS <- SIRIUS_formula_highscore_POS %>% 
  mutate('row ID' = mappingFeatureId) %>% 
  select(`row ID`, molecularFormula, SiriusScoreNormalized)


fqt_class_metadata_formula_POS <- merge(SIRIUS_formulas_POS, fqt_class_metadata_long_pos, by = 'row ID')

fqt_class_metadata_formula_POS <- fqt_class_metadata_formula_POS %>% 
  select(-molecularFormula.y) %>% 
  mutate(molecularFormula = molecularFormula.x) %>% 
  select(-molecularFormula.x)

```

## Seperate out molecular fomrula into elements and ratios 


```{r}

library(CHNOSZ)

formulas_vector_POS <- unique(fqt_class_metadata_formula_POS$molecularFormula)


formulas_POS <- makeup(formulas_vector_POS, count.zero = TRUE)

df_POS <- data.frame(matrix(unlist(formulas_POS), nrow=length(formulas_POS), byrow=TRUE), stringsAsFactors=FALSE)

element_column_names <- c("As","B","Br","C","Cl","F","H","I","N","O","P","S","Se","Si")

colnames(df_POS) <- element_column_names

df_stoichiometry_molecular_formulas_POS <- df_POS %>% 
  mutate(molecularFormula = formulas_vector_POS) %>% 
  distinct()


```

## Merge new Formula dataframs with parsed elements and stoichiometry with metadata 

```{r}

fqt_class_metadata_formula_stoichiometry_POS <- merge(fqt_class_metadata_formula_POS, df_stoichiometry_molecular_formulas_POS, by = "molecularFormula")

fqt_class_metadata_formula_stoichiometry_unique_POS <- fqt_class_metadata_formula_stoichiometry_POS %>%
  distinct() %>% 
  filter(ATTRIBUTE_sample_date != "9/1/24")


write_csv(fqt_class_metadata_formula_stoichiometry_unique_POS, "/Users/chanceenglish/Desktop/Lab Shiz/ARPA-e/Giant_Kelp_DOC/Data/metabolites/POS/fqt_class_metadata_formula_stoichiometry_unique_POS.csv")

fqt_class_metadata_formula_stoichiometry_unique_POS <- read_csv(here("Data", "metabolites", "POS","fqt_class_metadata_formula_stoichiometry_unique_POS.csv"))


```

## Calculate weighted C:N stoichiometries

```{r}

molecular_stoichiometryCN_POS <- fqt_class_metadata_formula_stoichiometry_unique_POS %>% 
  group_by(ATTRIBUTE_season, ATTRIBUTE_blade, ATTRIBUTE_age_d) %>% 
  mutate(weighted_CN = (sum(C*peak_area))/(sum(N*peak_area))) %>% 
  select(filename, ATTRIBUTE_season, ATTRIBUTE_tissue_CN, ATTRIBUTE_age_d, ATTRIBUTE_blade, ATTRIBUTE_phys_state, weighted_CN) %>% 
  unique()

molecular_stoichiometryCN_POS$mode <- "Positive"

write_csv(molecular_stoichiometryCN_POS, "/Users/chanceenglish/Desktop/Lab Shiz/ARPA-e/Giant_Kelp_DOC/Data/metabolites/POS/metabolite_weighted_CN_POS.csv")

molecular_stoichiometryCN_POS <- read_csv(here("Data", "metabolites", "POS","metabolite_weighted_CN_POS.csv"))

```

## Plot weighted stoichiometries over time between seasons 

```{r}

exo_CN_tissue_CN_pos_p <- molecular_stoichiometryCN_POS %>% 
  ggplot(aes(x = ATTRIBUTE_tissue_CN, y = weighted_CN, shape = ATTRIBUTE_season, color = ATTRIBUTE_age_d)) +
  geom_point(size = 4) +
  geom_smooth(method = "lm",se = F, color = "black", size = 1) +
  labs(x = "Tissue Stoichiometry (C:N)",
       y = "Exometabolite Stoichiometry (C:N)",
      color = "Age (d)",
      shape = NULL) +
  scico::scale_color_scico(palette = "vik", breaks = c(0,25,50,75,100)) +
  coord_cartesian(expand = c(0,0)) +
 scale_y_continuous(breaks = c(0,5,10,15,20,25,30), limits = c(0,30)) +
  scale_x_continuous(breaks = c(0,5,10,15,20,25,30,35,40,45), limits = c(0,45)) +
  theme(panel.background = element_rect(fill = "white", color = "black", size = 1.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = margin(1,1,1,1, "cm"),
        strip.background = element_rect(fill = "white", color = "white"),
        legend.key = element_rect(fill = "white", color = NA),
        legend.text = element_text(size = 15),
        legend.key.height = unit(0.4, "inch"),
        legend.key.width = unit(0.2, "inch"),
        legend.title = element_text(size = 20),
        axis.text = element_text(size = 15, color = "black"),
        axis.title = element_text(size = 15),
        text = element_text(family = "Times")) +
  guides(shape = guide_legend(override.aes = list(size = 5)))


mature_CN_p_pos <- molecular_stoichiometryCN_POS %>% 
  filter(ATTRIBUTE_phys_state == "Mature") %>% 
  ggplot(aes(x = ATTRIBUTE_season, y = weighted_CN)) +
  geom_boxplot(aes(x = ATTRIBUTE_season, y = weighted_CN)) +
  geom_point(aes(x = ATTRIBUTE_season, y = weighted_CN), 
             position = position_jitterdodge(0.3)) +
  scale_y_continuous(breaks = c(5,10,15,20,25,30), limits = c(5,20)) +
 labs(x = "",
       y = "Exometabolite C:N") +
        theme(panel.background = element_rect(fill = "white", color = "black", size = 1.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = margin(1,1,1,1, "cm"),
        strip.background = element_rect(fill = "white", color = "white"),
        legend.key = element_blank(),
        legend.text = element_text(size = 15),
        legend.key.height = unit(0.5, "inch"),
        legend.key.width = unit(0.4, "inch"),
        legend.title = element_blank(),
        axis.text.y = element_text(size = 20, color = "black"),
        axis.text.x = element_text(size = 24, color = "black"),
        axis.title = element_text(size = 24),
        text = element_text(family = "Times")) 



# T-test Mature kelp Exudate CN

molecular_stoichiometryCN_mature_pos <- molecular_stoichiometryCN_POS %>% 
  filter(ATTRIBUTE_phys_state == "Mature")

## Test for Normality


with(molecular_stoichiometryCN_mature_pos, shapiro.test(weighted_CN[ATTRIBUTE_season == "Spring"])) # p = 0.09 normal

with(molecular_stoichiometryCN_mature_pos, shapiro.test(weighted_CN[ATTRIBUTE_season == "Summer"])) # p = 0.02 normal

# Test for equal variances 

ftest.molecular_stoichiometryCN_mature_pos <- var.test(weighted_CN ~ ATTRIBUTE_season, data = molecular_stoichiometryCN_mature_pos)

# F = 0.26845, num df = 8, denom df = 17, p-value = 0.02 variances arent equal equal

## Use Wilcox t.test (unpaired so basically Mann Whitnet U) 

matureCN.wilcox.test_pos <- wilcox.test(molecular_stoichiometryCN_mature_pos$weighted_CN ~ molecular_stoichiometryCN_mature_pos$ATTRIBUTE_season, alternative = "less")

# W = 84 p = 0.57, CN of mature exudates is not signif lowere in the spring than summer

matureCN.wilcox.test_pos


# Run model II linear regressions between C:N of exudates and C:N of tissue 

molecular_stoichiometryCN_POS_spring <- molecular_stoichiometryCN_POS %>% 
  filter(ATTRIBUTE_season == "Spring")

spring_pos_CNexo_CN_tissue_lm2 <- lmodel2(data = molecular_stoichiometryCN_POS_spring,
                                          weighted_CN~ATTRIBUTE_tissue_CN)

spring_pos_CNexo_CN_tissue_lm2 #R2 = 0.87, p < 0.001, spring ESI+

molecular_stoichiometryCN_POS_summer <- molecular_stoichiometryCN_POS %>% 
  filter(ATTRIBUTE_season == "Summer")

summer_pos_CNexo_CN_tissue_lm2 <- lmodel2(data = molecular_stoichiometryCN_POS_summer,
                                          weighted_CN~ATTRIBUTE_tissue_CN)

summer_pos_CNexo_CN_tissue_lm2 #R2 = 0.34, p < 0.001, summer ESI+


```

## Calculate NOSC 

```{r}

molecular_stoichiometry_NOSC_POS <- fqt_class_metadata_formula_stoichiometry_unique_POS %>% 
  mutate(NOSC = (-((4*C + H - 3*N - 2*O + 5*P - 2*S)/C)+4)) %>% 
  group_by(ATTRIBUTE_season, ATTRIBUTE_blade, ATTRIBUTE_age_d) %>% 
  mutate(weighted_NOSC = (sum(NOSC*peak_area))/(sum(peak_area))) %>% 
  select(filename, ATTRIBUTE_season, ATTRIBUTE_tissue_CN, ATTRIBUTE_age_d, ATTRIBUTE_blade, ATTRIBUTE_phys_state, weighted_NOSC) %>% 
  unique()

molecular_stoichiometry_NOSC_POS %>% 
  ggplot(aes(x = ATTRIBUTE_age_d, y = weighted_NOSC, colour = ATTRIBUTE_season)) +
  geom_point(size = 4) +
  labs(x = "Age_d",
       y = "Exudate NOSC") +
  theme(panel.background = element_rect(fill = "white", color = "black", size = 1.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = margin(1,1,1,1, "cm"),
        strip.background = element_rect(fill = "white", color = "black"),
        legend.key = element_rect(fill = "white"),
        legend.text = element_text(size = 15),
        legend.key.height = unit(0.5, "inch"),
        legend.key.width = unit(0.4, "inch"),
        legend.title = element_text(size = 15),
        axis.text = element_text(size = 15, color = "black"),
        axis.title = element_text(size = 15),
        text = element_text(family = "Times")) 



```

## Carbon to Halogen Ratios 

```{r}

molecular_stoichiometryCBr_POS <- fqt_class_metadata_formula_stoichiometry_unique_POS %>% 
  group_by(ATTRIBUTE_season, ATTRIBUTE_blade, ATTRIBUTE_age_d) %>% 
  mutate(weighted_BrC = (sum(Br*peak_area))/((sum(C*peak_area)))) %>% 
  select(filename, ATTRIBUTE_season, ATTRIBUTE_tissue_CN, ATTRIBUTE_age_d, ATTRIBUTE_blade, ATTRIBUTE_phys_state, weighted_BrC) %>% 
  unique()

molecular_stoichiometryCBr_POS %>% 
  ggplot(aes(x = ATTRIBUTE_age_d, y = weighted_BrC, colour = ATTRIBUTE_season)) +
  geom_point(size = 4) +
  labs(x = "Age_d",
       y = "Exudate Br:C") +
  theme(panel.background = element_rect(fill = "white", color = "black", size = 1.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = margin(1,1,1,1, "cm"),
        strip.background = element_rect(fill = "white", color = "black"),
        legend.key = element_rect(fill = "white"),
        legend.text = element_text(size = 15),
        legend.key.height = unit(0.5, "inch"),
        legend.key.width = unit(0.4, "inch"),
        legend.title = element_text(size = 15),
        axis.text = element_text(size = 15, color = "black"),
        axis.title = element_text(size = 15),
        text = element_text(family = "Times")) 



```

## Peak Areas 

```{r}

blank_features <- fqt_long_metadata %>% 
  filter(ATTRIBUTE_source == "Blank")

blank_features_v <- blank_features$`row ID`[blank_features$peak_area > 0]

fqt_long_metadata_summarize_pos <- fqt_long_metadata %>% 
  filter(! `row ID` %in% blank_features_v) %>% 
  group_by(ATTRIBUTE_source, ATTRIBUTE_season, ATTRIBUTE_blade, ATTRIBUTE_age_d, ATTRIBUTE_DOC_prePPL_uMC) %>% 
  summarise(total_peak_area = sum(peak_area)) %>% 
  filter(ATTRIBUTE_season != "September") %>% 
  filter(ATTRIBUTE_source %in% c("Ambient", "Kelp"))

fqt_long_metadata_summarize_pos %>% 
  ggplot(aes(x = ATTRIBUTE_blade, y = total_peak_area)) +
  geom_col() +
  facet_grid(ATTRIBUTE_season~ATTRIBUTE_age_d)

fqt_long_metadata_summarize_pos %>% 
  ggplot(aes(x = ATTRIBUTE_DOC_prePPL_uMC, y = total_peak_area)) +
  geom_point(aes(color = ATTRIBUTE_age_d))


```

# Enriched Kelp Exudate Feature Ids for cytoscape

```{r}

pos_fqt_class_metadata_RA_PCOA_feature_list <- fqt_class_metadata_RA_pos_PCOA_4 %>% 
  select(`row ID`, ATTRIBUTE_phys_state) %>% 
  unique() %>% 
  mutate(featureID = `row ID`) 

write_csv(pos_fqt_class_metadata_RA_PCOA_feature_list, "/Users/chanceenglish/Desktop/Lab Shiz/ARPA-e/Giant_Kelp_DOC/Data/metabolites/POS/pos_fqt_class_metadata_RA_PCOA_feature_list.csv")

```

# FBMN Results for exudate features w/ subnetwork IDs, merge with Relative peak areas and metadata

```{r}

FBMN_results_pos <- read_csv(here("Data", "metabolites", "POS","FBMN_wNIST_cytoscape_results_POS.csv"))

FBMN_results_simple_pos <- FBMN_results_pos %>% 
  select(featureID, component, IsSingleNode) %>% 
  mutate(`row ID` = featureID) %>% 
  select(-featureID)


fqt_class_metadata_RA_long_pos <- fqt_class_metadata_RA_pos %>% 
  pivot_longer(cols = c(`240417_B2.mzML`:`240616_B5.mzML`),
               names_to = "filename",
               values_to = "rpa") 

fqt_class_metadata_RA_long_pos <- fqt_class_metadata_RA_long_pos %>% 
  unique() %>% 
  filter(ATTRIBUTE_season %in% c("Spring", "Summer"))


fqt_class_metadata_RA_subnetwork_sum_pos <- merge(fqt_class_metadata_RA_long_pos, FBMN_results_simple_pos, by = "row ID") %>% 
  unique()


#fqt_class_metadata_RA_subnetwork_sum_pos <- fqt_class_metadata_RA_subnetwork_sum_pos %>% 
  filter(!ATTRIBUTE_LC_vial_name %in% c("230823 B1","230823 B2","230823 B3"))

  

fqt_class_metadata_RA_subnetwork_sum2_pos <- fqt_class_metadata_RA_subnetwork_sum_pos %>% 
  group_by(component, ATTRIBUTE_season, ATTRIBUTE_phys_state, ATTRIBUTE_blade, ATTRIBUTE_age_d) %>% 
  summarize(subnetwork_rpa = sum(rpa)) %>% 
  ungroup() %>% 
  unique()

  
# Wilcox paired test, test if sub networks are significantly higher or lower between developmental stages


subnetwork_RA_phys_state_wilcox_test_pos <- fqt_class_metadata_RA_subnetwork_sum2_pos %>% 
  filter(ATTRIBUTE_season != "September") %>% 
  select(component, ATTRIBUTE_phys_state, subnetwork_rpa) %>% 
  nest(data = c(ATTRIBUTE_phys_state, subnetwork_rpa)) %>% 
  mutate(model = map(data, ~wilcox.test(subnetwork_rpa ~ ATTRIBUTE_phys_state, .)), 
         tidy = map(model, broom::tidy)) %>% 
  select(component, tidy) %>% 
  unnest(tidy) %>% 
  filter(p.value != "NA") %>% 
  mutate(adjusted_p.value = p.adjust(p.value, method = "BH")) %>% 
  filter(adjusted_p.value != "NaN")


# How many sub networks are significant 

length(subnetwork_RA_phys_state_wilcox_test_pos$component[subnetwork_RA_phys_state_wilcox_test_pos$adjusted_p.value < 0.05]) # 174 significant

# How many subnetworks in total 

length(subnetwork_RA_phys_state_wilcox_test_pos$component) # 977 total


subnetwork_RA_phys_state_wilcox_sig_pos <- subnetwork_RA_phys_state_wilcox_test_pos %>% 
  filter(adjusted_p.value < 0.05)


subnetwork_RA_phys_state_wilcox_sig_compounds_pos <- merge(subnetwork_RA_phys_state_wilcox_sig_pos, fqt_class_metadata_RA_subnetwork_sum_consensus_class, by = "component")



# Wilcox, test if sub networks are significantly higher or lower between seasons


subnetwork_RA_season_wilcox_test_pos <- fqt_class_metadata_RA_subnetwork_sum2_pos %>% 
  filter(ATTRIBUTE_season != "September") %>% 
  select(component, ATTRIBUTE_season, subnetwork_rpa) %>% 
  nest(data = c(ATTRIBUTE_season, subnetwork_rpa)) %>% 
  mutate(model = map(data, ~wilcox.test(subnetwork_rpa ~ ATTRIBUTE_season, .)), 
         tidy = map(model, broom::tidy)) %>% 
  select(component, tidy) %>% 
  unnest(tidy) %>% 
  filter(p.value != "NA") %>% 
  mutate(adjusted_p.value = p.adjust(p.value, method = "BH")) %>% 
  filter(adjusted_p.value != "NaN")


# How many sub networks are significant 

length(subnetwork_RA_season_wilcox_test_pos$component[subnetwork_RA_season_wilcox_test_pos$adjusted_p.value < 0.05]) # 195 significant

# How many subnetworks in total 

length(subnetwork_RA_season_wilcox_test_pos$component) # 635 total



```


# Plot amino acids, peptides, analogues and halogenated aromatics, phenols, aryls, benzenoids


```{r}

AAPA_p_pos <- fqt_class_metadata_RA_subnetwork_sum_pos %>% 
  filter(`ClassyFire#subclass` == "Amino acids, peptides, and analogues", 
         ATTRIBUTE_season != "September") %>% 
  group_by(ATTRIBUTE_age_d, ATTRIBUTE_season, ATTRIBUTE_blade) %>% 
  summarize(sum_rpa = sum(rpa)) %>% 
  ungroup() %>% 
  group_by(ATTRIBUTE_age_d, ATTRIBUTE_season) %>% 
  mutate(mean_rpa = mean(sum_rpa),
         sd_rpa = sd(sum_rpa)) %>% 
  distinct() %>% 
  ggplot() +
  geom_point(aes(x = ATTRIBUTE_age_d, y = sum_rpa*100, shape = ATTRIBUTE_season)) +
  geom_point(aes(x = ATTRIBUTE_age_d, y = mean_rpa*100, shape = ATTRIBUTE_season), size = 4) +
  geom_line(aes(x = ATTRIBUTE_age_d, y = mean_rpa*100, shape = ATTRIBUTE_season ), size = 0.5) +
  labs(x = "Age (d)",
       y = "Amino Acids, Peptides, analogues \n (% RPA)",
       shape = NULL) +
  scale_shape_manual(values = c(1,2)) +
  scale_x_continuous(breaks = c(10,20,30,40,50,60,70,80,90), limits = c(10,90)) +
  coord_cartesian(expand = c(0,0)) +
   theme(panel.background = element_rect(fill = "white", color = "black", size = 1.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = margin(1,1,1,1, "cm"),
        strip.background = element_rect(fill = "white", color = "black"),
        legend.key = element_rect(fill = "white",color = NA),
        legend.text = element_text(size = 15),
        legend.key.height = unit(0.5, "inch"),
        legend.key.width = unit(0.4, "inch"),
        legend.title = element_blank(),
        legend.position = "right",
        axis.text = element_text(size = 15, color = "black"),
        axis.title = element_text(size = 20),
        text = element_text(family = "Helvetica")) +
   annotate("rect", xmin = 10, xmax = 50, ymin = 0, ymax = Inf,
           alpha = .25,fill = "#06558B")  +
  annotate("rect", xmin = 50.1, xmax = 90, ymin = 0, ymax = Inf,
           alpha = .25,fill = "#AA4613") 



carbohydrates_plot_pos_p <- fqt_class_metadata_RA_subnetwork_sum_pos %>% 
  filter(`ClassyFire#subclass` == "Aminoxides", 
         ATTRIBUTE_season != "September") %>% 
  group_by(ATTRIBUTE_age_d, ATTRIBUTE_season, ATTRIBUTE_blade) %>% 
  summarize(sum_rpa = sum(rpa)) %>% 
  ungroup() %>% 
  group_by(ATTRIBUTE_age_d, ATTRIBUTE_season) %>% 
  mutate(mean_rpa = mean(sum_rpa),
         sd_rpa = sd(sum_rpa)) %>% 
  distinct() %>% 
  ggplot() +
  geom_point(aes(x = ATTRIBUTE_age_d, y = sum_rpa*100, shape = ATTRIBUTE_season)) +
  geom_point(aes(x = ATTRIBUTE_age_d, y = mean_rpa*100, shape = ATTRIBUTE_season), size = 4) +
  geom_line(aes(x = ATTRIBUTE_age_d, y = mean_rpa*100, shape = ATTRIBUTE_season ), size = 0.5) +
  scale_x_continuous(breaks = c(10,20,30,40,50,60,70,80,90), limits = c(10,90)) +
  scale_y_continuous(breaks = c(0,10,20,30,40), limits = c(0,40)) +
  labs(x = "Age (d)",
       y = "Diterpenoids (% RPA)",
       shape = NULL) +
  coord_cartesian(expand = c(0,0)) +
  scale_shape_manual(values = c(1,2)) +
   theme(panel.background = element_rect(fill = "white", color = "black", size = 1.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = margin(1,1,1,1, "cm"),
        strip.background = element_rect(fill = "white", color = "black"),
        legend.key = element_rect(fill = "white",color = NA),
        legend.text = element_text(size = 15),
        legend.key.height = unit(0.5, "inch"),
        legend.key.width = unit(0.4, "inch"),
        legend.title = element_blank(),
        legend.position = "right",
        axis.text = element_text(size = 15, color = "black"),
        axis.title = element_text(size = 20),
        text = element_text(family = "Helvetica")) +
   annotate("rect", xmin = 10, xmax = 50, ymin = 0, ymax = 40,
           alpha = .25,fill = "#06558B")  +
  annotate("rect", xmin = 50.1, xmax = 90, ymin = 0, ymax = 40,
           alpha = .25,fill = "#AA4613") 



my_colors <- scico(7, palette = "vik")
scales::show_col(my_colors)


```

# Select subnetworks that are signifcantly different between developmental stage  

```{r}


Subnetwork_1773_rpa_pos_p <- fqt_class_metadata_RA_subnetwork_sum_pos %>% 
  filter(component == 1773) %>% 
  group_by(ATTRIBUTE_phys_state, ATTRIBUTE_season, ATTRIBUTE_age_d, ATTRIBUTE_blade) %>% 
  summarize(sum_component = sum(rpa)) %>% 
  ungroup() %>% 
  ggplot() + 
  geom_boxplot(aes(x = ATTRIBUTE_phys_state, y = sum_component*100),
               outlier.shape = NA) +
  geom_point(aes(x = ATTRIBUTE_phys_state, y = sum_component*100), 
             position = position_jitterdodge(0.3)) +
  scale_y_continuous() +
  labs(x = "",
       y = "Subnetwork 1773 (% Peak Area)") +
        theme(panel.background = element_rect(fill = "white", color = "black", size = 1.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = margin(1,1,1,1, "cm"),
        strip.background = element_rect(fill = "white", color = "white"),
        legend.key = element_blank(),
        legend.text = element_text(size = 8),
        legend.key.height = unit(0.5, "inch"),
        legend.key.width = unit(0.4, "inch"),
        legend.title = element_blank(),
        axis.text.y = element_text(size = 8, color = "black"),
        axis.text.x = element_text(size = 15, color = "black"),
        axis.title = element_text(size = 15),
        text = element_text(family = "Times")) 


Subnetwork_691_rpa_pos_p <- fqt_class_metadata_RA_subnetwork_sum_pos %>% 
  filter(component == 691) %>% 
  group_by(ATTRIBUTE_phys_state, ATTRIBUTE_season, ATTRIBUTE_age_d, ATTRIBUTE_blade) %>% 
  summarize(sum_component = sum(rpa)) %>% 
  ungroup() %>% 
  ggplot() + 
  geom_boxplot(aes(x = ATTRIBUTE_phys_state, y = sum_component*100),
               outlier.shape = NA) +
  geom_point(aes(x = ATTRIBUTE_phys_state, y = sum_component*100), 
             position = position_jitterdodge(0.3)) +
  scale_y_continuous() +
  scale_fill_manual(values=c("dodgerblue1", "red4")) +
  labs(x = "",
       y = "Subnetwork 543 (% Peak Area)") +
        theme(panel.background = element_rect(fill = "white", color = "black", size = 1.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = margin(1,1,1,1, "cm"),
        strip.background = element_rect(fill = "white", color = "white"),
        legend.key = element_blank(),
        legend.text = element_text(size = 8),
        legend.key.height = unit(0.5, "inch"),
        legend.key.width = unit(0.4, "inch"),
        legend.title = element_blank(),
        axis.text.y = element_text(size = 8, color = "black"),
        axis.text.x = element_text(size = 15, color = "black"),
        axis.title = element_text(size = 15),
        text = element_text(family = "Times")) 
 
Subnetwork_974_rpa_pos_p <- fqt_class_metadata_RA_subnetwork_sum_pos %>% 
  filter(component == 974) %>% 
  group_by(ATTRIBUTE_phys_state, ATTRIBUTE_season, ATTRIBUTE_age_d, ATTRIBUTE_blade) %>% 
  summarize(sum_component = sum(rpa)) %>% 
  ungroup() %>% 
  ggplot() + 
  geom_boxplot(aes(x = ATTRIBUTE_phys_state, y = sum_component*100),
               outlier.shape = NA) +
  geom_point(aes(x = ATTRIBUTE_phys_state, y = sum_component*100), 
             position = position_jitterdodge(0.3)) +
  scale_y_continuous() +
  scale_fill_manual(values=c("dodgerblue1", "red4")) +
  labs(x = "",
       y = "Subnetwork 974 (% Peak Area)") +
        theme(panel.background = element_rect(fill = "white", color = "black", size = 1.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = margin(1,1,1,1, "cm"),
        strip.background = element_rect(fill = "white", color = "white"),
        legend.key = element_blank(),
        legend.text = element_text(size = 8),
        legend.key.height = unit(0.5, "inch"),
        legend.key.width = unit(0.4, "inch"),
        legend.title = element_blank(),
        axis.text.y = element_text(size = 8, color = "black"),
        axis.text.x = element_text(size = 15, color = "black"),
        axis.title = element_text(size = 15),
        text = element_text(family = "Times")) 


fqt_class_metadata_RA_subnetwork_sum_pos %>% 
  filter(component == 472) %>% 
  group_by(ATTRIBUTE_phys_state, ATTRIBUTE_season, ATTRIBUTE_age_d, ATTRIBUTE_blade) %>% 
  summarize(sum_component = sum(rpa)) %>% 
  ungroup() %>% 
  ggplot() + 
  geom_boxplot(aes(x = ATTRIBUTE_phys_state, y = sum_component*100),
               outlier.shape = NA) +
  geom_point(aes(x = ATTRIBUTE_phys_state, y = sum_component*100), 
             position = position_jitterdodge(0.3)) +
  scale_y_continuous() +
  labs(x = "",
       y = "Subnetwork 472 (% Peak Area)") +
        theme(panel.background = element_rect(fill = "white", color = "black", size = 1.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = margin(1,1,1,1, "cm"),
        strip.background = element_rect(fill = "white", color = "white"),
        legend.key = element_blank(),
        legend.text = element_text(size = 8),
        legend.key.height = unit(0.5, "inch"),
        legend.key.width = unit(0.4, "inch"),
        legend.title = element_blank(),
        axis.text.y = element_text(size = 8, color = "black"),
        axis.text.x = element_text(size = 15, color = "black"),
        axis.title = element_text(size = 15),
        text = element_text(family = "Times")) 

```




# Subnetwork relative bundance across age stacked bar plot 

```{r}

library(reshape2)

# Identify subnetworks with an average of 1% in at least one age group 

sig_subnetworks_one_percent_pos <- fqt_class_metadata_RA_subnetwork_sum2_pos %>% 
  group_by(ATTRIBUTE_age_d, component) %>% 
  summarise(avg_rpa = mean(subnetwork_rpa), .groups = "drop") %>% 
  ungroup() %>% 
  group_by(ATTRIBUTE_age_d, component) %>% 
  filter(any(avg_rpa > 0.01)) %>% 
  mutate(component = as.factor(component)) %>% 
  ungroup() %>% 
  group_by(component) %>% 
  filter(ATTRIBUTE_age_d != is.na(ATTRIBUTE_age_d))

sig_subnetworks_one_percent_pos_component <- sig_subnetworks_one_percent_pos$component

# Select subnetworks with more than 1% mean peak area per age 


fqt_class_metadata_RA_subnetwork_sum3_pos <- fqt_class_metadata_RA_subnetwork_sum2_pos %>% 
 filter(component %in% sig_subnetworks_one_percent_pos_component)


# Filter subnetworks into a consensus class for the stacked barplot 


fqt_class_metadata_RA_subnetwork_sum_consensus_class_pos <- fqt_class_metadata_RA_subnetwork_sum_pos %>% 
  group_by(component, `ClassyFire#subclass`, `ClassyFire#class`) %>% 
  summarise(Totalsum = sum(rpa), .groups = 'drop') %>%
  ungroup() %>% 
  group_by(component) %>% 
  slice_max(Totalsum, n = 1, with_ties = FALSE)
  

fqt_class_metadata_RA_subnetwork_sum3_compounds_classes_pos <- merge(fqt_class_metadata_RA_subnetwork_sum_consensus_class_pos, fqt_class_metadata_RA_subnetwork_sum3_pos, by = "component")

# Merge significance results with the peak area data and subnetwork 

fqt_class_metadata_RA_subnetwork_sum3_compounds_classes_pos <- fqt_class_metadata_RA_subnetwork_sum3_compounds_classes_pos %>% 
  mutate(significantly_enriched = ifelse(
    component %in% subnetwork_RA_phys_state_wilcox_sig_pos$component,
    "bold",
    "plain"
  ))

# Create unique identifier with subnetwork ID and consensus class
  
fqt_class_metadata_RA_subnetwork_sum3_compounds_classes_pos$com_cla_subcla <- do.call(paste, c(fqt_class_metadata_RA_subnetwork_sum3_compounds_classes_pos[c("component","ClassyFire#class", "ClassyFire#subclass")], sep=";")) 
  
fqt_class_metadata_RA_subnetwork_sum3_compounds_classes_pos <- fqt_class_metadata_RA_subnetwork_sum3_compounds_classes_pos %>% 
  group_by(component) %>% 
  mutate(prop_16 = sum(subnetwork_rpa[ATTRIBUTE_age_d %in% c(16,30,37, 43)], na.rm= T)/sum(subnetwork_rpa, na.rm=T),
         ATTRIBUTE_age_d = as.factor(ATTRIBUTE_age_d))


# Factor age for stacked bar plot

fqt_class_metadata_RA_subnetwork_sum3_compounds_classes_pos$ATTRIBUTE_age_d <- factor(fqt_class_metadata_RA_subnetwork_sum3_compounds_classes_pos$ATTRIBUTE_age_d, levels = c("16","30","37","43","64","77","78"))



# Make noramlized stacked barplot showing relative contribution of subnetworks at specific ages


norm_bar_plot_component_pos_p <- fqt_class_metadata_RA_subnetwork_sum3_compounds_classes_pos %>%
    filter(significantly_enriched == "bold") %>% 
  ggplot(aes(y = reorder(com_cla_subcla, prop_16, decreasing=T),
                             x = subnetwork_rpa, 
                             fill = ATTRIBUTE_age_d)) +
  geom_bar(position = "fill", stat = "identity") +
  labs(x = "Peak Area Normalized",
       y = "Subnetwork",
       fill = "Age (d)") +
  coord_cartesian(expand = c(0,0)) +
  scale_fill_manual(values = c("#001260", "#06558B", "#71A7C4", "#EBE5E0","#AA4613","#590007","#590007")) +
  scale_x_continuous() + 
   theme(panel.background = element_rect(fill = "white", color = "black", size = 1.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = margin(1,1,1,1, "cm"),
        strip.background = element_rect(fill = "white", color = "black"),
        legend.key = element_rect(fill = "white", color = NA),
        legend.text = element_text(size = 15),
        legend.position = "none",
        legend.key.height = unit(1, "inch"),
        legend.key.width = unit(0.4, "inch"),
        legend.title = element_text(size = 15),
        axis.text.y = element_text(size = 12, color = "black"),
        axis.text.x = element_text(size = 15, color = "black"),
        axis.title = element_text(size = 20),
        text = element_text(family = "Helvetica")) 


ggsave("norm_bar_plot_component_pos_p.pdf", plot = norm_bar_plot_component_pos_p, path = "/Users/chanceenglish/Desktop/Lab Shiz/ARPA-e/Giant_Kelp_DOC/Figures/HQ Figs Metabolites/", width = 10, height = 15, device='pdf', dpi=250, units = "in")
  

# Complimentary dotplot showing range of relative peak areas

norm_bar_plot_component_rpa_pos_p <- fqt_class_metadata_RA_subnetwork_sum3_compounds_classes_pos %>% 
      filter(significantly_enriched == "bold") %>% 
  ggplot(aes(y = reorder(com_cla_subcla, prop_16, decreasing=T),
                             x = subnetwork_rpa*100)) +
  geom_point(aes(fill = ATTRIBUTE_age_d,
                 shape = ATTRIBUTE_season), 
             size = 4,
             alpha = 0.8) +
  geom_line(color ="black", size = 0.2) +
  labs(x = "Peak Area (%)",
       y = "Subnetwork",
       color = NULL) +
   scale_shape_manual(values = c(21,24)) +
    scale_fill_manual(values = c("#001260", "#06558B", "#71A7C4", "#EBE5E0","#AA4613","#590007","#590007")) +
   scale_x_log10(breaks = c(0,0.001,0.01,0.1,1,10,100),
                    expand = expansion(mult = c(0, 0.05)),
                 labels = label_number())+
   theme(panel.background = element_rect(fill = "white", color = "black", size = 1.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = margin(1,1,1,1, "cm"),
        strip.background = element_rect(fill = "white", color = "black"),
        legend.key = element_rect(fill = "white", color = NA),
        legend.text = element_text(size = 24),
        legend.position = c(0.8,0.15),
        legend.title = element_text(size = 15),
        axis.text.x = element_text(size = 15, color = "black"),
        axis.text.y = element_blank(),
        axis.title.y = element_blank(),
        axis.title = element_text(size = 20),
        text = element_text(family = "Helvetica")) +
   scale_size(guide = 'none') +
  guides(shape=guide_legend(override.aes=list(size=4), title = ""),
         fill = "none")

ggsave("norm_bar_plot_component_rpa_pos_p.pdf", plot = norm_bar_plot_component_rpa_pos_p, path = "/Users/chanceenglish/Desktop/Lab Shiz/ARPA-e/Giant_Kelp_DOC/Figures/HQ Figs Metabolites/", width = 10, height = 15, device='pdf', dpi=250, units = "in")







```



# Van Krevelen Plots

```{r}

molecular_stoichiometry_VanK_pos <- fqt_class_metadata_formula_stoichiometry_unique_POS %>% 
  mutate(HC = (H*peak_area)/(C*peak_area),
         OC = (O*peak_area)/(C*peak_area)) %>% 
  filter(HC != "NaN",
         OC != "NaN")
 

VanKrev_pos_p <- molecular_stoichiometry_VanK_pos %>% 
  ggplot(aes(x = OC, HC, colour = ATTRIBUTE_phys_state)) +
  geom_point(aes(size = peak_area, shape = ATTRIBUTE_season)) +
  labs(x = "O:C",
       y = "H:C",
       color = "") +
  scale_color_manual(values = c("grey","orangered")) +
  scale_size_continuous(range  = c(0.1, 15), 
                        limits = c(5e4, 5e7), 
                        breaks = c(5e4,5e5,5e6,5e7)) +
  scale_x_continuous(limits = c(0,1), breaks = c(0,0.2,0.4,0.6,0.8,1.0)) +
  scale_y_continuous(limits = c(0,2.5), breaks = c(0,0.5,1.0,1.5,2.0,2.5)) +
  theme(panel.background = element_rect(fill = "white", color = "black", size = 1.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = margin(1,1,1,1, "cm"),
        strip.background = element_rect(fill = "white", color = "black"),
        legend.key = element_rect(fill = "white", color = NA),
        legend.text = element_text(size = 15),
        legend.key.height = unit(0.5, "inch"),
        legend.key.width = unit(0.4, "inch"),
        legend.title = element_text(size = 15),
        axis.text = element_text(size = 15, color = "black"),
        axis.title = element_text(size = 15),
        text = element_text(family = "Helvetica")) +
  scale_size(guide = 'none') +
  guides(color=guide_legend(override.aes=list(size=4), title = "Developmental Stage"), shape=guide_legend(override.aes=list(size=4), title = "Season"))





```

# Proportion of formulas

```{r}


formulas_simple_POS <- fqt_class_metadata_formula_stoichiometry_unique_POS %>%
   mutate(isCHON = case_when(
      C>0 & H >0 & O >0 & N > 0 & peak_area > 0 ~ TRUE,
      TRUE ~ FALSE
   )) %>% 
  mutate(isCHOBr = case_when(
    C > 0 & H >0 & O > 0 & Br > 0 & peak_area > 0 ~ TRUE,
    TRUE ~ FALSE
  )) %>% 
  mutate(isCHO = case_when(
    As < 1 & B < 1 & Br < 1 & C > 0 & Cl < 1 & F < 1 & H > 0 & I < 1 & N < 1 & O > 0 & P < 1 & S < 1 & Se < 1 & Si < 1 & peak_area > 0 ~ TRUE,
    TRUE ~ FALSE
  )) %>% 
  mutate(isCHOS = case_when(
    C > 0 & H >0 & O > 0 & S > 0 & peak_area > 0 ~ TRUE,
    TRUE ~ FALSE)) %>% 
  filter(peak_area > 0) %>% 
  group_by(ATTRIBUTE_season, ATTRIBUTE_phys_state, ATTRIBUTE_blade, ATTRIBUTE_age_d) %>% 
  summarize(CHO = mean(isCHO, na.rm = TRUE),
            CHOBr = mean(isCHOBr, na.rm = TRUE),
            CHON = mean(isCHON, na.rm = TRUE),
            CHOS = mean(isCHOS, na.rm = TRUE)) %>% 
  pivot_longer(
    cols = c(CHO, CHOBr, CHON, CHOS), 
    names_to = "formula_class",     
    values_to = "Proportion"      
  )
     

formula_p_pos_devstage <- ggboxplot(formulas_simple_POS,
                   x = "formula_class",
                  y = "Proportion", 
                  color = "ATTRIBUTE_phys_state",
                  shape = "ATTRIBUTE_season",
                  palette = my_pallet,
                  add = "jitter") +
  stat_compare_means(aes(x = formula_class, 
                   y = Proportion,
                   group = ATTRIBUTE_season),
                   label = "p.signif",
                   label.y = c(0.5, 0.4, 0.9, 0.5),
                   size = 6) +
  labs(x = "",
       y = "Proportion of Formulas (%)",
       fill = "") + 
  facet_wrap( ~ ATTRIBUTE_phys_state) +
  theme(panel.background = element_rect(fill = "white", color = "black", size = 1.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = margin(1,1,1,1, "cm"),
        strip.background = element_rect(fill = "white", color = "black"),
        legend.key = element_rect(fill = "white",color = NA),
        legend.text = element_text(size = 15),
        legend.key.height = unit(0.5, "inch"),
        legend.key.width = unit(0.4, "inch"),
        legend.position = "right",
        legend.title = element_blank(),
        axis.text = element_text(size = 15, color = "black"),
        axis.title = element_text(size = 15),
        text = element_text(family = "Helvetica")) +
  coord_cartesian(expand = c(0,1)) +
  scale_y_continuous(limits = c(0,1), breaks = c(0,0.2,0.4,0.6,0.8,1.0)) +
  guides()


formula_p_season <- ggboxplot(formulas_simple_POS,
                  x = "formula_class",
                  y = "Proportion", 
                  color = "ATTRIBUTE_phys_state",
                  shape = "ATTRIBUTE_season",
                  palette = my_pallet,
                  add = "jitter") +
  stat_compare_means(aes(x = formula_class, 
                   y = Proportion,
                   group = ATTRIBUTE_phys_state),
                   label = "p.signif",
                   label.y = c(0.5, 0.4, 0.9, 0.5),
                   size = 6) +
  labs(x = "",
       y = "Proportion of Formulas (%)",
       fill = "") + 
  facet_wrap( ~ ATTRIBUTE_season) +
  theme(panel.background = element_rect(fill = "white", color = "black", size = 1.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = margin(1,1,1,1, "cm"),
        strip.background = element_rect(fill = "white", color = "black"),
        legend.key = element_rect(fill = "white",color = NA),
        legend.text = element_text(size = 15),
        legend.key.height = unit(0.5, "inch"),
        legend.key.width = unit(0.4, "inch"),
        legend.position = "right",
        legend.title = element_blank(),
        axis.text = element_text(size = 15, color = "black"),
        axis.title = element_text(size = 15),
        text = element_text(family = "Helvetica")) +
  coord_cartesian(expand = c(0,1)) +
  scale_y_continuous(limits = c(0,1), breaks = c(0,0.2,0.4,0.6,0.8,1.0)) +
  guides()



     
formula_p_pos <- ggboxplot(formulas_simple_POS,
                   x = "formula_class",
                  y = "Proportion", 
                  color = "ATTRIBUTE_phys_state",
                  palette = my_pallet,
                  add = "jitter") +
  stat_compare_means(aes(x = formula_class, 
                   y = Proportion,
                   group = ATTRIBUTE_phys_state),
                   label = "p.signif",
                   label.y = c(0.5, 0.4, 0.9, 0.5),
                   size = 6) +
  labs(x = "",
       y = "Proportion of Formulas (%)",
       fill = "") +
  theme(panel.background = element_rect(fill = "white", color = "black", size = 1.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = margin(1,1,1,1, "cm"),
        strip.background = element_rect(fill = "white", color = "black"),
        legend.key = element_rect(fill = "white",color = NA),
        legend.text = element_text(size = 15),
        legend.key.height = unit(0.5, "inch"),
        legend.key.width = unit(0.4, "inch"),
        legend.position = "right",
        legend.title = element_blank(),
        axis.text = element_text(size = 15, color = "black"),
        axis.title = element_text(size = 15),
        text = element_text(family = "Helvetica")) +
  coord_cartesian(expand = c(0,1)) +
  scale_y_continuous(limits = c(0,1), breaks = c(0,0.2,0.4,0.6,0.8,1.0)) +
  guides()

# Sumamry stats 

summary_stoichiometry_table_POS <- formulas_simple_POS %>% 
  group_by(formula_class, ATTRIBUTE_phys_state) %>% 
  summarize(min_p = min(Proportion),
            max_p = max(Proportion),
            mean_p = mean(Proportion),
            sd_p = sd(Proportion))
     
     

```


# Old Analysis

## Aggregate relative peak areas by most specific class

```{r}

agg_by_mostspecificclass_pos <- aggregate(fqt_class_metadata_RA_pos[,19:60], 
                        by = list(fqt_class_metadata_RA_pos$smooshedclass), 
                        FUN = sum) 


agg_by_mostspecificclass_pos <- agg_by_mostspecificclass_pos %>% 
  mutate(smooshedclass = Group.1) %>% 
  select(-Group.1) %>% 
  separate(smooshedclass, into = c("super_class", "class", "subclass", "most_specific_class"), sep = "_")




```

## Merge specific class aggreagated dataframe with metadata 

```{r}

agg_by_mostspecificclass_long_pos <- agg_by_mostspecificclass_pos %>% 
  pivot_longer(!c(super_class, class, subclass, most_specific_class), names_to = "filename", values_to = "relative_peak_area")


agg_specific_class_w_metadata_pos <- merge(metadata_pos,agg_by_mostspecificclass_long_pos, by = "filename")

# Remove the 9/1/24 sample: this was not part of the experiment 

crude_extract_etAoc_pos <-  agg_specific_class_w_metadata_pos %>% 
  filter(ATTRIBUTE_sample_date == "9/1/24")

agg_specific_class_w_metadata_pos <- agg_specific_class_w_metadata_pos %>% 
  filter(ATTRIBUTE_sample_date != "9/1/24")


```

## Summarize by class and subclass for stacked barplot

```{r}

# Agg and sum by class level

agg_metadata_class_level_pos <- agg_specific_class_w_metadata_pos %>% 
  group_by(ATTRIBUTE_sample_date, ATTRIBUTE_age_d, ATTRIBUTE_season, ATTRIBUTE_blade, class,subclass) %>% 
  summarize(class_rpa = sum(relative_peak_area),
            ATTRIBUTE_phys_state = ATTRIBUTE_phys_state,
            super_class = super_class) %>% 
  filter(class_rpa > 0.01)



 agg_metadata_class_level_sum_pos <- agg_metadata_class_level_pos %>% 
  group_by(ATTRIBUTE_sample_date, ATTRIBUTE_age_d,ATTRIBUTE_season,class) %>% 
  summarize(mean_pa = mean(class_rpa),
            sd_pa = sd(class_rpa),
            ATTRIBUTE_phys_state = ATTRIBUTE_phys_state,
            super_class = super_class,
            subclass = subclass) %>% 
   unique()
 
 
# Agg and sum by subclass level

 
agg_metadata_subclass_level_pos <- agg_specific_class_w_metadata_pos %>% 
  group_by(ATTRIBUTE_sample_date, ATTRIBUTE_age_d, ATTRIBUTE_season, ATTRIBUTE_blade,subclass, ATTRIBUTE_phys_state) %>% 
  summarize(subclass_rpa = sum(relative_peak_area))

agg_metadata_subclass_level_sum_pos <- agg_metadata_subclass_level_pos %>% 
  group_by(ATTRIBUTE_sample_date, ATTRIBUTE_age_d,subclass) %>% 
  summarize(mean_pa = mean(subclass_rpa),
            sd_pa = sd(subclass_rpa),
            phys_state = ATTRIBUTE_phys_state)

```


## Amino acids, peptides, and analogues 

```{r}

agg_metadata_subclass_level_pos <- agg_specific_class_w_metadata_pos %>% 
  group_by(ATTRIBUTE_sample_date, ATTRIBUTE_age_d, ATTRIBUTE_season,ATTRIBUTE_blade, subclass) %>% 
  summarize(subclass_rpa = sum(relative_peak_area))

agg_metadata_subclass_level_sum_pos <- agg_metadata_subclass_level_pos %>% 
  group_by(ATTRIBUTE_sample_date, ATTRIBUTE_age_d, ATTRIBUTE_season,subclass) %>% 
  summarize(mean_pa = mean(subclass_rpa),
            sd_pa = sd(subclass_rpa))


agg_metadata_subclass_level_sum_pos %>% 
  filter(subclass == "Amino acids, peptides, and analogues") %>% 
  ggplot(aes(x = ATTRIBUTE_age_d, y = mean_pa, color = ATTRIBUTE_season)) +
  geom_point(size = 4) +
  geom_smooth(method = "lm", se = F, color = "black", size = 2) +
  geom_errorbar(aes(ymin = mean_pa - sd_pa, ymax = mean_pa + sd_pa), width = 0, alpha = 0.5, color = "black") +
  theme(panel.background = element_rect(fill = "white", color = "black", size = 1.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = margin(1,1,1,1, "cm"),
        strip.background = element_rect(fill = "white", color = "black"),
        legend.key = element_rect(fill = "white"),
        legend.text = element_text(size = 15),
        legend.key.height = unit(0.5, "inch"),
        legend.key.width = unit(0.4, "inch"),
        legend.title = element_text(size = 15),
        axis.text = element_text(size = 15, color = "black"),
        axis.title = element_text(size = 15),
        text = element_text(family = "Times")) 



```


## Diterpenoids

```{r}

agg_metadata_class_level_sum_pos %>% 
  filter(subclass == "Diterpenoids") %>% 
  ggplot(aes(x = ATTRIBUTE_age_d, y = mean_pa, color = ATTRIBUTE_season)) +
  geom_point(size = 4) +
  geom_smooth(method = "lm", se = F, color = "black", size = 2) +
  geom_errorbar(aes(ymin = mean_pa - sd_pa, ymax = mean_pa + sd_pa), width = 0, alpha = 0.5, color = "black") +
  theme(panel.background = element_rect(fill = "white", color = "black", size = 1.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = margin(1,1,1,1, "cm"),
        strip.background = element_rect(fill = "white", color = "black"),
        legend.key = element_rect(fill = "white"),
        legend.text = element_text(size = 15),
        legend.key.height = unit(0.5, "inch"),
        legend.key.width = unit(0.4, "inch"),
        legend.title = element_text(size = 15),
        axis.text = element_text(size = 15, color = "black"),
        axis.title = element_text(size = 15),
        text = element_text(family = "Times")) 





```


## Tree Plots

```{r}

agg_metadata_class_level_Phys_sum <- agg_metadata_class_level %>% 
  group_by(ATTRIBUTE_phys_state, class) %>% 
  summarize(mean_rpa = mean(class_rpa),
            sd_rpa = sd(class_rpa),
            ATTRIBUTE_phys_state = ATTRIBUTE_phys_state,
            super_class = super_class) %>% 
  unique() %>% 
  ungroup() %>% 
  mutate(class = ifelse(class == "NA", super_class, class))



mature_look <- agg_metadata_class_level_Phys_sum %>% 
  mutate(class = factor(class)) %>% 
  filter(ATTRIBUTE_phys_state == "Mature")

my_palette <- colorRampPalette(brewer.pal(10, "Set2"))(10)

png(filename = "treemap_output_mature_POS.png", width = 800, height = 600, units = "px")

agg_metadata_class_level_Phys_sum %>% 
  mutate(class = factor(class)) %>% 
  filter(ATTRIBUTE_phys_state == "Mature") %>% 
  treemap(vColor = "super_class",
          index= c("super_class","class"),
          fontcolor.labels = c("transparent", "black"),
            vSize="mean_rpa",
            type="categorical",
          overlap.labels = 1,
          palette = my_palette,
          border.col = c("black", "white"),
          bg.labels = c("transparent"),
          title = "Mature Exudates",
          border.lwds = c(2, 2))

dev.off()

## Create treemap of senescent exudates 

png(filename = "treemap_output_senescent_POS.png", width = 800, height = 600, units = "px")

agg_metadata_class_level_Phys_sum %>% 
  mutate(class = factor(class)) %>% 
  filter(ATTRIBUTE_phys_state == "Senescent") %>% 
  treemap(vColor = "super_class",
          index= c("super_class","class"),
          fontcolor.labels = c("transparent", "black"),
            vSize="mean_rpa",
            type="categorical",
          overlap.labels = 1,
          palette = my_palette,
          border.col = c("black", "white"),
          bg.labels = c("transparent"),
          title = "Senescent Exudates",
          title.legend = "Superclass",
          border.lwds = c(2, 1))

dev.off()


```

## Generate pca or nmds plot for seasons and dev stage using most specific class

```{r}

agg_specific_class_w_metadata_pca_prep_pos <- agg_specific_class_w_metadata_pos %>% 
  select(ATTRIBUTE_sample_date, ATTRIBUTE_phys_state, ATTRIBUTE_season, ATTRIBUTE_age_d, ATTRIBUTE_blade, most_specific_class, relative_peak_area) 

  
agg_specific_class_w_metadata_pca_shape_pos <- agg_specific_class_w_metadata_pca_prep_pos %>% 
  spread(key = most_specific_class, value = relative_peak_area)



agg_specific_class_w_metadata_pca_shape_pos <- agg_specific_class_w_metadata_pca_shape_pos[, colSums(agg_specific_class_w_metadata_pca_shape_pos != 0) > 0]


pos_metab_numeric <- agg_specific_class_w_metadata_pca_shape_pos[1:42,6:259]


pos_metab_numeric_angtransformed <- asin(sqrt(pos_metab_numeric))

#pos_metab_numeric_z_scored <- as.data.frame(scale(pos_metab_numeric_angtransformed, center = TRUE, scale = TRUE))

sugpos_metab.pca1 <- prcomp(pos_metab_numeric, scale = FALSE)

fviz_eig(sugpos_metab.pca1)


summary(sugpos_metab.pca1)

get_eig(sugpos_metab.pca1)

eigenvals(sugpos_metab.pca1)

print(sugpos_metab.pca1)

as.matrix(sugpos_metab.pca1)

var_pos <- get_pca_var(sugpos_metab.pca1)

names(var_pos)

head(var_pos$coord)

var_import_pos <- var_pos$coord

```

## PCA Plot

```{r}

fviz_pca_ind(sugpos_metab.pca1)

pca_plot_pos <- fviz_pca_ind(sugpos_metab.pca1,
                habillage = agg_specific_class_w_metadata_pca_shape_pos[1:42,]$ATTRIBUTE_phys_state, 
                addEllipses = TRUE, 
                ellipse.level = 0.95,
                label = "none",
                geom="point", pointsize = 4,
                 palette = c("grey","orangered")) +
  labs(title = "", 
       x = "PC1 (33 %)",
       y = "PC2 (26 %)") +
  ggtitle("Positive Mode") +
  scale_y_continuous(labels = label_number(accuracy = 0.1)) + 
   theme(panel.background = element_rect(fill = "white", color = "black", size = 1.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = margin(1,1,1,1, "cm"),
        strip.background = element_rect(fill = "white", color = "black"),
        legend.key = element_rect(fill = "white", color = NA),
        legend.text = element_text(size = 20),
        legend.position = "right",
        legend.title = element_blank(),
        plot.title = element_text(size = 15),
        axis.text = element_text(size = 15, color = "black"),
        axis.title = element_text(size = 20),
        text = element_text(family = "Helvetica")) +
  scale_shape_manual(values=c(19,19)) + 
  guides(shape = guide_legend(override.aes = list(size = 5)))



ggsave("pca_plot_pos.pdf", plot = pca_plot_pos, path = "/Users/chanceenglish/Desktop/Lab Shiz/ARPA-e/Giant_Kelp_DOC/Figures/", width = 10, height = 10, device='pdf', dpi=250, units = "in")




```

## PCA Loadings Plot 

```{r}

pca_loadings_plot_pos <- fviz_pca_var(sugpos_metab.pca1,
                col.var = "contrib",
                repel = TRUE,
                axes = c(1,2),
                select.var = list(contrib = 20)) +
  labs(title = "", 
       x = "PC1 (13 %)",
       y = "PC2 (11 %)") +
  ggtitle("Positive Mode") +
  scale_y_continuous(labels = label_number(accuracy = 1)) + 
  scale_color_gradient2(low="white", mid="blue",
           high="red", midpoint=0.6, breaks = seq(0.4,1.0, 0.05)) +
   theme(panel.background = element_rect(fill = "white", color = "black", size = 1.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        legend.key.height = unit(0.35, "inch"),
        legend.key.width = unit(0.4, "inch"),
        plot.margin = margin(1,1,1,1, "cm"),
        strip.background = element_rect(fill = "white", color = "black"),
        legend.key = element_rect(fill = "white"),
        legend.text = element_text(size = 20),
        legend.position = "right",
         plot.title = element_text(size = 24),
        legend.title = element_blank(),
        axis.text = element_text(size = 30, color = "black"),
        axis.title = element_text(size = 30),
        text = element_text(family = "Times"))


ggsave("pca_loadings_plot_pos.pdf", plot = pca_loadings_plot_pos, path = "/Users/chanceenglish/Desktop/Lab Shiz/ARPA-e/Giant_Kelp_DOC/Figures/", width = 10, height = 10, device='pdf', dpi=250, units = "in")



```


## Three outliers in the positive mode. In Dimension ther are enriched in acetamides, Trialkylglycerols, Secondary carboxylic acid amides

```{r}


agg_specific_class_w_metadata_pca_prep_outliers <- agg_specific_class_w_metadata_pca_prep %>% 
  filter(most_specific_class %in% c("Trialkylglycerols", "Secondary carboxylic acid amides", "Acetamides"))


# contamination of a plasticizer in 8/23/23 Blades 1-3



```

## Principle COORDINATE Analysis (better than PCA because you can use Bray Curtis which is better for zero inflated data which is common in metabolite/microbiome data) 

```{r}

# Use the sample-centric relative abundance normalized feature table that have been arcsine transformed


bray_dist_matrix_pos <- vegdist(pos_metab_numeric_angtransformed, method = "bray")

PCoA_NEG_metab_pos  <-  cmdscale(bray_dist_matrix_pos)

str(PCoA_NEG_metab_pos)

head(PCoA_NEG_metab_pos)

colnames(PCoA_NEG_metab_pos) <- c("pcoa1", "pcoa2") 

PCoA_NEG_metab_pos <- PCoA_NEG_metab_pos %>%  
  as_tibble(rownames = "samples")

# Getting eigenvalues 

PCoA_NEG_metab_eig_pos  <-  cmdscale(bray_dist_matrix_pos, eig = TRUE, add = TRUE)

positions_pos <- PCoA_NEG_metab_eig_pos$points

head(positions_pos)

colnames(PCoA_NEG_metab_eig_pos$points) <- c("pcoa1", "pcoa2") 

100* PCoA_NEG_metab_eig_pos$eig / sum(PCoA_NEG_metab_eig_pos$eig)


# Merge with metadata 

agg_specific_class_w_metadata_pca_shape_rownames_pos <- agg_specific_class_w_metadata_pca_shape_pos %>% 
  mutate(samples = 1:42)

PCoA_NEG_metab_metadata_pos <- merge(PCoA_NEG_metab_pos, agg_specific_class_w_metadata_pca_shape_rownames_pos, by = "samples")


#Plot PCo 1 and PCo 2 by developmental stage

PCoA_NEG_metab_metadata_pos %>% 
  ggplot(aes(x = pcoa1,  y = pcoa2)) +
  geom_point(aes(color = ATTRIBUTE_phys_state, shape = ATTRIBUTE_season),
             size = 5) +
  scale_color_manual(values = c("grey", "orangered")) +
  scale_fill_manual(values = c("grey", "orangered")) +
  scale_y_continuous(labels = label_number(accuracy = 0.1)) + 
  labs(x = "PCo 1 (23.3%)",
       y = "PCo 2 (15.6%)") +
   theme(panel.background = element_rect(fill = "white", color = "black", size = 1.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = margin(1,1,1,1, "cm"),
        legend.key = element_rect(fill = "white",color = NA),
        legend.text = element_text(size = 20),
        legend.position = "right",
        legend.title = element_blank(),
        axis.text = element_text(size = 15, color = "black"),
        axis.title = element_text(size = 20),
        text = element_text(family = "Helvetica")) +
  stat_ellipse(aes(x = pcoa1,  
                   y = pcoa2, 
                   color = ATTRIBUTE_phys_state,
                   fill = ATTRIBUTE_phys_state),
               geom = "polygon", alpha = 0.2) +
  guides(shape = guide_legend(override.aes = list(size = 5)))


#Plot PCo 1 and PCo 2 by Season 

PCoA_NEG_metab_metadata_pos %>% 
  ggplot(aes(x = pcoa1,  y = pcoa2)) +
  geom_point(aes(color = ATTRIBUTE_season, shape = ATTRIBUTE_phys_state),
             size = 5) +
  scale_color_manual(values = c("dodgerblue", "red")) +
  scale_fill_manual(values = c("dodgerblue", "red")) +
  scale_y_continuous(labels = label_number(accuracy = 0.1)) + 
  labs(x = "PCo 1 (30.7%)",
       y = "PCo 2 (11.3%)") +
   theme(panel.background = element_rect(fill = "white", color = "black", size = 1.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = margin(1,1,1,1, "cm"),
        legend.key = element_rect(fill = "white",color = NA),
        legend.text = element_text(size = 20),
        legend.position = "right",
        legend.title = element_blank(),
        axis.text = element_text(size = 15, color = "black"),
        axis.title = element_text(size = 20),
        text = element_text(family = "Helvetica")) +
  stat_ellipse(aes(x = pcoa1,  
                   y = pcoa2, 
                   color = ATTRIBUTE_season,
                   fill = ATTRIBUTE_season),
               geom = "polygon", alpha = 0.2) +
  guides(shape = guide_legend(override.aes = list(size = 5)))


# Mature Data Only by Season


PCoA_NEG_metab_metadata_pos %>% 
  filter(ATTRIBUTE_phys_state == "Mature") %>% 
  ggplot(aes(x = pcoa1,  y = pcoa2)) +
  geom_point(aes(color = ATTRIBUTE_season),
             size = 5) +
  scale_color_manual(values = c("grey", "orangered")) +
  scale_fill_manual(values = c("grey", "orangered")) +
  scale_y_continuous(labels = label_number(accuracy = 0.1)) + 
  labs(x = "PCo 1 (30.7%)",
       y = "PCo 2 (11.3%)") +
   theme(panel.background = element_rect(fill = "white", color = "black", size = 1.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = margin(1,1,1,1, "cm"),
        legend.key = element_rect(fill = "white",color = NA),
        legend.text = element_text(size = 20),
        legend.position = "right",
        legend.title = element_blank(),
        axis.text = element_text(size = 15, color = "black"),
        axis.title = element_text(size = 20),
        text = element_text(family = "Helvetica")) +
  stat_ellipse(aes(x = pcoa1,  
                   y = pcoa2, 
                   color = ATTRIBUTE_season,
                   fill = ATTRIBUTE_season),
               geom = "polygon", alpha = 0.2) +
  guides(shape = guide_legend(override.aes = list(size = 5)))


# Senescent Data Only by Season

PCoA_NEG_metab_metadata_pos %>% 
  filter(ATTRIBUTE_phys_state == "Senescent") %>% 
  ggplot(aes(x = pcoa1,  y = pcoa2)) +
  geom_point(aes(color = ATTRIBUTE_season),
             size = 5) +
  scale_color_manual(values = c("grey", "orangered")) +
  scale_fill_manual(values = c("grey", "orangered")) +
  scale_y_continuous(labels = label_number(accuracy = 0.1)) + 
  labs(x = "PCo 1 (30.7%)",
       y = "PCo 2 (11.3%)") +
   theme(panel.background = element_rect(fill = "white", color = "black", size = 1.5),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.margin = margin(1,1,1,1, "cm"),
        legend.key = element_rect(fill = "white",color = NA),
        legend.text = element_text(size = 20),
        legend.position = "right",
        legend.title = element_blank(),
        axis.text = element_text(size = 15, color = "black"),
        axis.title = element_text(size = 20),
        text = element_text(family = "Helvetica")) +
  stat_ellipse(aes(x = pcoa1,  
                   y = pcoa2, 
                   color = ATTRIBUTE_season,
                   fill = ATTRIBUTE_season),
               geom = "polygon", alpha = 0.2) +
  guides(shape = guide_legend(override.aes = list(size = 5)))


```

## Permanova for Sugar Mol% between Mature and Senescent phase Kelp and between seasons and seasons broken down by developmental stage


```{r}

# Variance stabilize the sample centric metabolites relative adundance data

POS_metab_c_4_permanova <- asin(sqrt(agg_specific_class_w_metadata_pca_shape_pos[1:42,6:259]))
  

# PERMANOVA of differences in metabolite composition by physiological state


POS_metab_phys_state_adonis <- adonis2(POS_metab_c_4_permanova~ATTRIBUTE_phys_state, data = agg_specific_class_w_metadata_pca_shape_pos[1:42,], method = "bray")

POS_metab_phys_state_adonis # R2 = 0.19 p = 0.001 F = 9.5544 stronger driver


# PERMANOVA of differences in metabolite composition by season

POS_metab_season_adonis <- adonis2(POS_metab_c_4_permanova~ATTRIBUTE_season, data = agg_specific_class_w_metadata_pca_shape_pos[1:42,], method = "bray")

POS_metab_season_adonis # R2 = 0.14 p = 0.001 F = 6.6775, weaker driver than dev stage

# PERMANOVA of differences in metabolite composition by season : Mature Kelp

agg_specific_class_w_metadata_pca_shape_mature_pos <- agg_specific_class_w_metadata_pca_shape_pos %>% 
  filter(ATTRIBUTE_phys_state == "Mature")

POS_metab_c_4_permanova_mature <- asin(sqrt(agg_specific_class_w_metadata_pca_shape_mature_pos[1:24,6:259]))

POS_metab_phys_state_adonis_mature <- adonis2(POS_metab_c_4_permanova_mature~ATTRIBUTE_season, data = agg_specific_class_w_metadata_pca_shape_mature_pos[1:24,], method = "bray")

POS_metab_phys_state_adonis_mature # R2 = 0.25 p = 0.001 F = 7.4058


# PERMANOVA of differences in metabolite composition by season : Senescent Kelp

agg_specific_class_w_metadata_pca_shape_senescent <- agg_specific_class_w_metadata_pca_shape %>% 
  filter(ATTRIBUTE_phys_state == "Senescent")

NEG_metab_c_4_permanova_senescent <- asin(sqrt(agg_specific_class_w_metadata_pca_shape_senescent[1:18,6:360]))

NEG_metab_phys_state_adonis_senescent <- adonis2(NEG_metab_c_4_permanova_senescent~ATTRIBUTE_season, data = agg_specific_class_w_metadata_pca_shape_senescent[1:18,], method = "bray")

NEG_metab_phys_state_adonis_senescent # R2 = 0.31 p = 0.001 F = 7.3469

```

